### 2024-03-13 doc/sections/mav-semantics.lagda.tex
Split up file

\section{Semantics}\label{sec:mav-semantics}

\subsection{$*$-autonomous and Duoidal Preorders}

\subsection{MAV Algebras}

\subsection{Interpretation}

\subsection{Chu Construction and Self-Dual Monoids}

\newcommand{\Chu}{\mathrm{Chu}}
\newcommand{\op}{\mathrm{op}}

To construct suitable MAV Algebras, we use the preorder version of the
Chu construction \cite{barr}. The Chu construction builds
$*$-autonomous categories from symmetric monoidal closed categories
with pullbacks. In the preorder case, the requirement for preorders
simplifies to binary meets. Therefore, for this section, we let
$(A, \leq, \bullet, \epsilon, -\kern-9pt\bullet)$ be a symmetric
monoidal closed preorder with all binary meets.

\begin{definition}
  Let $k$ be an element of $A$. $\Chu(A, k)$ is the preorder with
  elements comprised of pairs $(a^+, a^-)$ such that
  $a^+ \bullet a^- \leq k$, with ordering
  $(a^+,a^-) \sqsubseteq (b^+, b^-)$ when $a^+ \leq b^+$ and
  $b^- \leq a^-$.
\end{definition}

\begin{theorem}
  $\Chu(A, k)$ is a $*$-autonomous preorder with symmetric monoidal
  structure and negation defined as:
  \begin{mathpar}
    (a^+, a^-) \otimes (b^+, b^-) = (a^+ \bullet b^+, (b^+ \multimap a^-) \land (a^+ \multimap b^-))

    I = (\epsilon, k)

    (a^+,a^-)^\perp = (a^-, a^+)
  \end{mathpar}
\end{theorem}

\begin{theorem}
  If $A$ has binary joins, then $\Chu(A, k)$ has binary meets, given
  by $(a^+,a^-) \land (b^+,b^-) = (a^+ \land b^+, a^- \lor b^-)$.
\end{theorem}

\paragraph{Self-dual duoidal structure}
These two theorems give us enough structure to interpret the
multiplicative and additive constructs of MAV. We need to also
interpret the self-dual $P; Q$ connective. Let us assume that we have
an operation $-\rhd- : A \times A \to A$ that we want to induce
self-dual operator on $\Chu(A, k)$. By the way the Chu construction is
defined, we can make an operator that is self-dual by definition:
\begin{displaymath}
  (a^+, a^-) ; (b^+, b^-) = (a^+ \rhd b^+, a^- \rhd b^-)
\end{displaymath}
for this to work, we need to assume duoidality.

And that the dualising object $k$ is a
satisfies $k \rhd k \leq k$. If $\rhd$ has a unit $j$, then $(j, j)$ is a unit if

The Chu construction allows us to state
directly that any operator we define on $\Chu(A, k)$ is self dual by
defining as the same

\subsection{Monoids on Lower Sets}

Lower sets: $X : A^\op \to \Omega$.

\begin{proposition}
  FIXME: Day construction.
\end{proposition}

\subsection{Closure Operators on Lower Sets}

need the ``preorder of elements'' $\int X$ of a lower set $X$.

need trees, and their combination.

% what would the category version of this look like?

\begin{displaymath}
  \mathsf{C}(X) = \{ x \mid t \in \mathrm{Tree}(\int X), x \leq \mathrm{combine}(t) \}
\end{displaymath}

\begin{theorem}
  $\mathsf{C}$ is a closure operator. Moreover, it is lax monoidal wrt
  to one operator, and strong monoidal wrt the other.
\end{theorem}

### 2024-03-22 doc/sections/introduction.tex
Un-agda files

\section{Introduction}\label{sec:introduction}

\begin{enumerate}
      \item It makes sense to add a sequencing connective to MALL. This is
            motivated by coherence spaces (Retore), or by thinking in terms of
            session types.
      \item A sequent calculus is not possible (CITE: Tiu, Strassberger),
            but it is possible to define a proof calculus based on deep
            inference. (Also Retore's proof nets, but it turns out they define a
            different logic).
      \item To make sure that a proof system makes sense, we need some kind
            of Cut-elimination theorem that ensures that all proofs can be
            placed into a normal form where it is evident that it is not
            possible to derive all results.
\end{enumerate}

MAV is defined by Horne \cite{Horne15:mav}, who gave a syntactic proof
of cut-elimination and the admissibility of several other rules. We
provide an alternative proof of cut-elimination via a semantic
model. This proof avoids some of the intrincate syntactic reasoning in
Horne's proof and is more modular, as evidenced by the extensions we
present in \autoref{sec:mav-extensions}.

Cut-elimination for MALL by construction of a semantic model is due to
Okada \cite{Okada99:psc}, who shows that the a Phase Space model of
MALL (described by Girard \cite{Girard87:ll} and Troelstra
\cite{TroelstraXX:lnll}) can be constructed from cut-proof proofs. The
completeness of this model directly yields the existence of a cut-free
proof for every proof constructible in the MALL sequent calculus. For
MAV, we cannot use Phase Spaces due to the

The same technique has been used for MALL with fixpoints (CITE:
Saurin) and for Bunched Implications with extensions (CITE: Frumin).

### 2024-03-22 doc/sections/mav-extensions.tex
Un-agda files

\section{Extensions}\label{sec:mav-extensions}

\subsection{Additive Units}

\subsection{Multiplicative-Additive Linear Logic}

\subsection{Display Calculus}

Cut-elimination for a Display calculus?

### 2024-03-22 doc/sections/mav-syntax.tex
Un-agda files

\begin{code}[hide]
  module mav-syntax (Atom : Set) where
\end{code}
\section{Multiplicative-Additive System Virtual}\label{sec:mav-syntax}

TODO: introduce MAV and Deep Inference.

Formulas:
\begin{code}[hide]
  infix 20 _⁺
  infix 20 _⁻
  infix 10 _⅋_
  infix 10 _⊗_
  infix 10 _&_
  infix 10 _⊕_
  infix 10 _▷_
\end{code}

\begin{code}
  data Formula : Set where
    I    : Formula
    _⁺   : Atom → Formula
    _⁻   : Atom → Formula
    _⅋_  : Formula → Formula → Formula
    _⊗_  : Formula → Formula → Formula
    _&_  : Formula → Formula → Formula
    _⊕_  : Formula → Formula → Formula
    _▷_  : Formula → Formula → Formula
\end{code}

\begin{displaymath}
  P, Q
  \Coloneq A^{+}
  \mid     A^{-}
  \mid     I
  \mid     P \bvtens Q
  \mid     P \bvparr Q
  \mid     P \bvwith Q
  \mid     P \bvplus Q
  \mid     P \bvseq  Q
\end{displaymath}

\begin{code}[hide]
  variable
    A A′ A₁ A₂ : Atom
    P P′ P₁ P₂ : Formula
    Q Q′ Q₁ Q₂ : Formula
    R R′ R₁ R₂ : Formula
    S S′ S₁ S₂ : Formula
\end{code}

Negation:
% \begin{displaymath}
%   \begin{array}{lcl}
%     (a)^\perp           & = & a^\perp                     \\
%     (a^\perp)^\perp     & = & a                           \\
%     (I)^\perp           & = & I                           \\
%     (P \otimes Q)^\perp & = & (P)^\perp \parr   (Q)^\perp \\
%     (P \parr   Q)^\perp & = & (P)^\perp \otimes (Q)^\perp \\
%     (P \with   Q)^\perp & = & (P)^\perp \oplus  (Q)^\perp \\
%     (P \oplus  Q)^\perp & = & (P)^\perp \with   (Q)^\perp \\
%     (P ; Q)^\perp       & = & (P)^\perp ; (Q)^\perp
%   \end{array}
% \end{displaymath}

\begin{code}[hide]
  infix 15 ¬_
\end{code}

\begin{code}
  ¬_ : Formula → Formula
  ¬ I          = I
  ¬ A ⁺        = A ⁻
  ¬ A ⁻        = A ⁺
  ¬ (P  ⅋  Q)  = ¬ P  ⊗  ¬ Q
  ¬ (P  ⊗  Q)  = ¬ P  ⅋  ¬ Q
  ¬ (P  &  Q)  = ¬ P  ⊕  ¬ Q
  ¬ (P  ⊕  Q)  = ¬ P  &  ¬ Q
  ¬ (P  ▷  Q)  = ¬ P  ▷  ¬ Q
\end{code}

### 2024-03-22 doc/sections/mav-syntax.tex
Add DSL for BV connectives

@@
-\begin{code}[hide]
-  module mav-syntax (Atom : Set) where
-\end{code}
 \section{Multiplicative-Additive System Virtual}\label{sec:mav-syntax}
@@
 Formulas:
-\begin{code}[hide]
-  infix 20 _⁺
-  infix 20 _⁻
-  infix 10 _⅋_
-  infix 10 _⊗_
-  infix 10 _&_
-  infix 10 _⊕_
-  infix 10 _▷_
-\end{code}
-
-\begin{code}
-  data Formula : Set where
-    I    : Formula
-    _⁺   : Atom → Formula
-    _⁻   : Atom → Formula
-    _⅋_  : Formula → Formula → Formula
-    _⊗_  : Formula → Formula → Formula
-    _&_  : Formula → Formula → Formula
-    _⊕_  : Formula → Formula → Formula
-    _▷_  : Formula → Formula → Formula
-\end{code}
-
 \begin{displaymath}
@@
   \mid     A^{-}
-  \mid     I
-  \mid     P \bvtens Q
-  \mid     P \bvparr Q
-  \mid     P \bvwith Q
-  \mid     P \bvplus Q
-  \mid     P \bvseq  Q
+  \mid     \Unit
+  \mid     P \Tens Q
+  \mid     P \Parr Q
+  \mid     P \With Q
+  \mid     P \Plus Q
+  \mid     P \Seq  Q
 \end{displaymath}
 
-\begin{code}[hide]
-  variable
-    A A′ A₁ A₂ : Atom
-    P P′ P₁ P₂ : Formula
-    Q Q′ Q₁ Q₂ : Formula
-    R R′ R₁ R₂ : Formula
-    S S′ S₁ S₂ : Formula
-\end{code}
-
 Negation:
-% \begin{displaymath}
-%   \begin{array}{lcl}
-%     (a)^\perp           & = & a^\perp                     \\
-%     (a^\perp)^\perp     & = & a                           \\
-%     (I)^\perp           & = & I                           \\
-%     (P \otimes Q)^\perp & = & (P)^\perp \parr   (Q)^\perp \\
-%     (P \parr   Q)^\perp & = & (P)^\perp \otimes (Q)^\perp \\
-%     (P \with   Q)^\perp & = & (P)^\perp \oplus  (Q)^\perp \\
-%     (P \oplus  Q)^\perp & = & (P)^\perp \with   (Q)^\perp \\
-%     (P ; Q)^\perp       & = & (P)^\perp ; (Q)^\perp
-%   \end{array}
-% \end{displaymath}
-
-\begin{code}[hide]
-  infix 15 ¬_
-\end{code}
-
-\begin{code}
-  ¬_ : Formula → Formula
-  ¬ I          = I
-  ¬ A ⁺        = A ⁻
-  ¬ A ⁻        = A ⁺
-  ¬ (P  ⅋  Q)  = ¬ P  ⊗  ¬ Q
-  ¬ (P  ⊗  Q)  = ¬ P  ⅋  ¬ Q
-  ¬ (P  &  Q)  = ¬ P  ⊕  ¬ Q
-  ¬ (P  ⊕  Q)  = ¬ P  &  ¬ Q
-  ¬ (P  ▷  Q)  = ¬ P  ▷  ¬ Q
-\end{code}
+\begin{displaymath}
+  \begin{array}{lcl}
+    \Dual(\Pos(A))   & = & \Neg(A)                 \\
+    \Dual(\Neg(A))   & = & \Pos(A)                 \\
+    \Dual(\Unit)     & = & \Unit                   \\
+    \Dual(P \Tens Q) & = & \Dual(P) \Parr \Dual(Q) \\
+    \Dual(P \Parr Q) & = & \Dual(P) \Tens \Dual(Q) \\
+    \Dual(P \With Q) & = & \Dual(P) \Plus \Dual(Q) \\
+    \Dual(P \Plus Q) & = & \Dual(P) \With \Dual(Q) \\
+    \Dual(P \Seq  Q) & = & \Dual(P) \Seq  \Dual(Q)
+  \end{array}
+\end{displaymath}

### 2024-03-23 doc/sections/mav-syntax.tex
Push changes before rewrite
Stuff

@@
 
-TODO: introduce MAV and Deep Inference.
+\begin{itemize}
+  \item Structural equivalences are explicit.
+  \item Inference is a congruence.
+  \item Inference rules are unary.
+  \item Relate to usual presentation of MALL.
+  \item Relate to usual presentation of BV.
+\end{itemize}
 
@@
 \begin{displaymath}
-  P, Q
-  \Coloneq A^{+}
-  \mid     A^{-}
-  \mid     \Unit
-  \mid     P \Tens Q
-  \mid     P \Parr Q
-  \mid     P \With Q
-  \mid     P \Plus Q
-  \mid     P \Seq  Q
+  \vP,\vQ
+  \Coloneq \vPos\vA
+  \mid     \vNeg\vA
+  \mid     \vUnit
+  \mid     \vP\vSeq \vQ
+  \mid     \vP\vTens\vQ
+  \mid     \vP\vParr\vQ
+  \mid     \vP\vWith\vQ
+  \mid     \vP\vPlus\vQ
 \end{displaymath}
@@
 \begin{displaymath}
-  \begin{array}{lcl}
-    \Dual(\Pos(A))   & = & \Neg(A)                 \\
-    \Dual(\Neg(A))   & = & \Pos(A)                 \\
-    \Dual(\Unit)     & = & \Unit                   \\
-    \Dual(P \Tens Q) & = & \Dual(P) \Parr \Dual(Q) \\
-    \Dual(P \Parr Q) & = & \Dual(P) \Tens \Dual(Q) \\
-    \Dual(P \With Q) & = & \Dual(P) \Plus \Dual(Q) \\
-    \Dual(P \Plus Q) & = & \Dual(P) \With \Dual(Q) \\
-    \Dual(P \Seq  Q) & = & \Dual(P) \Seq  \Dual(Q)
+  \begin{array}{
+      l@{\;=\;}l @{\hspace{1cm}}
+      l@{\;=\;}l @{\hspace{1cm}}
+      l@{\;=\;}l @{\hspace{1cm}}
+      l@{\;=\;}l}
+    \vDual{\vPos\vA}     & \vNeg\vA
+                         &
+    \vDual{\vUnit}       & \vUnit
+                         &
+    \vDual{\vP\vTens\vQ} & \vDual\vP \vParr \vDual\vQ
+                         &
+    \vDual{\vP\vParr\vQ} & \vDual\vP \vTens \vDual\vQ
+    \\
+    \vDual{\vNeg\vA}     & \vPos\vA
+                         &
+    \vDual{\vP\vSeq \vQ} & \vDual\vP \vSeq  \vDual\vQ
+                         &
+    \vDual{\vP\vWith\vQ} & \vDual\vP \vPlus \vDual\vQ
+                         &
+    \vDual{\vP\vPlus\vQ} & \vDual\vP \vWith \vDual\vQ
   \end{array}
 \end{displaymath}
+
+Inference rules:
+\begin{displaymath}
+  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
+    \vP\vParr\vDual\vP
+     & \vUnit
+     & \RuleLabel{axiom}
+    \\
+    \vUnit
+     & \vP\vTens\vDual\vP
+     & \RuleLabel{cut}
+    \\
+    \vUnit\vWith\vUnit
+     & \vUnit
+     & \RuleLabel{tidy}
+    \\
+    (\vP\vTens\vQ)\vParr\vR
+     & \vP\vTens(\vQ\vParr\vR)
+     & \RuleLabel{switch}
+    \\
+    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
+     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
+     & \RuleLabel{sequence}
+    \\
+    \vP\vPlus\vQ
+     & \vP
+     & \RuleLabel{left}
+    \\
+    \vP\vPlus\vQ
+     & \vQ
+     & \RuleLabel{right}
+    \\
+    (\vP\vWith\vQ)\vParr\vR
+     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
+     & \RuleLabel{external}
+    \\
+    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
+     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
+     & \RuleLabel{medial}
+  \end{array}
+\end{displaymath}
+
+Equivalence rules:
+\begin{displaymath}
+  \begin{array}{
+      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
+      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
+      l@{\;\vEquiv\;}ll}
+    \vP\vSeq\vUnit
+     & \vP
+     & \RuleLabel*[seq-runit]{\vSeq-Unit\textsuperscript{R}}
+     &
+    \vUnit\vSeq\vP
+     & \vP
+     & \RuleLabel*[seq-lunit]{\vSeq-Unit\textsuperscript{L}}
+     &
+    \vP\vSeq(\vQ\vSeq\vR)
+     & (\vP\vSeq\vQ)\vSeq\vP
+     & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
+    \\
+    \vP\vTens\vUnit
+     & \vP
+     & \RuleLabel*[tens-unit]{\vTens-Unit}
+     &
+    \vP\vTens\vQ
+     & \vQ\vTens\vP
+     & \RuleLabel*[tens-comm]{\vTens-Comm}
+     &
+    \vP\vTens(\vQ\vTens\vR)
+     & (\vP\vTens\vQ)\vTens\vP
+     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
+    \\
+    \vP\vParr\vUnit
+     & \vP
+     & \RuleLabel*[parr-unit]{\vParr-Unit}
+     &
+    \vP\vParr\vQ
+     & \vQ\vParr\vP
+     & \RuleLabel*[parr-comm]{\vParr-Comm}
+     &
+    \vP\vParr(\vQ\vParr\vR)
+     & (\vP\vParr\vQ)\vParr\vP
+     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
+  \end{array}
+\end{displaymath}
+
+We write $\vEquiv$ for invertible inference rules, \ie $\vP\vEquiv\vQ$ means $\vP\vInfer\vQ$ and $\vQ\vInfer\vP$.
+
+We write $\vInfer*$ for the reflexive, transitive closure of $\vInfer$.

### 2024-03-23 doc/sections/introduction.tex
Grow TODO list

@@
 
-\begin{enumerate}
-      \item It makes sense to add a sequencing connective to MALL. This is
-            motivated by coherence spaces (Retore), or by thinking in terms of
-            session types.
-      \item A sequent calculus is not possible (CITE: Tiu, Strassberger),
-            but it is possible to define a proof calculus based on deep
-            inference. (Also Retore's proof nets, but it turns out they define a
-            different logic).
+\begin{itemize}
+      \item BV by Guglielmi~\cite{Guglielmi07:sis} is an extension of MLL inspired by process algebras such as CCS~\cite{Milner89:CC,Milner80:CCS} and Pomset Logic~\cite{Retore97:pomset}.
+      \item MAV by Hornes~\cite{Horne15:mav} extends BV with the additives.
+      \item BV adds a non-commutative connective to MLL. Such a connective can be motivated by coherence spaces, or by session types.
+      \item A shallow sequent calculus cannot capture BV~\cite{Tiu06:sisii}.
       \item To make sure that a proof system makes sense, we need some kind
@@
             possible to derive all results.
-\end{enumerate}
+\end{itemize}
 

### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] sketch some of the semantics section

--- 2024-03-13 doc/sections/mav-semantics.lagda.tex
@@
 
-\subsection{$*$-autonomous and Duoidal Preorders}
+\subsection{$*$-autonomous and Duoidal Partial Orders}
+
+\begin{definition}
+  A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
+  $(A, \leq)$ comprises a binary operator $\bullet : A \times A \to A$
+  that is monotone in both arguments and an element $i \in A$ such
+  that the usual monoid laws hold. A \emph{commutative pomonoid} is a
+  pomonoid where additionally $x \bullet y = y \bullet x$.
+\end{definition}
+
+\begin{definition}
+  A \emph{$*$-autonomous partial order} is ... TODO
+\end{definition}
+
+FIXME: cite that combinatorics book.
+\begin{definition}
+  Two pomonoids $(\bullet, i)$ and $(\rhd, j)$ on a partial order
+  $(A, \leq)$ are in a \emph{duoidal} relationship if the following
+  inequalities hold:
+  \begin{enumerate}
+  \item $(w \rhd x) \bullet (y \rhd z) \leq (w \bullet y) \rhd (x \bullet z)$
+  \item $j \bullet j \leq j$
+  \item $i \leq i \rhd i$
+  \item $i \leq j$
+  \end{enumerate}
+\end{definition}
+
+\begin{remark}
+  In the case when the two pomonoids share a common unit (as in MAV),
+  the last three conditions for a duoidal relationship are
+  automatically satisfied.
+\end{remark}
 
@@
 
+\begin{definition}
+  An \emph{MAV Algebra} is a structure $(A, \leq, ...)$
+  \begin{enumerate}
+  \item 
+  \end{enumerate}
+\end{definition}
+
+\bob{Consequences of the definition, as listed in the Agda}
+
 \subsection{Interpretation}
+
+\begin{theorem}
+  The interpretation of SMAV proofs in an MAV Algebra is sound. \bob{elaborate...}
+\end{theorem}
+
+\subsection{MAV Frames}
+
+\begin{definition}
+  An \emph{MAV Frame} is a structure
+  $(F, \leq, I, \parallel, \rhd, +)$ where $(F, \leq)$ is a partial
+  order, $(F, \leq, I, \parallel)$ is a commutative pomonoid,
+  $(F, \leq, I, \rhd)$ is a pomonoid, $+$ is a binary monotone
+  function on $(F, \leq)$, and these structures satisfy the following:
+  \begin{enumerate}
+  \item $(w \rhd x) \parallel (y \rhd z) \leq (w \parallel y) \rhd (x \parallel z)$
+  \item $(x + y) \parallel z \leq (x \parallel z) + (y \parallel z)$
+  \item $(w \rhd x) + (y \rhd z) \leq (w + y) \rhd (x + z)$
+  \item $I + I \leq I$
+  \end{enumerate}
+\end{definition}
+
+\begin{remark}
+  \bob{Connection to process algebras}
+\end{remark}
+
+\begin{proposition}
+  \bob{The Cut-free system forms an MAV Frame}
+\end{proposition}
 
@@
 
-To construct suitable MAV Algebras, we use the preorder version of the
+To construct suitable MAV Algebras, we use the poset version of the
 Chu construction \cite{barr}. The Chu construction builds

### 2024-03-25 doc/sections/introduction.tex
Add virginialake, Ozan cite,
Add Nguyễn and Straßburger

@@
 
+We present an algebraic semantics and semantic proof of cut elimination for the multiplicative-additive deep inference calculus MAV~\cite{Horne15:mav}, an extension of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll} with a self-dual non-commutative connective.
+
+Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems which arose from Guglielmi's attempts to relate process algebras~\cite[CCS]{Milner89:CC,Milner80:CCS} to linear logic~\cite{Girard87:ll}.
+The problem is that, while the connectives of linear logic capture parallel composition, no connective captures \emph{sequential composition}.
+Eventually, Guglielmi's attempts yielded the basic deep inference calculus, BV~\cite{Guglielmi99:bv,Guglielmi07:sis}, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that does capture sequential composition.
+Such a connective was already present in Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence spaces~\cite[Chapter 8]{GirardTL89:proofs}, which are a semantics for proofs of linear logic.
+While BV is similar to Pomset logic, the two are not the same.
+Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that the theorems of BV are a proper subset of the theorems of Pomset logic.
+
+% Neither BV nor Pomset logic has a sequent calculus.
+% ~\cite{Tiu06:sisii}
+
 \begin{itemize}
-      \item BV by Guglielmi~\cite{Guglielmi07:sis} is an extension of MLL inspired by process algebras such as CCS~\cite{Milner89:CC,Milner80:CCS} and Pomset Logic~\cite{Retore97:pomset}.
+      \item BV~\cite{Guglielmi07:sis} by Guglielmi is an extension of MLL inspired by process algebras such as CCSand Pomset Logic~\cite{Retore97:pomset}.
       \item MAV by Hornes~\cite{Horne15:mav} extends BV with the additives.

### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] more material on the semantics of MAV

@@
   A \emph{$*$-autonomous partial order} is ... TODO
+
 \end{definition}
+
+\begin{remark}
+  The structure of a $*$-autonomous partial order has a number of
+  immediate consequences, but we leave description of these until
+  after the definition of MAV algebra below. \bob{because there are
+    even more consequences in the presence of additive and duoidal
+    structure}
+\end{remark}
 
@@
 \begin{definition}
-  An \emph{MAV Algebra} is a structure $(A, \leq, ...)$
+  An \emph{MAV Algebra} is a structure
+  $(A, \leq, \otimes, \rhd, I, \lnot)$ with the following properties:
   \begin{enumerate}
-  \item 
+  \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
+  \item $(A, \leq, \rhd, I)$ is a pomonoid.
+  \item $(\otimes, I)$ and $(\rhd, I)$ are in a duoidal relationship.
+  \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
   \end{enumerate}
@@
 
+\begin{proposition}\label{prop:mav-algebra-consequences}
   \bob{Consequences of the definition, as listed in the Agda}
+\end{proposition}
 
-\subsection{Interpretation}
+\begin{definition}\label{defn:mav-interpretation}
+  Let $\mathit{At}$ be a set of atomic propositions. Given an MAV
+  Algebra $(A, \leq, \otimes, \rhd, I, \lnot)$ and valuation
+  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas as follows:
+  \begin{mathpar}
+    FIXME
+  \end{mathpar}
+\end{definition}
 
-\begin{theorem}
-  The interpretation of SMAV proofs in an MAV Algebra is sound. \bob{elaborate...}
+\begin{theorem}\label{thm:soundness}
+  The interpretation defined in Definition
+  \ref{defn:mav-interpretation} is sound: for all formulas $P$, if
+  $P \longrightarrow^* I$, then $I \leq \llbracket P \rrbracket$.
 \end{theorem}
 
+\begin{proof}
+  Each of the required inequalities has been established in
+  Proposition \ref{prop:mav-algebra-consequences}.
+\end{proof}
+
 \subsection{MAV Frames}
+
+To prove completeness of the cut-free fragment of SMAV, we will
+construct a particular MAV Algebra from the syntax and cut-free
+proofs. Since cut-free proofs do not a priori have all the necessary
+structure for an MAV Algebra, we develop a procedure to construct MAV
+Algebra from the lighter requirements of an MAV Frame, defined in this
+section. MAV Frames have an intuitive reading as a kind of process
+algebra, so we use process algebra-like notation. In the following
+sections, we show how every MAV Frame induces an MAV Algebra, and in
+Section XXX we will show that the MAV Algebra constructed from the
+cut-free proof MAV Frame allows us to prove that all proofs in SMAV
+have cut-free normal forms.
 
@@
   $(F, \leq, I, \rhd)$ is a pomonoid, $+$ is a binary monotone
-  function on $(F, \leq)$, and these structures satisfy the following:
+  function on $(F, \leq)$, and these structures satisfy the following
+  inequalities:
   \begin{enumerate}
@@
 \begin{remark}
-  \bob{Connection to process algebras}
+  \bob{A frame is nearly two duoidal structures, except that we don't
+    assume that $+$ is a monoid, nor is there a unit element for it.}
+\end{remark}
+
+\begin{remark}
+  \bob{Connection to process algebras: we can read the ordering as
+    ``reduces to'' and the connectives as parallel combination,
+    sequential composition, and choice, respectively. If we add in
+    atomic elements with duals and an interaction law, then we get
+    something like CCS without restriction, but with sequential
+    composition.}
 \end{remark}
@@
 \begin{proposition}
-  \bob{The Cut-free system forms an MAV Frame}
+  \bob{The Cut-free system forms an MAV Frame; fwd ref to next section}
 \end{proposition}
 
-\subsection{Chu Construction and Self-Dual Monoids}
+\subsection{Constructing MAV Algebras from MAV Frames}
 
+\newcommand{\LowerSet}[1]{\widehat{#1}}
+
+\bob{Some introductory text here: explain the steps in the construction and what each one adds.}
+
+\subsubsection{Lower Sets}
+
+\begin{definition}
+  Given a partial order $(A, \leq)$, the set of lower sets
+  $\LowerSet{A}$ consists of subsets $F \subseteq A$ that are
+  down-closed: $x \in F$ and $y \leq x$ implies $y \in F$. Lower sets
+  are ordered by inclusion. Define the embedding
+  $\eta : A \to \LowerSet{A}$ as $\eta(x) = \{ y \mid y \leq x \}$.
+\end{definition}
+
+\begin{proposition}
+  For any $(A, \leq)$, the function $\eta$ is monotone, and
+  $(\LowerSet{A}, \subseteq)$ has meets and joins given by
+  intersection and union respectively.
+
+  \bob{and $\eta$ preserves any meets that exist}
+\end{proposition}
+
+\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
+
+\begin{proposition}\label{prop:day-construction}
+  If $(\bullet, i)$ is a pomonoid on $(A, \leq)$, then there is a
+  corresponding \emph{Day pomonoid} $(\Day{\bullet}, \Day{i})$ on
+  $\LowerSet{A}$ defined as
+  $F \Day\bullet G = \{ z \mid z \leq x \bullet y, x \in F, y \in G
+  \}$ and $\Day{i} = \eta(i)$. Moreover:
+  \begin{enumerate}
+  \item $(\Day{\bullet}, \Day{i})$ is left and right residuated: there
+    exists a function
+    $\Day{\rightblackspoon} : \LowerSet{A} \times \LowerSet{A} \to
+    \LowerSet{A}$ such that ... FIXME
+  \item If $(\bullet, i)$ is a commutative pomonoid, then so is
+    $(\Day{\bullet}, \Day{i})$. In this case, the residuals coincide.
+  \end{enumerate}
+  \bob{Could also say that $\eta$ preserves the monoids}
+\end{proposition}
+
+\begin{remark}
+  This is the Day construction \cite{day} restricted to the case of
+  partial orders.
+\end{remark}
+
+\begin{remark}
+  When $(A, \leq)$ is an MAV Frame, by \ref{prop:day-construction} we
+  obtain two pomonoids $(\Day{\parallel}, \Day{I})$ and
+  $(\Day{\rhd}, \Day{I})$ on $\LowerSet{A}$. Moreover, the next
+  proposition states that the duoidal relationship between these
+  monoids is preserved by the Day construction:
+\end{remark}
+
+\begin{proposition}\label{prop:lower-set-duoidal}
+  If $(\bullet, i)$ and $(\rhd, j)$ are in a duoidal relationship then
+  so are $(\Day{\bullet}, \Day{i})$ and $(\Day{\rhd}, \Day{j})$.
+\end{proposition}
+
+\subsubsection{Closed Lower Sets}
+
+\newcommand{\ClosedLowerSet}[1]{\widehat{#1}^+}
+\newcommand{\ClosedDay}[1]{\mathop{\widehat{#1}^+}}
 \newcommand{\Chu}{\mathrm{Chu}}
 \newcommand{\op}{\mathrm{op}}
+
+The Lower Set adds residuals to the pomonoids of an MAV Frame, so the
+Chu construction below will allow us to add duals to interpret all of
+the multiplicative subsystem of MAV. To incorporate the additives in
+such a way that we will be able to derive the proof normalisation
+property, we need to refine lower sets to ones that are closed under
+$+$-combinations.
+
+This corresponds to a sheaf construction, but we do not assume that
+the ``join'' operation is stable with respect to meets.
+
+The following development has proved amenable to mechanisation.
+
+Formal $+$-contexts are the semantic analogue of Horne's \emph{Killing
+  contexts}.
+
+\begin{definition}
+  Let $(A, \leq)$ be a partial order with a monotone binary operation
+  $+ : A \times A \to A$.  Let $F \in \LowerSet{A}$. A \emph{formal
+    $+$-context} over $F$ is a binary tree built from constructors
+  $\mathsf{leaf} : F \to \mathrm{ctxt}(F)$ and
+  $\mathsf{node} : \mathrm{ctxt}(F) \times \mathrm{ctxt}(F) \to
+  \mathrm{ctxt}(F)$. We define the \emph{sum} of a context as
+  $\mathit{sum}(\mathsf{leaf}~x) = x$ and
+  $\mathit{sum}(\mathsf{node}(c,d)) = \mathit{sum}(c) +
+  \mathit{sum}(d)$.
+\end{definition}
+
+\begin{remark}
+  Conceptually higher level view on contexts: if we view a lower set
+  $F$ as a monotone function $F : A^\op \to \Omega$, then we can view
+  the context construction as a relative monad on lower sets to
+  partial orders.  \bob{and this should extend to presheaves and
+    categories}.
+\end{remark}
+
+\begin{definition}
+  A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if for all
+  $c \in \mathsf{ctxt}(F)$, $\mathit{sum}(c) \in F$. $+$-closed lower
+  sets are ordered by subset inclusion and form a partial order
+  $(\ClosedLowerSet{A}, \subseteq)$.
+\end{definition}
+
+\begin{proposition}
+  There is a monotone function
+  $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ with the following
+  properties. It is a Galois reflection. FIXME
+\end{proposition}
+
+\begin{proof}
+  Explain the Agda, this relies on the fact that $\mathrm{ctxt}$ is a
+  (relative) monad.
+\end{proof}
+
+\begin{proposition}
+  $(\ClosedLowerSet{A}, \subseteq)$ has all meets and joins. In the
+  binary case, meets are defined by intersection and joins are defined
+  by $x \lor y = \alpha (U(x) \cup U(y))$.
+\end{proposition}
+
+\begin{remark}
+  Note that $\alpha$ does not preserve meets.
+\end{remark}
+
+\begin{proposition}\label{prop:closed-monoid-distrib}
+  Monoid construction 1, for monoids that distribute over $+$.
+\end{proposition}
+
+\begin{proof}
+  $\alpha$ preserves the monoidal structure, so we can use it to prove
+  the monoid laws for the constructed monoid.
+
+  Sketch why this works: we can multiply together the contexts.
+\end{proof}
+
+\begin{proposition}\label{prop:closed-monoid-duoidal}
+  For a pomonoid $(\rhd, j)$ on $(A, \leq)$, if this satisfies
+  $(w \rhd x) + (y \rhd z) \leq (w + y) \rhd (x + z)$ then the Day
+  construction
+  $F \Day{\rhd} G = \{ z \mid z \leq x \rhd y, x \in F, y \in G \}$ on
+  lower sets is $+$-closed when $F$ and $G$ are. We write
+  $F \ClosedDay{\rhd} G$ to indicate when we mean this construction as
+  an operation on $+$-closed lower sets. If $j + j \leq j$, then the
+  Day unit $\Day{j} = \eta(j)$ is also closed and we write it as
+  $\ClosedDay{j} \in \ClosedLowerSet{A}$. Together
+  $(\ClosedDay{\rhd}, \ClosedDay{j})$ form a pomonoid on
+  $(\ClosedLowerSet{A}, \subseteq)$.
+\end{proposition}
+
+\begin{proof}
+  In this case, the Day pomonoid is already closed, by use of the duoidal property.
+
+  \bob{Explain the Agda here}
+\end{proof}
+
+\begin{remark}
+  Generalising the situation for the unit $j$ in Proposition
+  \ref{prop:closed-monoid-duoidal}, $\eta(x)$ is closed for any $x$
+  such that $x + x \leq x$. Note that if $+$ were a join on
+  $(A, \leq)$, then this would automatically be satisfied.
+\end{remark}
+
+\begin{remark}
+  We have used the same decoration $\ClosedDay{\bullet}$ and
+  $\ClosedDay{\rhd}$ for two separate constructions of pomonoids on
+  $+$-closed lower sets. We will be careful to distinguish which we
+  mean: a symmetric operator like $\bullet$ 
+\end{remark}
+
+\begin{proposition}
+  Let $(\bullet, i)$ and $(\rhd, j)$ be pomonoids on $(A, \leq)$ in a
+  duoidal relationship, and assume that $(\bullet, i)$ distributes
+  over $+$ (as in Proposition \ref{prop:closed-monoid-distrib}) and
+  $(\rhd, j)$ is entropic with respect to $+$ (as in Proposition
+  \ref{prop:closed-monoid-duoidal}). Then
+  $(\ClosedDay{\bullet}, \ClosedDay{i})$ and
+  $(\ClosedDay{\rhd}, \ClosedDay{j})$ are in a duoidal relationship on
+  $(\ClosedLowerSet{A}, \subseteq)$.
+\end{proposition}
+
+\begin{proof}
+  \bob{Explain the Agda here}
+\end{proof}
+
+\subsubsection{Chu Construction}
 
@@
 simplifies to binary meets. Therefore, for this section, we let
-$(A, \leq, \bullet, \epsilon, -\kern-9pt\bullet)$ be a symmetric
-monoidal closed preorder with all binary meets.
+$(A, \leq, \bullet, i, \rightblackspoon)$ be a symmetric monoidal
+closed preorder with all binary meets.
 
 \begin{definition}
-  Let $k$ be an element of $A$. $\Chu(A, k)$ is the preorder with
-  elements comprised of pairs $(a^+, a^-)$ such that
-  $a^+ \bullet a^- \leq k$, with ordering
-  $(a^+,a^-) \sqsubseteq (b^+, b^-)$ when $a^+ \leq b^+$ and
+  Let $k$ be an element of $A$. $\Chu(A, k)$ is the partial order with
+  elements pairs $(a^+, a^-)$ such that $a^+ \bullet a^- \leq k$, with
+  ordering $(a^+,a^-) \sqsubseteq (b^+, b^-)$ when $a^+ \leq b^+$ and
   $b^- \leq a^-$.
@@
 
-\begin{theorem}
-  $\Chu(A, k)$ is a $*$-autonomous preorder with symmetric monoidal
-  structure and negation defined as:
+\begin{proposition}
+  $\Chu(A, k)$ is a $*$-autonomous partial order with pomonoid and
+  negation structure defined as:
   \begin{mathpar}
-    (a^+, a^-) \otimes (b^+, b^-) = (a^+ \bullet b^+, (b^+ \multimap a^-) \land (a^+ \multimap b^-))
+    (a^+, a^-) \otimes (b^+, b^-) = (a^+ \bullet b^+, (b^+ \rightblackspoon a^-) \land (a^+ \rightblackspoon b^-))
 
-    I = (\epsilon, k)
+    I = (i, k)
 
@@
   \end{mathpar}
-\end{theorem}
+\end{proposition}
 
-\begin{theorem}
+\begin{remark}
+  If we choose $k = i$, then $\Chu(A, i)$ is a $*$-autonomous partial
+  order that satisfies \emph{mix}.
+\end{remark}
+
+\begin{proposition}
   If $A$ has binary joins, then $\Chu(A, k)$ has binary meets, given
-  by $(a^+,a^-) \land (b^+,b^-) = (a^+ \land b^+, a^- \lor b^-)$.
-\end{theorem}
+  by $(a^+,a^-) \with (b^+,b^-) = (a^+ \land b^+, a^- \lor b^-)$.
+\end{proposition}
 
@@
 
-\subsection{Monoids on Lower Sets}
-
-Lower sets: $X : A^\op \to \Omega$.
+\begin{proposition}
+  \bob{self dual operators from pomonoids with $k \rhd k \leq k$ and $j \leq k$.}
+\end{proposition}
 
 \begin{proposition}
-  FIXME: Day construction.
+  \bob{duoidality is preserved.}
 \end{proposition}
 
-\subsection{Closure Operators on Lower Sets}
+\subsubsection{Complete Construction}
 
-need the ``preorder of elements'' $\int X$ of a lower set $X$.
-
-need trees, and their combination.
-
-% what would the category version of this look like?
-
-\begin{displaymath}
-  \mathsf{C}(X) = \{ x \mid t \in \mathrm{Tree}(\int X), x \leq \mathrm{combine}(t) \}
-\end{displaymath}
+We can now state the second main theorem of this section:
 
 \begin{theorem}
-  $\mathsf{C}$ is a closure operator. Moreover, it is lax monoidal wrt
-  to one operator, and strong monoidal wrt the other.
+  If $(F, \leq, \parallel, \rhd, I, +)$ is an MAV Frame, then
+  $\Chu(\ClosedLowerSet{F}, I)$ has the structure of an MAV Algebra.
 \end{theorem}
+
+\begin{proof}
+  Combining all the propositions above.
+\end{proof}

### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] more semantics

@@
   An \emph{MAV Algebra} is a structure
-  $(A, \leq, \otimes, \rhd, I, \lnot)$ with the following properties:
+  $(A, \leq, \otimes, ;, I, \lnot)$ with the following properties:
   \begin{enumerate}
   \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
-  \item $(A, \leq, \rhd, I)$ is a pomonoid.
-  \item $(\otimes, I)$ and $(\rhd, I)$ are in a duoidal relationship.
+  \item $(A, \leq, ;, I)$ is a pomonoid.
+  \item $(\otimes, I)$ and $(;, I)$ are in a duoidal relationship.
   \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
@@
   properties. It is a Galois reflection. FIXME
+
+  \begin{displaymath}
+    \alpha(F) = \{ x \mid c \in \mathrm{ctxt}(F), x \leq \mathit{sum}(c) \}
+  \end{displaymath}
 \end{proposition}
@@
 \end{proof}
+
+\begin{remark}
+  By this proposition, $U \circ \alpha$ is a closure operator on
+  $\LowerSet{A}$ \cite{davey-priestley}, and the closed elements are
+  those of $\ClosedLowerSet{A}$. The next proposition is standard for
+  showing that meets and joins exist on the closed elements for some
+  closure operator.
+\end{remark}
 
@@
 
-  Sketch why this works: we can multiply together the contexts.
+  \bob{Sketch why this works: we can multiply together the contexts.}
 \end{proof}
@@
 \begin{proof}
-  In this case, the Day pomonoid is already closed, by use of the duoidal property.
-
   \bob{Explain the Agda here}
@@
   $+$-closed lower sets. We will be careful to distinguish which we
-  mean: a symmetric operator like $\bullet$ 
+  mean: a symmetric operator like $\bullet$ will distribute over $+$
+  and so $\ClosedDay{\bullet}$ will be constructed by Proposition
+  \ref{prop:closed-monoid-distrib}; and a non-symmetric operator like
+  $\rhd$ will be entropic with respect to $+$ and so
+  $\ClosedDay{\rhd}$ will be constructed by Proposition
+  \ref{prop:closed-monoid-duoidal}.
+\end{remark}
+
+\begin{remark}
+  If we have two $(A, \leq)$ pomonoids with the same unit, then the
+  two constructions will yield the same closed lower set.
+  \bob{elaborate a bit...}
 \end{remark}
@@
 
-The Chu construction allows us to state
-directly that any operator we define on $\Chu(A, k)$ is self dual by
-defining as the same
+\begin{proposition}\label{prop:chu-self-dual}
+  Let $(\rhd, j)$ be a pomonoid on $(A, \leq)$ such that
+  $k \rhd k \leq k$ and $j \leq k$, then
+  $x ; y = (x^+ \rhd y^+, x^- \rhd y^-)$ and $J = (j, j)$ form a
+  self-dual pomonoid on $\Chu(A, k)$.
+\end{proposition}
+
+\begin{proof}
+  \bob{show that that two extra bits are needed.}
+\end{proof}
+
+\begin{remark}
+  When $k = j$, the two conditions in the proposition are
+  automatically satisfied. Moreover, if $k = i = j$, then not only
+  does the $*$-autonomous structure satisfy \emph{mix}, but we also
+  have $I =J$.
+\end{remark}
 
 \begin{proposition}
-  \bob{self dual operators from pomonoids with $k \rhd k \leq k$ and $j \leq k$.}
+  If $(\bullet, i)$ and $(\rhd, j)$ are in a duoidal relationship on
+  $(A, \leq)$, and $(\rhd, j)$ satisfies the conditions of Proposition
+  \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(;, J)$ are in a
+  duoidal relationship on $\Chu(A, k)$.
 \end{proposition}
 
-\begin{proposition}
-  \bob{duoidality is preserved.}
-\end{proposition}
+\begin{proof}
+  \bob{Explain the Agda}
+\end{proof}
 
-\subsubsection{Complete Construction}
-
-We can now state the second main theorem of this section:
+\subsection{Construction of MAV-algebras}
 
@@
 \begin{proof}
-  Combining all the propositions above.
+  Combining all the propositions above, in the special case when some
+  of the units collapse.
 \end{proof}

### 2024-03-25 doc/sections/introduction.tex
Intro

@@
 
-We present an algebraic semantics and semantic proof of cut elimination for the multiplicative-additive deep inference calculus MAV~\cite{Horne15:mav}, an extension of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll} with a self-dual non-commutative connective.
+We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive deep inference calculus MAV~\cite{Horne15:mav}, an extension of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll} with a self-dual non-commutative connective.
 
@@
 Eventually, Guglielmi's attempts yielded the basic deep inference calculus, BV~\cite{Guglielmi99:bv,Guglielmi07:sis}, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that does capture sequential composition.
-Such a connective was already present in Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence spaces~\cite[Chapter 8]{GirardTL89:proofs}, which are a semantics for proofs of linear logic.
+Such a connective was already present in Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence spaces~\cite[\C8]{GirardTL89:proofs}, which are a semantic model of linear logic.
 While BV is similar to Pomset logic, the two are not the same.
 Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that the theorems of BV are a proper subset of the theorems of Pomset logic.
+Neither BV nor Pomset logic has a sequent calculus. In fact, Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.
 
-% Neither BV nor Pomset logic has a sequent calculus.
-% ~\cite{Tiu06:sisii}
+MAV extends BV with the additives of MALL.
+Horne~\cite{Horne15:mav} gave a syntactic proof of cut-elimination.
+We present an alternative proof of cut-elimination via a semantic model.
+This proof avoids some of the intrincate syntactic reasoning in Horne's proof and is more modular, as shown by the extensions we present in \cref{sec:mav-extensions}.
 
-\begin{itemize}
-      \item BV~\cite{Guglielmi07:sis} by Guglielmi is an extension of MLL inspired by process algebras such as CCSand Pomset Logic~\cite{Retore97:pomset}.
-      \item MAV by Hornes~\cite{Horne15:mav} extends BV with the additives.
-      \item BV adds a non-commutative connective to MLL. Such a connective can be motivated by coherence spaces, or by session types.
-      \item A shallow sequent calculus cannot capture BV~\cite{Tiu06:sisii}.
-      \item To make sure that a proof system makes sense, we need some kind
-            of Cut-elimination theorem that ensures that all proofs can be
-            placed into a normal form where it is evident that it is not
-            possible to derive all results.
-\end{itemize}
+The technique of cut-elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the phase space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
+The completeness of this model directly yields the existence of a cut-free proof for every proof constructible in the MALL sequent calculus.
+The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and by Frumin~\cite{Frumin22:psc} for bunched implications.
 
-MAV is defined by Horne \cite{Horne15:mav}, who gave a syntactic proof
-of cut-elimination and the admissibility of several other rules. We
-provide an alternative proof of cut-elimination via a semantic
-model. This proof avoids some of the intrincate syntactic reasoning in
-Horne's proof and is more modular, as evidenced by the extensions we
-present in \autoref{sec:mav-extensions}.
-
-Cut-elimination for MALL by construction of a semantic model is due to
-Okada \cite{Okada99:psc}, who shows that the a Phase Space model of
-MALL (described by Girard \cite{Girard87:ll} and Troelstra
-\cite{TroelstraXX:lnll}) can be constructed from cut-proof proofs. The
-completeness of this model directly yields the existence of a cut-free
-proof for every proof constructible in the MALL sequent calculus. For
-MAV, we cannot use Phase Spaces due to the
-
-The same technique has been used for MALL with fixpoints (CITE:
-Saurin) and for Bunched Implications with extensions (CITE: Frumin).
+For MAV, we cannot use the phase space model, due to the presence of the self-dual connective.

### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] more semantics

@@
 \begin{remark}
-  In the case when the two pomonoids share a common unit (as in MAV),
-  the last three conditions for a duoidal relationship are
-  automatically satisfied.
+  In the case when the two pomonoids share a common unit the last
+  three conditions for a duoidal relationship are automatically
+  satisfied.
 \end{remark}
 
-\subsection{MAV Algebras}
+\bob{need to define \emph{entropy} and \emph{entropic} somewhere}
+
+\subsection{MAV-algebras}
 
 \begin{definition}
-  An \emph{MAV Algebra} is a structure
+  An \emph{MAV-algebra} is a structure
   $(A, \leq, \otimes, ;, I, \lnot)$ with the following properties:
@@
 \begin{definition}\label{defn:mav-interpretation}
-  Let $\mathit{At}$ be a set of atomic propositions. Given an MAV
-  Algebra $(A, \leq, \otimes, \rhd, I, \lnot)$ and valuation
-  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas as follows:
+  Let $\mathit{At}$ be a set of atomic propositions. Given an
+  MAV-algebra $(A, \leq, \otimes, \rhd, I, \lnot)$ and valuation
+  $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
+  as follows:
   \begin{mathpar}
@@
 
-\subsection{MAV Frames}
+\subsection{MAV-frames}
 
 To prove completeness of the cut-free fragment of SMAV, we will
-construct a particular MAV Algebra from the syntax and cut-free
+construct a particular MAV-algebra from the syntax and cut-free
 proofs. Since cut-free proofs do not a priori have all the necessary
-structure for an MAV Algebra, we develop a procedure to construct MAV
-Algebra from the lighter requirements of an MAV Frame, defined in this
-section. MAV Frames have an intuitive reading as a kind of process
-algebra, so we use process algebra-like notation. In the following
-sections, we show how every MAV Frame induces an MAV Algebra, and in
-Section XXX we will show that the MAV Algebra constructed from the
-cut-free proof MAV Frame allows us to prove that all proofs in SMAV
-have cut-free normal forms.
+structure for an MAV-algebra, we develop a procedure to construct
+MAV-algebra from the lighter requirements of an MAV-frame, defined in
+this section. MAV-frames have an intuitive reading as a kind of
+process algebra, so we use process algebra-like notation. In the
+following sections, we show how every MAV-frame induces an
+MAV-algebra, and in Section XXX we will show that the MAV-algebra
+constructed from the cut-free proof MAV-frame allows us to prove that
+all proofs in SMAV have cut-free normal forms.
 
 \begin{definition}
-  An \emph{MAV Frame} is a structure
+  An \emph{MAV-frame} is a structure
   $(F, \leq, I, \parallel, \rhd, +)$ where $(F, \leq)$ is a partial
@@
   \bob{A frame is nearly two duoidal structures, except that we don't
-    assume that $+$ is a monoid, nor is there a unit element for it.}
+    assume that $+$ is a monoid, nor is there a unit element for
+    it. If we assumed that $+$ was a lattice join, then (iii) and (iv)
+    would automatically be true. We do not include this because these
+    facts are not true for the cut-free MAV system.}
 \end{remark}
@@
 \begin{proposition}
-  \bob{The Cut-free system forms an MAV Frame; fwd ref to next section}
+  \bob{The Cut-free system forms an MAV-frame; fwd ref to next section}
 \end{proposition}
 
-\subsection{Constructing MAV Algebras from MAV Frames}
+\subsection{Constructing MAV-algebras from MAV-frames}
 
 \newcommand{\LowerSet}[1]{\widehat{#1}}
+\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
 
@@
 \end{proposition}
-
-\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
 
@@
 \begin{remark}
-  When $(A, \leq)$ is an MAV Frame, by \ref{prop:day-construction} we
+  When $(A, \leq)$ is an MAV-frame, by \ref{prop:day-construction} we
   obtain two pomonoids $(\Day{\parallel}, \Day{I})$ and
@@
 
-The Lower Set adds residuals to the pomonoids of an MAV Frame, so the
+The Lower Set adds residuals to the pomonoids of an MAV-frame, so the
 Chu construction below will allow us to add duals to interpret all of
@@
 \begin{proposition}\label{prop:closed-monoid-distrib}
-  Monoid construction 1, for monoids that distribute over $+$.
+  \bob{Monoid construction 1, for monoids that distribute over
+    $+$. This also has a residual.}
 \end{proposition}
@@
 
-To construct suitable MAV Algebras, we use the poset version of the
+To construct suitable MAV-algebras, we use the poset version of the
 Chu construction \cite{barr}. The Chu construction builds
@@
 \begin{theorem}
-  If $(F, \leq, \parallel, \rhd, I, +)$ is an MAV Frame, then
-  $\Chu(\ClosedLowerSet{F}, I)$ has the structure of an MAV Algebra.
+  If $(F, \leq, \parallel, \rhd, I, +)$ is an MAV-frame, then
+  $\Chu(\ClosedLowerSet{F}, I)$ has the structure of an MAV-algebra.
 \end{theorem}

### 2024-03-25 doc/sections/introduction.tex
Enough intro for now.
Minor edits

@@
 
-Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems which arose from Guglielmi's attempts to relate process algebras~\cite[CCS]{Milner89:CC,Milner80:CCS} to linear logic~\cite{Girard87:ll}.
+Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebras~\cite[CCS]{Milner80:CCS,Milner89:CC} to linear logic~\cite{Girard87:ll}.
 The problem is that, while the connectives of linear logic capture parallel composition, no connective captures \emph{sequential composition}.
-Eventually, Guglielmi's attempts yielded the basic deep inference calculus, BV~\cite{Guglielmi99:bv,Guglielmi07:sis}, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that does capture sequential composition.
+Eventually, Guglielmi's attempts yielded the basic deep inference calculus, BV\footnote{
+      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pair production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
+}~\cite{Guglielmi99:bv,Guglielmi07:sis}, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
 Such a connective was already present in Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence spaces~\cite[\C8]{GirardTL89:proofs}, which are a semantic model of linear logic.
-While BV is similar to Pomset logic, the two are not the same.
-Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that the theorems of BV are a proper subset of the theorems of Pomset logic.
+Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
 Neither BV nor Pomset logic has a sequent calculus. In fact, Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.
@@
 For MAV, we cannot use the phase space model, due to the presence of the self-dual connective.
+\wen{%
+      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}

### 2024-03-25 doc/sections/introduction.tex
[ tex ] some todos and comments

@@
       I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
+\bob{I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely.
+So I think it is unlikely that phase spaces can be adapted to BV.}

### 2024-03-25 doc/sections/introduction.tex
Minor rewrites in intro

@@
 
-We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive deep inference calculus MAV~\cite{Horne15:mav}, an extension of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll} with a self-dual non-commutative connective.
+We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
+      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pair production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
+}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
 
-Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebras~\cite[CCS]{Milner80:CCS,Milner89:CC} to linear logic~\cite{Girard87:ll}.
-The problem is that, while the connectives of linear logic capture parallel composition, no connective captures \emph{sequential composition}.
-Eventually, Guglielmi's attempts yielded the basic deep inference calculus, BV\footnote{
-      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pair production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
-}~\cite{Guglielmi99:bv,Guglielmi07:sis}, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
-Such a connective was already present in Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence spaces~\cite[\C8]{GirardTL89:proofs}, which are a semantic model of linear logic.
+MAV and BV are \emph{deep inference} systems.
+Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to linear logic~\cite{Girard87:ll}.
+The problem with such a relation is that, while the multiplicative connectives of linear logic capture parallel composition, no connective of linear logic captures \emph{sequential composition}.
+Eventually, Guglielmi's attempts yielded BV, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
+Such a connective was already present in another extension of linear logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of linear logic~\cite[\C8]{GirardTL89:proofs}.
 Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
-Neither BV nor Pomset logic has a sequent calculus. In fact, Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.
+Neither BV nor Pomset logic has a sequent calculus. Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.
 
-MAV extends BV with the additives of MALL.
-Horne~\cite{Horne15:mav} gave a syntactic proof of cut-elimination.
+Horne~\cite{Horne15:mav} gave a syntactic proof of cut-elimination for MAV.
 We present an alternative proof of cut-elimination via a semantic model.

### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] some todos and comments
[ tex ] more semantics

@@
 \section{Semantics}\label{sec:mav-semantics}
+
+\newcommand{\LowerSet}[1]{\widehat{#1}}
+\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
+\newcommand{\ClosedLowerSet}[1]{\widehat{#1}^+}
+\newcommand{\ClosedDay}[1]{\mathop{\widehat{#1}^+}}
+\newcommand{\Chu}{\mathrm{Chu}}
+\newcommand{\op}{\mathrm{op}}
 
@@
 \begin{definition}
-  A \emph{$*$-autonomous partial order} is ... TODO
-
+  A \emph{$*$-autonomous partial order} is a structure
+  $(A, \leq, \otimes, I, \lnot)$ where $(\otimes, I)$ is a pomonoid on
+  $(A, \leq)$ and $\lnot : A^\op \to A$ is an anti-monotone and
+  involutive operator on $A$, together satisfying
+  $x \otimes y \leq \lnot z$ iff $x \leq \lnot (y \otimes z)$.  A
+  $*$-autonomous partial order satisfies \emph{mix} if $\lnot I = I$.
 \end{definition}
@@
   immediate consequences, but we leave description of these until
-  after the definition of MAV algebra below. \bob{because there are
+  after the definition of MAV-algebra below. \bob{because there are
     even more consequences in the presence of additive and duoidal
@@
 FIXME: cite that combinatorics book.
+
+\bob{need to define \emph{entropy} and \emph{entropic} somewhere}
+
 \begin{definition}
@@
 
-\bob{need to define \emph{entropy} and \emph{entropic} somewhere}
+\begin{remark}
+  If $\bullet$ is a join, or $\rhd$ is a meet, then all the conditions
+  for a duoidal relationship are automatically met for any other
+  monoid. \bob{fwd ref to where we use this.}
+\end{remark}
+
+\begin{remark}
+  The duoidal relationship is not symmetric.
+\end{remark}
 
@@
 \begin{proposition}\label{prop:mav-algebra-consequences}
-  \bob{Consequences of the definition, as listed in the Agda}
+  Let $(A, \leq, \otimes, ;, I, \lnot)$ be a MAV-algebra.
+  \begin{enumerate}
+  \item There is another pomonoid structure $(\parr, I)$ on
+    $(A, \leq)$, defined as
+    $x \parr y = \lnot(\lnot x \otimes \lnot y)$.
+  \item $(\otimes, I)$ and $(\parr, I)$ are linearly distributive
+    \cite{cockett}:
+    $x \otimes (y \parr z) \leq (x \otimes y) \parr z$.
+  \item $(A, \leq)$ has binary joins, given by
+    $x \oplus y = \lnot (\lnot x \with \lnot y)$.
+  \item $\oplus$ distributes over $\otimes$:
+    $x \otimes (y \oplus z) = ((x \otimes y) \oplus (x \otimes z)$.
+  \item $\with$ distributes over $\parr$:
+    $(x \parr z) \with (y \parr z) = (x \with y) \parr z$.
+  \item $;$ is entropic over $\parr$:
+    $(w \parr x); (y \parr z) \leq (w;y) \parr (x;z)$.
+  \item $;$ is entropic over $\with$:
+    $(w \with x); (y \with z) \leq (w ; y) \with (x; z)$.
+  \item $\oplus$ is entropic over $;$:
+    $(w ; x) \oplus (y ; z) \leq (x \oplus y) ; (x \oplus z)$.
+  \end{enumerate}
 \end{proposition}
+
+\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
 
@@
   $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
-  as follows:
-  \begin{mathpar}
-    FIXME
-  \end{mathpar}
+  as follows: $\sem{\vUnit} = I$, $\sem{a} = V(a)$,
+  $\sem{\vDual a} = \lnot V(a)$,
+  $\sem{\vP\vTens\vQ} = \sem{\vP} \otimes \sem{\vQ}$,
+  $\sem{\vP\vParr\vQ} = \sem{\vP} \parr \sem{\vQ}$,
+  $\sem{\vP\vSeq\vQ} = \sem{\vP};\sem{\vQ}$,
+  $\sem{\vP\vWith\vQ} = \sem{\vP} \with \sem{\vQ}$, and
+  $\sem{\vP\vPlus\vQ} = \sem{\vP} \oplus \sem{\vQ}$.
 \end{definition}
+
+\begin{lemma}
+  For all $\vP$, $\sem{\vDual{\vP}} = \lnot \sem{\vP}$.
+\end{lemma}
 
@@
   \ref{defn:mav-interpretation} is sound: for all formulas $P$, if
-  $P \longrightarrow^* I$, then $I \leq \llbracket P \rrbracket$.
+  $P \longrightarrow^* I$, then $I \leq \sem{P}$.
 \end{theorem}
@@
 
-\newcommand{\LowerSet}[1]{\widehat{#1}}
-\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
-
 \bob{Some introductory text here: explain the steps in the construction and what each one adds.}
 
-\subsubsection{Lower Sets}
+\subsubsection{Lower Sets and Day pomonoids}
 
@@
 \subsubsection{Closed Lower Sets}
-
-\newcommand{\ClosedLowerSet}[1]{\widehat{#1}^+}
-\newcommand{\ClosedDay}[1]{\mathop{\widehat{#1}^+}}
-\newcommand{\Chu}{\mathrm{Chu}}
-\newcommand{\op}{\mathrm{op}}
 
@@
 
+\begin{lemma}
+  \bob{entropy on residuals}
+\end{lemma}
+
 \begin{proposition}

### 2024-03-25 doc/sections/introduction.tex
Gave it a shot

@@
 
-For MAV, we cannot use the phase space model, due to the presence of the self-dual connective.
+The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
+The phase space model defines duals by means of double negation with respect to the monoidal structure, which means that attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
 \wen{%
       I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
-\bob{I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely.
+\bob{%
+      I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely.
 So I think it is unlikely that phase spaces can be adapted to BV.}
+\wen{%
+      Gave it a shot.}

### 2024-03-25 doc/sections/introduction.tex
Add remark

@@
 We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
-      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pair production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
+      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
 }~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.

### 2024-03-25 doc/sections/mav-syntax.tex
Minor edits
Minor rewrites in intro
Add remark

@@
-\section{Multiplicative-Additive System Virtual}\label{sec:mav-syntax}
+\section{The system MAV}\label{sec:mav-syntax}
 
-\begin{itemize}
-  \item Structural equivalences are explicit.
-  \item Inference is a congruence.
-  \item Inference rules are unary.
-  \item Relate to usual presentation of MALL.
-  \item Relate to usual presentation of BV.
-\end{itemize}
-
-Formulas:
+The structures of MAV are formed from positive and negative atoms ($\vPos\vA$ and $\vNeg\vA$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
 \begin{displaymath}
-  \vP,\vQ
+  \vP,\vQ,\vR,\vS
   \Coloneq \vPos\vA
@@
 \end{displaymath}
-
-Negation:
+Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective seq.
 \begin{displaymath}
@@
 \end{displaymath}
+
+\begin{itemize}
+  \item Structural equivalences are explicit.
+  \item Inference is a congruence.
+  \item Inference rules are unary.
+  \item Relate to usual presentation of MALL.
+  \item Relate to usual presentation of BV.
+\end{itemize}
 
@@
 We write $\vInfer*$ for the reflexive, transitive closure of $\vInfer$.
+
+\begin{remark}
+  In the usual presentation of BV, the structure connectives are written as lists of structures, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
+\end{remark}

### 2024-03-25 doc/sections/mav-syntax.tex
About to flip that triangle

@@
     \vDual{\vP\vPlus\vQ} & \vDual\vP \vWith \vDual\vQ
+  \end{array}
+\end{displaymath}
+
+Equivalences:
+\begin{displaymath}
+  \begin{array}{
+      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
+      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
+      l@{\;\vEquiv\;}ll}
+    \vP\vSeq\vUnit
+     & \vP
+     & \RuleLabel*[seq-runit]{\vSeq-Unit\textsuperscript{R}}
+     &
+    \vUnit\vSeq\vP
+     & \vP
+     & \RuleLabel*[seq-lunit]{\vSeq-Unit\textsuperscript{L}}
+     &
+    \vP\vSeq(\vQ\vSeq\vR)
+     & (\vP\vSeq\vQ)\vSeq\vP
+     & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
+    \\
+    \vP\vTens\vUnit
+     & \vP
+     & \RuleLabel*[tens-unit]{\vTens-Unit}
+     &
+    \vP\vTens\vQ
+     & \vQ\vTens\vP
+     & \RuleLabel*[tens-comm]{\vTens-Comm}
+     &
+    \vP\vTens(\vQ\vTens\vR)
+     & (\vP\vTens\vQ)\vTens\vP
+     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
+    \\
+    \vP\vParr\vUnit
+     & \vP
+     & \RuleLabel*[parr-unit]{\vParr-Unit}
+     &
+    \vP\vParr\vQ
+     & \vQ\vParr\vP
+     & \RuleLabel*[parr-comm]{\vParr-Comm}
+     &
+    \vP\vParr(\vQ\vParr\vR)
+     & (\vP\vParr\vQ)\vParr\vP
+     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
   \end{array}
@@
 
-Equivalence rules:
-\begin{displaymath}
-  \begin{array}{
-      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
-      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
-      l@{\;\vEquiv\;}ll}
-    \vP\vSeq\vUnit
-     & \vP
-     & \RuleLabel*[seq-runit]{\vSeq-Unit\textsuperscript{R}}
-     &
-    \vUnit\vSeq\vP
-     & \vP
-     & \RuleLabel*[seq-lunit]{\vSeq-Unit\textsuperscript{L}}
-     &
-    \vP\vSeq(\vQ\vSeq\vR)
-     & (\vP\vSeq\vQ)\vSeq\vP
-     & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
-    \\
-    \vP\vTens\vUnit
-     & \vP
-     & \RuleLabel*[tens-unit]{\vTens-Unit}
-     &
-    \vP\vTens\vQ
-     & \vQ\vTens\vP
-     & \RuleLabel*[tens-comm]{\vTens-Comm}
-     &
-    \vP\vTens(\vQ\vTens\vR)
-     & (\vP\vTens\vQ)\vTens\vP
-     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
-    \\
-    \vP\vParr\vUnit
-     & \vP
-     & \RuleLabel*[parr-unit]{\vParr-Unit}
-     &
-    \vP\vParr\vQ
-     & \vQ\vParr\vP
-     & \RuleLabel*[parr-comm]{\vParr-Comm}
-     &
-    \vP\vParr(\vQ\vParr\vR)
-     & (\vP\vParr\vQ)\vParr\vP
-     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
-  \end{array}
-\end{displaymath}
-
 We write $\vEquiv$ for invertible inference rules, \ie $\vP\vEquiv\vQ$ means $\vP\vInfer\vQ$ and $\vQ\vInfer\vP$.
@@
 \begin{remark}
-  In the usual presentation of BV, the structure connectives are written as lists of structures, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
+  The usual presentation of BV writes the structure connectives as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
 \end{remark}

### 2024-03-25 doc/sections/mav-semantics.tex
Flip the triangle

@@
 \begin{definition}
-  Two pomonoids $(\bullet, i)$ and $(\rhd, j)$ on a partial order
+  Two pomonoids $(\bullet, i)$ and $(\lhd, j)$ on a partial order
   $(A, \leq)$ are in a \emph{duoidal} relationship if the following
@@
   \begin{enumerate}
-  \item $(w \rhd x) \bullet (y \rhd z) \leq (w \bullet y) \rhd (x \bullet z)$
+    \item $(w \lhd x) \bullet (y \lhd z) \leq (w \bullet y) \lhd (x \bullet z)$
     \item $j \bullet j \leq j$
-  \item $i \leq i \rhd i$
+    \item $i \leq i \lhd i$
     \item $i \leq j$
@@
 \begin{remark}
-  If $\bullet$ is a join, or $\rhd$ is a meet, then all the conditions
+  If $\bullet$ is a join, or $\lhd$ is a meet, then all the conditions
   for a duoidal relationship are automatically met for any other
@@
   Let $\mathit{At}$ be a set of atomic propositions. Given an
-  MAV-algebra $(A, \leq, \otimes, \rhd, I, \lnot)$ and valuation
+  MAV-algebra $(A, \leq, \otimes, \lhd, I, \lnot)$ and valuation
   $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
@@
   An \emph{MAV-frame} is a structure
-  $(F, \leq, I, \parallel, \rhd, +)$ where $(F, \leq)$ is a partial
+  $(F, \leq, I, \parallel, \lhd, +)$ where $(F, \leq)$ is a partial
   order, $(F, \leq, I, \parallel)$ is a commutative pomonoid,
-  $(F, \leq, I, \rhd)$ is a pomonoid, $+$ is a binary monotone
+  $(F, \leq, I, \lhd)$ is a pomonoid, $+$ is a binary monotone
   function on $(F, \leq)$, and these structures satisfy the following
@@
   \begin{enumerate}
-  \item $(w \rhd x) \parallel (y \rhd z) \leq (w \parallel y) \rhd (x \parallel z)$
+    \item $(w \lhd x) \parallel (y \lhd z) \leq (w \parallel y) \lhd (x \parallel z)$
     \item $(x + y) \parallel z \leq (x \parallel z) + (y \parallel z)$
-  \item $(w \rhd x) + (y \rhd z) \leq (w + y) \rhd (x + z)$
+    \item $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$
     \item $I + I \leq I$
@@
   obtain two pomonoids $(\Day{\parallel}, \Day{I})$ and
-  $(\Day{\rhd}, \Day{I})$ on $\LowerSet{A}$. Moreover, the next
+  $(\Day{\lhd}, \Day{I})$ on $\LowerSet{A}$. Moreover, the next
   proposition states that the duoidal relationship between these
@@
 \begin{proposition}\label{prop:lower-set-duoidal}
-  If $(\bullet, i)$ and $(\rhd, j)$ are in a duoidal relationship then
-  so are $(\Day{\bullet}, \Day{i})$ and $(\Day{\rhd}, \Day{j})$.
+  If $(\bullet, i)$ and $(\lhd, j)$ are in a duoidal relationship then
+  so are $(\Day{\bullet}, \Day{i})$ and $(\Day{\lhd}, \Day{j})$.
 \end{proposition}
@@
 \begin{proposition}\label{prop:closed-monoid-duoidal}
-  For a pomonoid $(\rhd, j)$ on $(A, \leq)$, if this satisfies
-  $(w \rhd x) + (y \rhd z) \leq (w + y) \rhd (x + z)$ then the Day
+  For a pomonoid $(\lhd, j)$ on $(A, \leq)$, if this satisfies
+  $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$ then the Day
   construction
-  $F \Day{\rhd} G = \{ z \mid z \leq x \rhd y, x \in F, y \in G \}$ on
+  $F \Day{\lhd} G = \{ z \mid z \leq x \lhd y, x \in F, y \in G \}$ on
   lower sets is $+$-closed when $F$ and $G$ are. We write
-  $F \ClosedDay{\rhd} G$ to indicate when we mean this construction as
+  $F \ClosedDay{\lhd} G$ to indicate when we mean this construction as
   an operation on $+$-closed lower sets. If $j + j \leq j$, then the
@@
   $\ClosedDay{j} \in \ClosedLowerSet{A}$. Together
-  $(\ClosedDay{\rhd}, \ClosedDay{j})$ form a pomonoid on
+  $(\ClosedDay{\lhd}, \ClosedDay{j})$ form a pomonoid on
   $(\ClosedLowerSet{A}, \subseteq)$.
@@
   We have used the same decoration $\ClosedDay{\bullet}$ and
-  $\ClosedDay{\rhd}$ for two separate constructions of pomonoids on
+  $\ClosedDay{\lhd}$ for two separate constructions of pomonoids on
   $+$-closed lower sets. We will be careful to distinguish which we
@@
   \ref{prop:closed-monoid-distrib}; and a non-symmetric operator like
-  $\rhd$ will be entropic with respect to $+$ and so
-  $\ClosedDay{\rhd}$ will be constructed by Proposition
+  $\lhd$ will be entropic with respect to $+$ and so
+  $\ClosedDay{\lhd}$ will be constructed by Proposition
   \ref{prop:closed-monoid-duoidal}.
@@
 \begin{proposition}
-  Let $(\bullet, i)$ and $(\rhd, j)$ be pomonoids on $(A, \leq)$ in a
+  Let $(\bullet, i)$ and $(\lhd, j)$ be pomonoids on $(A, \leq)$ in a
   duoidal relationship, and assume that $(\bullet, i)$ distributes
   over $+$ (as in Proposition \ref{prop:closed-monoid-distrib}) and
-  $(\rhd, j)$ is entropic with respect to $+$ (as in Proposition
+  $(\lhd, j)$ is entropic with respect to $+$ (as in Proposition
   \ref{prop:closed-monoid-duoidal}). Then
   $(\ClosedDay{\bullet}, \ClosedDay{i})$ and
-  $(\ClosedDay{\rhd}, \ClosedDay{j})$ are in a duoidal relationship on
+  $(\ClosedDay{\lhd}, \ClosedDay{j})$ are in a duoidal relationship on
   $(\ClosedLowerSet{A}, \subseteq)$.
@@
 interpret the self-dual $P; Q$ connective. Let us assume that we have
-an operation $-\rhd- : A \times A \to A$ that we want to induce
+an operation $-\lhd- : A \times A \to A$ that we want to induce
 self-dual operator on $\Chu(A, k)$. By the way the Chu construction is
@@
 \begin{displaymath}
-  (a^+, a^-) ; (b^+, b^-) = (a^+ \rhd b^+, a^- \rhd b^-)
+  (a^+, a^-) ; (b^+, b^-) = (a^+ \lhd b^+, a^- \lhd b^-)
 \end{displaymath}
@@
 And that the dualising object $k$ is a
-satisfies $k \rhd k \leq k$. If $\rhd$ has a unit $j$, then $(j, j)$ is a unit if
+satisfies $k \lhd k \leq k$. If $\lhd$ has a unit $j$, then $(j, j)$ is a unit if
 
 \begin{proposition}\label{prop:chu-self-dual}
-  Let $(\rhd, j)$ be a pomonoid on $(A, \leq)$ such that
-  $k \rhd k \leq k$ and $j \leq k$, then
-  $x ; y = (x^+ \rhd y^+, x^- \rhd y^-)$ and $J = (j, j)$ form a
+  Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that
+  $k \lhd k \leq k$ and $j \leq k$, then
+  $x ; y = (x^+ \lhd y^+, x^- \lhd y^-)$ and $J = (j, j)$ form a
   self-dual pomonoid on $\Chu(A, k)$.
@@
 \begin{proposition}
-  If $(\bullet, i)$ and $(\rhd, j)$ are in a duoidal relationship on
-  $(A, \leq)$, and $(\rhd, j)$ satisfies the conditions of Proposition
+  If $(\bullet, i)$ and $(\lhd, j)$ are in a duoidal relationship on
+  $(A, \leq)$, and $(\lhd, j)$ satisfies the conditions of Proposition
   \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(;, J)$ are in a
@@
 \begin{theorem}
-  If $(F, \leq, \parallel, \rhd, I, +)$ is an MAV-frame, then
+  If $(F, \leq, \parallel, \lhd, I, +)$ is an MAV-frame, then
   $\Chu(\ClosedLowerSet{F}, I)$ has the structure of an MAV-algebra.

### 2024-03-25 doc/sections/mav-syntax.tex
Stopping mid sentence

@@
 \end{displaymath}
-
-Equivalences:
+Structures are considered equivalent module the syntactic equivalence relation $\vEquiv$, which is the smallest equivalence relation that contains the following equivalences:
 \begin{displaymath}
@@
 \end{displaymath}
+Such an equivalence is not unusual for proof systems, \eq most proof systems consider structures equivalent
 

### 2024-03-26 doc/sections/mav-semantics.tex
[ tex ] semantics semantics semantics

@@
   pomonoid where additionally $x \bullet y = y \bullet x$.
+\end{definition}
+
+\begin{definition}
+  \bob{residuation}
 \end{definition}
@@
   \item $(A, \leq, ;, I)$ is a pomonoid.
-    \item $(\otimes, I)$ and $(;, I)$ are in a duoidal relationship.
+  \item $;$ is self dual: $\lnot (x ; y) = (\lnot x); (\lnot y)$.
+  \item $(\otimes, I)$ is duoidal over $(;, I)$.
   \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
@@
 To prove completeness of the cut-free fragment of SMAV, we will
-construct a particular MAV-algebra from the syntax and cut-free
+construct a particular MAV-algebra from the formulas and cut-free
 proofs. Since cut-free proofs do not a priori have all the necessary
@@
   $(F, \leq, I, \lhd)$ is a pomonoid, $+$ is a binary monotone
-  function on $(F, \leq)$, and these structures satisfy the following
+  function on $(F, \leq)$, and these data satisfy the following
   inequalities:
@@
 \begin{proposition}
-  \bob{The Cut-free system forms an MAV-frame; fwd ref to next section}
+  The \emph{cut-free MAV-frame} $\textsc{CFMav}$ is the partial order
+  arising as the quotient of the preorder formed from the formulas of
+  MAV and $P \leq Q$ if $P \longrightarrow^* Q$. Define
+  $P \parallel Q = P \vParr Q$, $P \lhd Q = P \vSeq Q$,
+  $P + Q = P \vWith Q$ and $I = \vUnit$. The required (in)equalities
+  follow directly from the definition of $\longrightarrow^*$.
 \end{proposition}
+
+\begin{remark}
+  The construction of the MAV-frame \textsc{CFMav} does not use the
+  $\otimes$ and $\oplus$ structure of MAV directly. We will see in
+  Section \ref{sec:mav-cut-elimination} that this structure is
+  recovered by duality from the other connectives by the constructions
+  in the rest of this section. \bob{Which one is ``positive'' again?}
+\end{remark}
 
@@
 
-Formal $+$-contexts are the semantic analogue of Horne's \emph{Killing
+$+$-contexts are the semantic analogue of Horne's \emph{Killing
   contexts}.
@@
   Let $(A, \leq)$ be a partial order with a monotone binary operation
-  $+ : A \times A \to A$.  Let $F \in \LowerSet{A}$. A \emph{formal
-    $+$-context} over $F$ is a binary tree built from constructors
+  $+ : A \times A \to A$.  Let $F \in \LowerSet{A}$. A
+  \emph{$+$-context} over $F$ is a binary tree built from constructors
   $\mathsf{leaf} : F \to \mathrm{ctxt}(F)$ and
@@
   binary case, meets are defined by intersection and joins are defined
-  by $x \lor y = \alpha (U(x) \cup U(y))$.
+  by $F \lor G = \alpha (U F \cup U G)$.
 \end{proposition}
@@
 \begin{proposition}\label{prop:closed-monoid-distrib}
-  \bob{Monoid construction 1, for monoids that distribute over
-    $+$. This also has a residual.}
+  For a commutative pomonoid $(\bullet, i)$ on $(A, \leq)$ that
+  distributes over $+$
+  ($(x \bullet y) + z = (x + z) \bullet (y + z)$), then
+  $F \ClosedDay{\bullet} G = \alpha(U F \Day{\bullet} U G)$ and
+  $\ClosedDay{j} = \alpha(\Day{j})$ define a residuated commutative
+  pomonoid on $\ClosedLowerSet{A}$.
 \end{proposition}
@@
   $+$-closed lower sets. We will be careful to distinguish which we
-  mean: a symmetric operator like $\bullet$ will distribute over $+$
-  and so $\ClosedDay{\bullet}$ will be constructed by Proposition
-  \ref{prop:closed-monoid-distrib}; and a non-symmetric operator like
-  $\lhd$ will be entropic with respect to $+$ and so
-  $\ClosedDay{\lhd}$ will be constructed by Proposition
+  mean: in our present application, a symmetric operator like
+  $\bullet$ will distribute over $+$ and so $\ClosedDay{\bullet}$ will
+  be constructed by Proposition \ref{prop:closed-monoid-distrib}; and
+  a non-symmetric operator like $\lhd$ will be entropic with respect
+  to $+$ and so $\ClosedDay{\lhd}$ will be constructed by Proposition
   \ref{prop:closed-monoid-duoidal}.
@@
 \begin{remark}
-  If we have two $(A, \leq)$ pomonoids with the same unit, then the
-  two constructions will yield the same closed lower set.
-  \bob{elaborate a bit...}
+  If we have two pomonoids on $(A, \leq)$ that share a unit, then the
+  two constructions of units in Propositions
+  \ref{prop:closed-monoid-distrib} and
+  \ref{prop:closed-monoid-duoidal} will yield the same element of
+  $\ClosedLowerSet{A}$.
 \end{remark}
@@
 $*$-autonomous categories from symmetric monoidal closed categories
-with pullbacks. In the preorder case, the requirement for preorders
-simplifies to binary meets. Therefore, for this section, we let
-$(A, \leq, \bullet, i, \rightblackspoon)$ be a symmetric monoidal
-closed preorder with all binary meets.
+with pullbacks. In the partial order case, the requirement for
+pullbacks simplifies to binary meets. Therefore, for this section, we
+let $(A, \leq, \bullet, i, \rightblackspoon)$ be a partial order with
+a residuated pomonoid structure and all binary meets.
 
@@
 \begin{proposition}
-  $\Chu(A, k)$ is a $*$-autonomous partial order with pomonoid and
-  negation structure defined as:
-  \begin{mathpar}
+  $(\Chu(A, k), \sqsubseteq)$ has a $*$-autonomous structure defined
+  as:
+  \begin{displaymath}
     (a^+, a^-) \otimes (b^+, b^-) = (a^+ \bullet b^+, (b^+ \rightblackspoon a^-) \land (a^+ \rightblackspoon b^-))
-
+    \qquad
     I = (i, k)
-
-    (a^+,a^-)^\perp = (a^-, a^+)
-  \end{mathpar}
+    \qquad
+    \lnot(a^+,a^-) = (a^-, a^+)
+  \end{displaymath}
 \end{proposition}
@@
 \begin{remark}
-  If we choose $k = i$, then $\Chu(A, i)$ is a $*$-autonomous partial
-  order that satisfies \emph{mix}.
+  If we choose $k = i$, then $(\Chu(A, i), \sqsubseteq)$ has
+  $*$-autonomous structure that satisfies \emph{mix}.
 \end{remark}
 
-\begin{proposition}
-  If $A$ has binary joins, then $\Chu(A, k)$ has binary meets, given
-  by $(a^+,a^-) \with (b^+,b^-) = (a^+ \land b^+, a^- \lor b^-)$.
+\begin{proposition}\label{prop:chu-meets}
+  If $A$ has binary joins, then $(\Chu(A, k), \sqsubseteq) x$ has
+  binary meets, given by
+  $(a^+,a^-) \with (b^+,b^-) = (a^+ \land b^+, a^- \lor b^-)$.
 \end{proposition}
 
-\paragraph{Self-dual duoidal structure}
-These two theorems give us enough structure to interpret the
-multiplicative and additive constructs of MAV. We need to also
-interpret the self-dual $P; Q$ connective. Let us assume that we have
-an operation $-\lhd- : A \times A \to A$ that we want to induce
-self-dual operator on $\Chu(A, k)$. By the way the Chu construction is
-defined, we can make an operator that is self-dual by definition:
-\begin{displaymath}
-  (a^+, a^-) ; (b^+, b^-) = (a^+ \lhd b^+, a^- \lhd b^-)
-\end{displaymath}
-for this to work, we need to assume duoidality.
+\begin{remark}
+  Since $(\Chu(A, k), \sqsubseteq)$ is a $*$-autonomous partial order,
+  then Proposition \ref{prop:chu-meets} also means that $\Chu(A, k)$
+  has all binary joins, with
+  $(a^+, a^-) \oplus (b^+, b^-) = (a^+ \lor b^+, a^- \land b^-)$.
+\end{remark}
 
-And that the dualising object $k$ is a
-satisfies $k \lhd k \leq k$. If $\lhd$ has a unit $j$, then $(j, j)$ is a unit if
-
+We now turn to the self-dual duoidal structure required to interpret
+the $\vSeq$ connective. First we transfer pomonoids from $(A, \leq)$
+to self-dual pomonoids on $(\Chu(A, k), \sqsubseteq)$ provided they
+interact well with $k$:
 \begin{proposition}\label{prop:chu-self-dual}
@@
 
-\begin{lemma}
-  \bob{entropy on residuals}
+Finally, we need to show that if $(\bullet, j)$ is duoidal over
+$(\lhd, j)$, then their Chu counterparts are in the same
+relationship. Due to the use of residuals in the definition of
+$\otimes$, we need the following fact about duoidal residuated
+pomonoids:
+
+\begin{lemma}\label{lem:duoidal-residual}
+  If $(\bullet, j)$ is duoidal over $(\lhd, j)$ in a partial order
+  $(A, \leq)$ and $(\bullet, j)$ has a residual $\rightblackspoon$,
+  then
+  $(w \rightblackspoon x) \lhd (y \rightblackspoon z) \leq (w \lhd y)
+  \rightblackspoon (x \lhd z)$.
 \end{lemma}
+
+\begin{remark}
+  Lemma \ref{lem:duoidal-residual} is in some sense the
+  ``intuitionistic'' version of the duoidal relationship for $\parr$
+  arising as the dual of that for $\otimes$ in a $*$-autonomous
+  partial order.
+\end{remark}
 
@@
   If $(F, \leq, \parallel, \lhd, I, +)$ is an MAV-frame, then
-  $\Chu(\ClosedLowerSet{F}, I)$ has the structure of an MAV-algebra.
+  $(\Chu(\ClosedLowerSet{F}, I), \sqsubseteq)$ has the structure of an
+  MAV-algebra.
 \end{theorem}

### 2024-03-26 doc/sections/mav-semantics.tex
[ tex ] various

@@
 
-\subsection{$*$-autonomous and Duoidal Partial Orders}
+\bob{Short introduction to the section here}
+
+\subsection{$*$-autonomous and Duoidal Structure on Partial Orders}
 
@@
 
+The definition of $*$-autonomous category is due to Barr
+\cite{Barr_1979}. For our purposes, we need the partial order
+analogue, also called a CL algebra by Troelstra
+\cite{Troelstra92:lll}.
+
 \begin{definition}
@@
   immediate consequences, but we leave description of these until
-  after the definition of MAV-algebra below. \bob{because there are
-    even more consequences in the presence of additive and duoidal
-    structure}
+  after the definition of MAV-algebra in Definition
+  \ref{defn:mav-algebra}.
 \end{remark}
@@
 
-\bob{need to define \emph{entropy} and \emph{entropic} somewhere}
+\bob{need to define \emph{entropy} and \emph{entropic} somewhere. I
+  think we can have that one pomonoid is \emph{entropic} over another,
+  and the structure of having two monoids where one is entropic over
+  the other is called duoidal structure.}
 
@@
 
-\begin{definition}
+\begin{definition}\label{defn:mav-algebra}
   An \emph{MAV-algebra} is a structure
@@
 
-The Lower Set adds residuals to the pomonoids of an MAV-frame, so the
-Chu construction below will allow us to add duals to interpret all of
-the multiplicative subsystem of MAV. To incorporate the additives in
-such a way that we will be able to derive the proof normalisation
-property, we need to refine lower sets to ones that are closed under
+In the phase semantics, formulas are interpreted as elements that are
+fixed points of a closure operator defined by a double negation with
+respect to the monoid on the original frame. This closure operator
+generates a partial order of ``facts'' whose meets and joins exactly
+correspond to the syntactic ones when the original monoid is derived
+from the proofs. As we mentioned in the introduction, the presence of
+a self-dual operator in BV means that we cannot use double negation
+closure, and we have to proceed more deliberately to preserve
+join-like structure in an MAV-frame when building MAV-algebras.
+
+We do this by defining closed lower sets as those that are closed
+under finite $+$-combinations of their elements.
+
+Lower sets add residuals to the pomonoids of an MAV-frame, so the Chu
+construction below will allow us to add duals to interpret all of the
+multiplicative subsystem of MAV. To incorporate the additives in such
+a way that we will be able to derive the proof normalisation property,
+we need to refine lower sets to ones that are closed under
 $+$-combinations.
@@
   distributes over $+$
-  ($(x \bullet y) + z = (x + z) \bullet (y + z)$), then
+  ($(x + y) \bullet z \leq (x \bullet z) + (y \bullet z)$), then
   $F \ClosedDay{\bullet} G = \alpha(U F \Day{\bullet} U G)$ and

### 2024-03-26 doc/sections/mav-syntax.tex
[ tex ] semantics semantics semantics
Rephrase equivalence

--- 2024-03-25 doc/sections/mav-syntax.tex
@@
 \end{displaymath}
-
-Equivalences:
+Usually, in BV and its extension, structures are considered equivalent modulo a decidable equality comprising duality, as given above, and the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a pomonoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative pomonoids.
 \begin{displaymath}

### 2024-03-26 doc/sections/mav-semantics.tex
[ tex ] done most of the semantics section

@@
-\section{Semantics}\label{sec:mav-semantics}
+\section{Semantic Models for MAV}\label{sec:mav-semantics}
 
@@
 
-\subsection{$*$-autonomous and Duoidal Structure on Partial Orders}
+\begin{itemize}
+\item We construct algebraic models of MAV
+\item MAV-algebras are algebras that MAV is sound for. In some
+  sense, this is straightforward, but we identify precisely the
+  structure that is needed.
+\item The key structure is duoidality, or entropy.
+\item We develop some model theory here, and show that MAV-algebras
+  can be induced by the weaker structure of MAV-frames. This is
+  essential for the cut-free elimination proof.
+\end{itemize}
+
+\subsection{Pomonoidal, $*$-autonomous, and Duoidal Structure on Partial Orders}
 
@@
 \subsection{MAV-algebras}
+
+\bob{Change $;$ to $\lhd$}
 
@@
 \begin{remark}
-  \bob{A frame is nearly two duoidal structures, except that we don't
-    assume that $+$ is a monoid, nor is there a unit element for
-    it. If we assumed that $+$ was a lattice join, then (iii) and (iv)
-    would automatically be true. We do not include this because these
-    facts are not true for the cut-free MAV system.}
+  An MAV-frame is essentially two duoidal relationships and a
+  distributivity law.
 \end{remark}
@@
 \begin{remark}
-  \bob{Connection to process algebras: we can read the ordering as
-    ``reduces to'' and the connectives as parallel combination,
-    sequential composition, and choice, respectively. If we add in
-    atomic elements with duals and an interaction law, then we get
-    something like CCS without restriction, but with sequential
-    composition.}
+  MAV-frames have a intuitive reading as a CCS-like process algebra
+  (see Milner \cite{milner89} for an introduction to CCS). If we
+  assume the existence of a collection of ``action'' elements
+  $a \in F$ and their duals $\overline{a} \in F$, satisfying
+  $a \parallel \overline{a} \leq I$, then we can read the constructs
+  of an MAV-frame as parallel composition, sequential composition, and
+  choice. The ordering is interpreted as a reduction relation. An
+  interesting avenue for future work would be to discover to what
+  extent MAV can be thought of as a logic for processes in this
+  process algebra.
 \end{remark}
@@
 
-\bob{Some introductory text here: explain the steps in the construction and what each one adds.}
+We construct MAV-algebras from MAV-frames in a three step process. In
+Section \ref{sec:lower-sets}, we use lower sets and the Day
+construction to add meets, joins and residuals for pomonoids to a
+partial order. This construction creates joins freely, so we restrict
+to $+$-closed lower sets in Section \ref{sec:closed-lower-sets}, which
+separates the Day construction of pomonoids into two separate
+cases. Finally, we create the $*$-autonomous structure using the Chu
+construction in Section \ref{sec:chu}. We maintain the duoidal
+structure through each construction.
 
 \subsubsection{Lower Sets and Day pomonoids}
+\label{sec:lower-sets}
 
@@
   intersection and union respectively.
-
-  \bob{and $\eta$ preserves any meets that exist}
+%
+%  \bob{and $\eta$ preserves any meets that exist}
 \end{proposition}
@@
   \end{enumerate}
-  \bob{Could also say that $\eta$ preserves the monoids}
+  \bob{Could also say that $\eta$ preserves the monoids. Does this
+    come up later?}
 \end{proposition}
@@
 \begin{proposition}\label{prop:lower-set-duoidal}
-  If $(\bullet, i)$ and $(\lhd, j)$ are in a duoidal relationship then
-  so are $(\Day{\bullet}, \Day{i})$ and $(\Day{\lhd}, \Day{j})$.
+  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ then
+  $(\Day{\bullet}, \Day{i})$ is duoidal over $(\Day{\lhd}, \Day{j})$.
 \end{proposition}
 
-\subsubsection{Closed Lower Sets}
+\subsubsection{$+$-closed Lower Sets}
+\label{sec:closed-lower-sets}
 
@@
 closure, and we have to proceed more deliberately to preserve
-join-like structure in an MAV-frame when building MAV-algebras.
+join-like structure in an MAV-frame when building MAV-algebras. We do
+this by defining $+$-closed lower sets as those that are closed under
+finite $+$-combinations of their elements. This leads to a closure
+operator on lower sets that allows us to immediately deduce that
+$+$-closed lower sets form a lattice. We also preserve the
+Day-pomonoids from lower sets, but in two different ways, depending on
+how the original pomonoid interacts with $+$. In Proposition
+\ref{prop:closed-monoid-distrib} we handle pomonoids that distribute
+over $+$, and in Propositional \ref{prop:closed-monoid-duoidal} we
+handle pomonoids that are entopic under $+$. We need these
+constructions to lift the $\parallel$ and $\lhd$ pomonoids from
+MAV-frames to $+$-closed lower sets. Finally in this section, we show
+that duoidal structure on lower sets from Proposition
+\ref{prop:lower-set-duoidal} is preserved in $+$-closed lower sets.
 
-We do this by defining closed lower sets as those that are closed
-under finite $+$-combinations of their elements.
-
-Lower sets add residuals to the pomonoids of an MAV-frame, so the Chu
-construction below will allow us to add duals to interpret all of the
-multiplicative subsystem of MAV. To incorporate the additives in such
-a way that we will be able to derive the proof normalisation property,
-we need to refine lower sets to ones that are closed under
-$+$-combinations.
-
-This corresponds to a sheaf construction, but we do not assume that
-the ``join'' operation is stable with respect to meets.
-
-The following development has proved amenable to mechanisation.
-
-$+$-contexts are the semantic analogue of Horne's \emph{Killing
-  contexts}.
+For this section, we assume that $(A, \leq)$ is a partial order with a
+monotone binary operation $+ : A \times A \to A$ (we do not assume
+that $+$ is a join or even a pomonoid.)
 
 \begin{definition}
-  Let $(A, \leq)$ be a partial order with a monotone binary operation
-  $+ : A \times A \to A$.  Let $F \in \LowerSet{A}$. A
-  \emph{$+$-context} over $F$ is a binary tree built from constructors
+  A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if $x \in F$
+  and $y \in F$ imply $x + y \in F$. $+$-closed lower sets are ordered
+  by subset inclusion and form a partial order
+  $(\ClosedLowerSet{A}, \subseteq)$.
+\end{definition}
+
+\begin{proposition}
+  Let $U : \ClosedLowerSet{A} \to \LowerSet{A}$ be the ``forgetful''
+  function that forgets the $+$-closed property. There is a monotone
+  function $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ such that
+  for all $F \in \ClosedLowerSet{A}$, $\alpha(U F) = F$ and for all
+  $F \in \LowerSet{A}$, $F \subseteq U (\alpha F)$.
+\end{proposition}
+
+\begin{proof}
+  To define $\alpha$, we close lower sets under all
+  $+$-combinations. To this end, for $F \in \LowerSet{A}$, define
+  $\mathrm{ctxt}(F)$, the set of all $+$-combinations of $F$
+  inductively built from constructors
   $\mathsf{leaf} : F \to \mathrm{ctxt}(F)$ and
@@
   $\mathit{sum}(\mathsf{node}(c,d)) = \mathit{sum}(c) +
-    \mathit{sum}(d)$.
-\end{definition}
-
-\begin{remark}
-  Conceptually higher level view on contexts: if we view a lower set
-  $F$ as a monotone function $F : A^\op \to \Omega$, then we can view
-  the context construction as a relative monad on lower sets to
-  partial orders.  \bob{and this should extend to presheaves and
-    categories}.
-\end{remark}
-
-\begin{definition}
-  A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if for all
-  $c \in \mathsf{ctxt}(F)$, $\mathit{sum}(c) \in F$. $+$-closed lower
-  sets are ordered by subset inclusion and form a partial order
-  $(\ClosedLowerSet{A}, \subseteq)$.
-\end{definition}
-
-\begin{proposition}
-  There is a monotone function
-  $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ with the following
-  properties. It is a Galois reflection. FIXME
-
-  \begin{displaymath}
-    \alpha(F) = \{ x \mid c \in \mathrm{ctxt}(F), x \leq \mathit{sum}(c) \}
-  \end{displaymath}
-\end{proposition}
-
-\begin{proof}
-  Explain the Agda, this relies on the fact that $\mathrm{ctxt}$ is a
-  (relative) monad.
+  \mathit{sum}(d)$. Now define:
+  $\alpha(F) = \{ x \mid c \in \mathrm{ctxt}(F), x \leq
+  \mathit{sum}(c) \}$. This is $+$-closed, by taking the
+  $\mathsf{node}$ combination of contexts. $\alpha \circ U$ is
+  idempotent because $\alpha$ does not introduce any elements to lower
+  sets that are already closed. For arbitrary lower sets $F$,
+  $F \subseteq U(\alpha F)$ by the $\mathsf{leaf}$ constructor.
 \end{proof}
@@
 \begin{proof}
-  $\alpha$ preserves the monoidal structure, so we can use it to prove
-  the monoid laws for the constructed monoid.
-
-  \bob{Sketch why this works: we can multiply together the contexts.}
+  We can define an operation
+  $\bullet^c : \mathrm{ctxt}(F) \times \mathrm{ctxt}(G) \to
+  \mathrm{ctxt}(F \Day{\bullet} G)$ that ``multiplies'' two trees,
+  such that
+  $\mathit{sum}(c) \bullet \mathit{sum}(d) \leq \mathit{sum}(c
+  \bullet^c d)$, using the distributivity. This allows us to show that
+  $\alpha$ preserves the monoid operation:
+  $\alpha F \ClosedDay{\bullet} \alpha F = \alpha (F \Day{\bullet}
+  G)$. With this, we can show that the monotonicity, associativity,
+  unit, and commutativity properties of $\Day{\bullet}$ transfer over
+  to $\ClosedDay{\bullet}$. The definition of the residual from lower
+  sets is already $+$-closed, by distributivity.
 \end{proof}
@@
 \begin{proof}
-  \bob{Explain the Agda here}
+  Since $+$ is entropic over $(\lhd, j)$, the Day monoid $\Day{\lhd}$
+  is automatically $+$-closed. The monoid structure directly
+  transfers. Similarly, $\eta(j)$ is automatically $+$-closed since
+  $j + j \leq j$.
 \end{proof}
@@
   over $+$ (as in Proposition \ref{prop:closed-monoid-distrib}) and
-  $(\lhd, j)$ is entropic with respect to $+$ (as in Proposition
+  $+$ is entropic over $(\lhd, j)$ (as in Proposition
   \ref{prop:closed-monoid-duoidal}). Then
@@
 \begin{proof}
-  \bob{Explain the Agda here}
+  The entropic relationship established in Proposition
+  \ref{prop:lower-set-duoidal} carries over thanks to the properties
+  of $\alpha$ and $U$. The fact that
+  $\ClosedDay{i} \subseteq \ClosedDay{j}$ relies on the condition
+  $j + j \leq j$ to collapse $+$-contexts of $j$s.
 \end{proof}
@@
 \subsubsection{Chu Construction}
+\label{sec:chu}
 
@@
 \begin{proposition}\label{prop:chu-self-dual}
-  Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that
+  Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that $(\bullet, i)$ is entropic over 
   $k \lhd k \leq k$ and $j \leq k$, then
@@
 \begin{proof}
-  \bob{show that that two extra bits are needed.}
+  $x;y$ is well-defined because
+  $(x^+ \lhd y^+) \bullet (x^- \lhd y^-) \leq (x^+ \bullet x^-) \lhd
+  (y^+ \bullet y^-) \leq k \lhd k \leq k$. $J$ is well defined because
+  $j \bullet j \leq j \leq k$. The pomonoid laws all transfer directly.
 \end{proof}
@@
 \begin{proposition}
-  If $(\bullet, i)$ and $(\lhd, j)$ are in a duoidal relationship on
-  $(A, \leq)$, and $(\lhd, j)$ satisfies the conditions of Proposition
+  If $(\bullet, i)$ is entropic over $(\lhd, j)$ on $(A, \leq)$, and
+  $(\lhd, j)$ satisfies the conditions of Proposition
   \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(;, J)$ are in a
@@
 \begin{proof}
-  \bob{Explain the Agda}
+  For the positive half of the Chu construction, this is a direct
+  consequence of the entropy on $(A, \leq)$. For the negative half, we
+  use Lemma \ref{lem:duoidal-residual} and the fact that meets are
+  always duoidal.
 \end{proof}

### 2024-03-26 doc/sections/mav-syntax.tex
Change atoms to alpha/beta

--- 2024-03-25 doc/sections/mav-syntax.tex
@@
 
-The structures of MAV are formed from positive and negative atoms ($\vPos\vA$ and $\vNeg\vA$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
+The structures of MAV are formed from positive and negative atoms ($\vPos\va$ and $\vNeg\va$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
 \begin{displaymath}
   \vP,\vQ,\vR,\vS
-  \Coloneq \vPos\vA
-  \mid     \vNeg\vA
+  \Coloneq \vPos\va
+  \mid     \vNeg\va
   \mid     \vUnit
@@
       l@{\;=\;}l}
-    \vDual{\vPos\vA}     & \vNeg\vA
+    \vDual{\vPos\va}     & \vNeg\va
                          &
@@
     \\
-    \vDual{\vNeg\vA}     & \vPos\vA
+    \vDual{\vNeg\va}     & \vPos\va
                          &
@@
 \end{displaymath}
-
-Equivalences:
+Structures are considered equivalent modulo the decidable equality $\vEquiv$, which is the smallest congruence defined by the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a monoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative monoids.
 \begin{displaymath}
@@
 \begin{remark}
-  The usual presentation of BV writes the structure connectives as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
+  The structural connectives of BV are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
 \end{remark}
+
+\begin{displaymath}
+  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
+    \vNeg\va\vParr\vPos\va
+     & \vUnit
+     & \RuleLabel{Axiom}
+  \end{array}
+\end{displaymath}

### 2024-03-26 doc/sections/mav-syntax.tex
Tiny changes
Tiny change

@@
 \begin{displaymath}
-  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
+  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
     \vP\vParr\vDual\vP
+     & \vInferFrom
      & \vUnit
@@
     \vUnit
+     & \vInferFrom
      & \vP\vTens\vDual\vP
@@
     \vUnit\vWith\vUnit
+     & \vInferFrom
      & \vUnit
@@
     (\vP\vTens\vQ)\vParr\vR
+     & \vInferFrom
      & \vP\vTens(\vQ\vParr\vR)
@@
     (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
+     & \vInferFrom
      & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
@@
     \vP\vPlus\vQ
+     & \vInferFrom
      & \vP
@@
     \vP\vPlus\vQ
+     & \vInferFrom
      & \vQ
@@
     (\vP\vWith\vQ)\vParr\vR
+     & \vInferFrom
      & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
@@
     (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
+     & \vInferFrom
      & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
      & \RuleLabel{medial}
+    \\
+    \vC\vPlug\vP\vInferFrom\vC\vPlug\vQ
+     & \text{if}
+     & \vP\vInferFrom\vQ
+     & \RuleLabel{cong}
+    % \\
+    % \vP\vInferFrom\vQ
+    %  & \text{if}
+    %  & \vP\vEquiv\vQ
+    %  & \RuleLabel{equiv}
   \end{array}
@@
 
-We write $\vEquiv$ for invertible inference rules, \ie $\vP\vEquiv\vQ$ means $\vP\vInfer\vQ$ and $\vQ\vInfer\vP$.
-
-We write $\vInfer*$ for the reflexive, transitive closure of $\vInfer$.
+We write $\vInferFrom*$ for the reflexive, transitive closure of $\vInferFrom$.
+We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.
 
@@
 \begin{displaymath}
-  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
+  \begin{array}{l@{\;\vInferFrom\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
     \vNeg\va\vParr\vPos\va

### 2024-03-26 doc/sections/mav-cut-elimination.tex
[ agda tex ] more conceptual proof of reflection property

\section{Semantic Cut-Elimination}\label{sec:mav-cut-elimination}

\begin{proposition}
  Let $\Chu(\ClosedLowerSet{\textsc{CFMav}}, \ClosedDay{I})$ be the
  MAV-algebra constructed from the Cut-free proof MAV-frame
  (Proposition \ref{prop:cfmav-frame}), where elements are
  positive/negative pairs of $+$-closed lower sets of formulas.

  \bob{describe the interpretation of atoms}

  The interpretation of SMAV formulas in this MAV-algebra satisfies
  the following two properties for every formula $\vP$:
  \begin{enumerate}
  \item $\eta^+(P) \subseteq \sem{\vP}^-$
  \item $\sem{\vP}^+ \subseteq \eta^+(P) \rightblackspoon \ClosedDay{i}$
%  \item $\forall \vR \in \sem{\vP}^+.~(\vR \vParr \vP) \longrightarrow^* I$
  \end{enumerate}
\end{proposition}

\begin{remark}
  These properties are akin to the \emph{reflect} and \emph{reify}
  functions used in Normalisation by Evaluation (NbE). The
  \emph{reflect} property creates a canonical negative proof of every
  formula assuming that formula (corresponding to $\eta$-expansion in
  NbE. The \emph{reify} property extracts a normal-form proof from the
  semantic model.
\end{remark}

\begin{proof}
  By induction on the structure of the formula $\vP$.
  \begin{itemize}
  \item[$\vUnit$] reflexivity
  \item[A+] reflexivity
  \item[A-] reflexivity
  \item[$\vP \vParr \vQ$] $\eta^+$ preserves monoids (FIXME: proposition)
  \item[$\vP \vTens \vQ$] complicated
  \item[$\vP \vWith \vQ$] $\eta^i$ preserves $+$
  \item[$\vP \vPlus \vQ$] interpreted as a meet, so we reason directly
  \item[$\vP \vSeq \vQ$] $\eta^+$ preserves monoids (FIXME: proposition)
  \end{itemize}
\end{proof}

\subsection{The Okada Property}

### 2024-03-26 doc/sections/mav-semantics.tex
[ agda tex ] more conceptual proof of reflection property

@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:cfmav-frame}
   The \emph{cut-free MAV-frame} $\textsc{CFMav}$ is the partial order

### 2024-03-26 doc/sections/mav-syntax.tex
Define symmetric core

@@
 We write $\vInferFrom*$ for the reflexive, transitive closure of $\vInferFrom$.
-We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.
+We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ (\ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$) and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.
 

### 2024-03-27 doc/sections/mav-cut-elimination.tex
[ agda tex ] Streamline and write up the cut elimination proof

@@
-\section{Semantic Cut-Elimination}\label{sec:mav-cut-elimination}
+\section{Semantic Cut-Elimination and Proof Normalisation}
+\label{sec:mav-cut-elimination}
 
-\begin{proposition}
+\newcommand{\ChuEmbed}{\eta^c}
+\newcommand{\ClosedLowerEmbed}{\eta^+}
+\newcommand{\LowerEmbed}{\eta}
+
 Let $\Chu(\ClosedLowerSet{\textsc{CFMav}}, \ClosedDay{I})$ be the
-  MAV-algebra constructed from the Cut-free proof MAV-frame
-  (Proposition \ref{prop:cfmav-frame}), where elements are
-  positive/negative pairs of $+$-closed lower sets of formulas.
+MAV-algebra constructed from the Cut-free proof MAV-frame (Proposition
+\ref{prop:cfmav-frame}), where elements are positive/negative pairs of
+$+$-closed lower sets of formulas. We define the valuation of atoms as
+$V(\alpha) = \ChuEmbed(\ClosedLowerEmbed(\vDual{\alpha}))$. By Theorem
+\ref{thm:soundness}, we have an interpretation of SMAV formulas
+$\sem{P}$ such that if $P \longrightarrow^* I$, then $I \leq
+sem{P}$. We now prove our main proposition about the MAV-algebra
+\textsc{CFMav} that will allow us to derive the admissibility of Cut
+and all the other symmetric rules of SMAV.
 
-  \bob{describe the interpretation of atoms}
-
-  The interpretation of SMAV formulas in this MAV-algebra satisfies
-  the following two properties for every formula $\vP$:
-  \begin{enumerate}
-  \item $\eta^+(P) \subseteq \sem{\vP}^-$
-  \item $\sem{\vP}^+ \subseteq \eta^+(P) \rightblackspoon \ClosedDay{i}$
-%  \item $\forall \vR \in \sem{\vP}^+.~(\vR \vParr \vP) \longrightarrow^* I$
-  \end{enumerate}
+\begin{proposition}\label{prop:embedding-sem}
+  $\sem{P} \leq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$
 \end{proposition}
 
-\begin{remark}
-  These properties are akin to the \emph{reflect} and \emph{reify}
-  functions used in Normalisation by Evaluation (NbE). The
-  \emph{reflect} property creates a canonical negative proof of every
-  formula assuming that formula (corresponding to $\eta$-expansion in
-  NbE. The \emph{reify} property extracts a normal-form proof from the
-  semantic model.
-\end{remark}
+\begin{proof}
+  By the definition of the Chu construction, this statement breaks
+  down into two inclusions between pairs of $+$-closed lower sets:
+  \begin{enumerate}
+  \item $\ClosedLowerEmbed(P) \subseteq \sem{\vP}^-$
+  \item $\sem{\vP}^+ \subseteq \ClosedLowerEmbed(P) \rightblackspoon^+ \ClosedDay{I}$
+  \end{enumerate}
+  We prove the second assuming the first. It suffices to prove that
+  $\sem{\vP}^+ \ClosedDay{\bullet} \ClosedLowerEmbed(P) \leq
+  \ClosedDay{I}$, which follows from the first part and the property
+  of all Chu-elements that
+  $\sem{\vP}^+ \ClosedDay{\bullet} \sem{\vP}^- \leq \ClosedDay{I}$.
+
+  We prove the first part by induction on $P$. In the cases when
+  $P = \vUnit$ or $P = \vDual{\alpha}$, we already have
+  $\sem{P}^- = \ClosedLowerEmbed(P)$. When $P = \alpha$, we have
+  $\sem{\alpha}^- = \ClosedLowerEmbed(\vDual{\alpha})
+  \rightblackspoon^+ \ClosedDay{I}$. It suffices to prove that
+  $\ClosedLowerEmbed(\alpha) \ClosedDay{\bullet}
+  \ClosedLowerEmbed(\vDual{\alpha}) \leq \ClosedDay{I}$, which follows
+  from the preservation of monoids by $\ClosedLowerEmbed$ and the
+  \RuleLabel{Axiom} rule of MAV.
+
+  When $P = Q \vParr R$, $Q \vWith R$, or $Q \vSeq R$, the result
+  follows from preservation of the corresponding monoid structure by
+  $\ClosedLowerEmbed$. For example,
+  $\ClosedLowerEmbed(Q \vParr R) \leq \ClosedLowerEmbed(Q)
+  \ClosedDay{\bullet} \ClosedLowerEmbed(R) \leq \sem{Q}^-
+  \ClosedDay{\bullet} \sem{R}^- = \sem{Q \vParr R}^-$.
+
+  When $P = Q \vPlus R$, we have
+  $\ClosedLowerEmbed(Q \vPlus R) \leq \ClosedLowerEmbed(Q)$ and
+  $\ClosedLowerEmbed(Q \vPlus R) \leq \ClosedLowerEmbed(R)$, by the
+  \RuleLabel{Left} and \RuleLabel{Right} rules. Therefore,
+  $\ClosedLowerEmbed(Q \vPlus R) \leq \ClosedLowerEmbed(Q) \lor
+  \ClosedLowerEmbed(R) \leq \sem{Q}^- \lor \sem{R}^- = \sem{Q \vPlus
+    R}^-$.
+
+  When $P = Q \vTens R$, we have
+  $\sem{Q \vTens R}^- = (\sem{Q}^+ \rightblackspoon \sem{R}^-) \land
+  (\sem{R}^+ \rightblackspoon \sem{Q}^-)$. We prove inclusion in the
+  left-hand side, the right-hand side is similar. The key property we need to prove is:
+  \begin{equation}\label{eq:interaction-leq}
+    \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
+    \leq
+    \ClosedLowerEmbed(R)
+  \end{equation}
+  Using the monoidality and monotonicity of $\alpha$, this property is
+  implied by the following property in lower sets
+  $\LowerSet{\textsc{CFMav}}$:
+  \begin{displaymath}
+    \LowerEmbed(Q \vTens R) \Day{\bullet} (U(\ClosedLowerEmbed(Q)) \rightblackspoon \Day{I})
+    \leq
+    \LowerEmbed(R)
+  \end{displaymath}
+  which follows from the \RuleLabel{Switch} rule of MAV and
+  calculation. Using Inequation \ref{eq:interaction-leq}, and property
+  (ii) above, we can prove the inequality we need:
+  \begin{displaymath}
+    \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} \sem{Q}^+
+    \leq
+    \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
+    \leq
+    \ClosedLowerEmbed(R)
+    \leq
+    \sem{R}^-
+  \end{displaymath}
+  Using the residuation property of $\ClosedDay{\bullet}$ we can conclude.
+\end{proof}
+
+\begin{theorem}
+  If $P \longrightarrow^* I$ in SMAV, then $P \longrightarrow^* I$ in MAV.
+\end{theorem}
 
 \begin{proof}
-  By induction on the structure of the formula $\vP$.
-  \begin{itemize}
-  \item[$\vUnit$] reflexivity
-  \item[A+] reflexivity
-  \item[A-] reflexivity
-  \item[$\vP \vParr \vQ$] $\eta^+$ preserves monoids (FIXME: proposition)
-  \item[$\vP \vTens \vQ$] complicated
-  \item[$\vP \vWith \vQ$] $\eta^i$ preserves $+$
-  \item[$\vP \vPlus \vQ$] interpreted as a meet, so we reason directly
-  \item[$\vP \vSeq \vQ$] $\eta^+$ preserves monoids (FIXME: proposition)
-  \end{itemize}
+  By Theorem \ref{thm:soundness}, $P \longrightarrow^* I$ in SMAV
+  implies $I \leq \sem{P}$. Combined with Proposition
+  \ref{prop:embedding-sem}, we have
+  $I \leq \lnot \ChuEmbed(\LowerEmbed(P)$. By Definition
+  \ref{defn:chu} of the ordering of Chu elements, we have
+  $\ClosedLowerEmbed(P) \subseteq \ClosedDay{I}$. Since
+  $P \in \ClosedLowerEmbed(P)$, we have $P \in \ClosedDay{I}$, which
+  by definition means that $P \longrightarrow^* I$ in MAV.
 \end{proof}
-
-\subsection{The Okada Property}

### 2024-03-27 doc/sections/mav-semantics.tex
[ agda tex ] Streamline and write up the cut elimination proof

@@
 
-FIXME: cite that combinatorics book.
+\bob{FIXME: cite that combinatorics book.}
 
@@
   $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
-  as follows: $\sem{\vUnit} = I$, $\sem{a} = V(a)$,
-  $\sem{\vDual a} = \lnot V(a)$,
+  as follows: $\sem{\vUnit} = I$, $\sem{\alpha} = V(\alpha)$,
+  $\sem{\vDual \alpha} = \lnot V(\alpha)$,
   $\sem{\vP\vTens\vQ} = \sem{\vP} \otimes \sem{\vQ}$,
@@
     $\Day{\rightblackspoon} : \LowerSet{A} \times \LowerSet{A} \to
-            \LowerSet{A}$ such that ... FIXME
+    \LowerSet{A}$ such that ... \bob{FIXME}
   \item If $(\bullet, i)$ is a commutative pomonoid, then so is
     $(\Day{\bullet}, \Day{i})$. In this case, the residuals coincide.
+  \item The embedding preserves the monoid:
+    $\eta(x \bullet y) = \eta(x) \Day\bullet \eta(y)$.
   \end{enumerate}
-  \bob{Could also say that $\eta$ preserves the monoids. Does this
-    come up later?}
 \end{proposition}
@@
 \begin{remark}
-  This is the Day construction \cite{day} restricted to the case of
-  partial orders.
+  This is the Day monoidal product \cite{day} restricted to the case
+  of partial orders.
 \end{remark}
@@
 \begin{remark}
-  When $(A, \leq)$ is an MAV-frame, by \ref{prop:day-construction} we
-  obtain two pomonoids $(\Day{\parallel}, \Day{I})$ and
-  $(\Day{\lhd}, \Day{I})$ on $\LowerSet{A}$. Moreover, the next
-  proposition states that the duoidal relationship between these
-  monoids is preserved by the Day construction:
+  When $(A, \leq)$ is an MAV-frame, Proposition
+  \ref{prop:day-construction} gives us two pomonoids
+  $(\Day{\parallel}, \Day{I})$ and $(\Day{\lhd}, \Day{I})$ on
+  $\LowerSet{A}$. Moreover, the next proposition states that the
+  duoidal relationship between these monoids is preserved by the Day
+  construction:
 \end{remark}
@@
 
+\begin{definition}
+  Define the embedding $\eta^+ : A \to \ClosedLowerSet{A}$ as
+  $\eta^+(x) = \alpha(\eta(x))$.
+\end{definition}
+
 \begin{remark}
@@
 
+\begin{proposition}\label{prop:closed-eta-preserve-joins}
+  $\eta^+(x + y) \subseteq \eta^+(x) \lor \eta^+(y)$.
+\end{proposition}
+
 \begin{remark}
-  Note that $\alpha$ does not preserve meets.
+  Proposition \ref{prop:closed-eta-preserve-joins} is the reason for
+  requiring $+$-closure. This property will allow us to prove the
+  crucial embedding property for all formulas in Section
+  \ref{sec:mav-cut-elimination}.
+
+  \bob{Not an equality, I think, because $+$ isn't necessarily a join.}
 \end{remark}
@@
   $\ClosedDay{j} = \alpha(\Day{j})$ define a residuated commutative
-  pomonoid on $\ClosedLowerSet{A}$.
+  pomonoid on $\ClosedLowerSet{A}$. Moreover,
+  $\eta^+(x \bullet y) = \eta^+(x) \ClosedDay{\bullet} \eta^+(y)$.
 \end{proposition}
@@
   $(\ClosedDay{\lhd}, \ClosedDay{j})$ form a pomonoid on
-  $(\ClosedLowerSet{A}, \subseteq)$.
+  $(\ClosedLowerSet{A}, \subseteq)$. Moreover,
+  $\eta^+(x \lhd y) = \eta^+(x) \ClosedDay{\lhd} \eta^+(y)$.
 \end{proposition}
@@
 
-\begin{definition}
+\begin{definition}\label{defn:chu}
   Let $k$ be an element of $A$. $\Chu(A, k)$ is the partial order with

### 2024-03-27 doc/sections/mav-syntax.tex
Tiny phrase
Commit to pull Bob's changes

@@
 \end{displaymath}
-
-\begin{itemize}
-  \item Structural equivalences are explicit.
-  \item Inference is a congruence.
-  \item Inference rules are unary.
-  \item Relate to usual presentation of MALL.
-  \item Relate to usual presentation of BV.
-\end{itemize}
-
-Inference rules:
+The inference rules of MAV are presented as a \emph{rewriting system} on structures.
+As this may be surprising to readers unfamiliar with deep inference, let us examine how this presentation relates to the usual presentation of linear logic.
+Rule~(\ref{rule:ll-axiom}) is the axiom rule in the usual one-sided presentation of linear logic.
+In the one-sided presentation, the turnstile is vestigial syntax, and can be removed.
+In BV, the $\vParr$ connective plays the same role as the comma does in the antecedent of a linear logic sequent, and the $\vUnit$ plays the same role as the empty sequent, which would give us rule~(\ref{rule:bv-axiom-bad}) for BV.
+However, BV's inference rules can work arbitrarily deep in the structure. (Hence, \emph{deep} inference.)
+Therefore, the axiom for BV is actually rule~(\ref{rule:bv-axiom-good}), where $\vC$ is a one-hole structure context.
+In BV, all inference rules are unary.
+A branching inference rule enforces \emph{disjointness} of its premise derivations.
+In BV, disjointness is internalised by the $\vTens$ connective.
+\begin{center}
+  $\inlineequation[rule:ll-axiom]{%
+      \vlderivation{\vlin{}{}{\vdash\vP,\vDual\vP}{\vlhy{}}}}$
+  \qquad
+  $\inlineequation[rule:bv-axiom-bad]{%
+      \vlderivation{\vlin{}{}{\vP\vParr\vDual\vP}{\vlhy{\vUnit}}}}$
+  \qquad
+  $\inlineequation[rule:bv-axiom-good]{%
+      \vlderivation{\vlin{}{}{%
+          \vC\vPlug{\vP\vParr\vDual\vP}}{%
+          \vlhy{\vC\vPlug{\vUnit}}}}}$
+  \qquad
+  $\inlineequation[rule:mav-axiom]{%
+      \vP\vParr\vDual\vP\vInferFrom\vUnit}$
+  \\[1\baselineskip]
+  $\inlineequation[rule:ll-cut]{%
+      \vlderivation{\vliin{}{}{%
+          \vdash\vGG,\vGG',\vGD,\vGD'}{%
+          \vlhy{\vdash\vGG,\vP,\vGG'}}{%
+          \vlhy{\vdash\vGD,\vDual\vP,\vGD'}}}}$
+  \qquad
+  $\inlineequation[rule:ll-cut]{%
+      \vlderivation{\vliin{}{}{%
+          \vGG,\vGG',\vUnit,\vGD,\vGD'}{%
+          \vlhy{\vdash\vGG,\vP,\vGG'}}{%
+          \vlhy{\vdash\vGD,\vDual\vP,\vGD'}}}}$
+  \qquad
+  $\inlineequation[rule:bv-cut-good]{%
+      \vlderivation{\vlin{}{}{%
+          \vC\vPlug{\vP\vParr\vDual\vP}}{%
+          \vlhy{\vC\vPlug{\vUnit}}}}}$
+  \qquad
+  $\inlineequation[rule:mav-cut]{%
+      \vP\vParr\vDual\vP\vInferFrom\vUnit}$
+\end{center}
+The inference rules of MAV are presented as a \emph{rewrite rules} on structures.
+We write $\vP\vInferFrom\vQ$ when $\vP$ can be inferred from $\vQ$.
+The axiom of linear logic is typically given as \ref{rule:axiom-ll}.
+In MAV, the structure connective $\vParr$ plays the same role as the comma does in the antecedent of a linear logic sequent.
 \begin{displaymath}
@@
      & \vP\vInferFrom\vQ
-     & \RuleLabel{cong}
+     & \RuleLabel{mono}
     % \\
@@
 
+A \emph{normal} derivation is a derivation where \cref{rule:cut} is not used and \cref{rule:axiom} is restricted to atoms.
+
 \begin{displaymath}
@@
 \end{displaymath}
+
+\begin{itemize}
+  \item Structural equivalences are explicit.
+  \item Inference is a congruence.
+  \item Inference rules are unary.
+  \item Relate to usual presentation of MALL.
+  \item Relate to usual presentation of BV.
+\end{itemize}

### 2024-03-27 doc/sections/mav-mechanisation.tex
[ tex ] Add a section on the Agda formalisation

\section{Mechanisation in Agda}
\label{sec:mechanisation}

We developed the proof in the previous two sections in the Agda proof
assistant \cite{agda}. The source code for this development is
available at this URL:
\begin{center}
  \url{https://github.com/bobatkey/semantic-cut-elimination}
\end{center}

The formalisation uses setoids to represent sets, reusing definitions
from the Agda Standard Library \cite{agda-stdlib}. Each of the
definitions and propositions above links to the corresponding part of
the development.

As well as giving confidence in our results, a key benefit of
formalising the development in a proof assistant like Agda is that the
proof normalisation process (Theorem \ref{thm:cut-elim}) is
executable. For example, we can normalise the one step SMAV proof
(using \RuleLabel{Axiom}) of $\vP \vParr \vDual{\vP}$ where
$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a FIXME
step MAV proof, given in the Appendix.

\bob{Wen: do you want to write something about the formalisation of
  the congruence rules in the proof system?}

### 2024-03-27 doc/sections/mav-syntax.tex
Add AtomAxiom

@@
 As this may be surprising to readers unfamiliar with deep inference, let us examine how this presentation relates to the usual presentation of linear logic.
-Rule~(\ref{rule:ll-axiom}) is the axiom rule in the usual one-sided presentation of linear logic.
+Rule~(\ref{rule:AxiomLL}), shown below, is the axiom rule in the usual one-sided presentation of linear logic.
 In the one-sided presentation, the turnstile is vestigial syntax, and can be removed.
-In BV, the $\vParr$ connective plays the same role as the comma does in the antecedent of a linear logic sequent, and the $\vUnit$ plays the same role as the empty sequent, which would give us rule~(\ref{rule:bv-axiom-bad}) for BV.
+In BV, the $\vParr$ connective plays the same role as the comma does in the antecedent of a linear logic sequent, and the $\vUnit$ plays the same role as the empty sequent, which would give us rule~(\ref{rule:AxiomBV-bad}) for BV.
 However, BV's inference rules can work arbitrarily deep in the structure. (Hence, \emph{deep} inference.)
-Therefore, the axiom for BV is actually rule~(\ref{rule:bv-axiom-good}), where $\vC$ is a one-hole structure context.
-In BV, all inference rules are unary.
-A branching inference rule enforces \emph{disjointness} of its premise derivations.
-In BV, disjointness is internalised by the $\vTens$ connective.
+Hence, the axiom for BV is rule~(\ref{rule:AxiomBV}), where $\vC$ is a one-hole structure context.
 \begin{center}
-  $\inlineequation[rule:ll-axiom]{%
+  $\inlineequation[rule:AxiomLL]{%
       \vlderivation{\vlin{}{}{\vdash\vP,\vDual\vP}{\vlhy{}}}}$
   \qquad
-  $\inlineequation[rule:bv-axiom-bad]{%
+  $\inlineequation[rule:AxiomBV-bad]{%
       \vlderivation{\vlin{}{}{\vP\vParr\vDual\vP}{\vlhy{\vUnit}}}}$
   \qquad
-  $\inlineequation[rule:bv-axiom-good]{%
+  $\inlineequation[rule:AxiomBV]{%
       \vlderivation{\vlin{}{}{%
@@
           \vlhy{\vC\vPlug{\vUnit}}}}}$
-  \qquad
-  $\inlineequation[rule:mav-axiom]{%
-      \vP\vParr\vDual\vP\vInferFrom\vUnit}$
-  \\[1\baselineskip]
-  $\inlineequation[rule:ll-cut]{%
+  % \qquad
+  % $\inlineequation[rule:mav-axiom]{%
+  %     \vP\vParr\vDual\vP\vInferFrom\vUnit}$
+\end{center}
+Rule (\ref{rule:CutLL}) is the cut rule in the usual one-sided presentation of linear logic.
+In rule (\ref{rule:CutLL}), as in any branching inference rule, the branching enforces the \emph{disjointness} of the premise derivations.
+In BV, disjointness is internalised by the $\vTens$ connective.
+Hence, it plays the same role as branching does in sequent calculus.
+This would give us rule (\ref{rule:CutBVBad}) for BV.
+However, as BV's inference rules can work arbitrarily deep in the structure, the surrounding context of pars is unnecessary---and too restrictive. Hence, the cut for BV is rule (\ref{rule:CutBV}).
+\begin{center}
+  $\inlineequation[rule:CutLL]{%
       \vlderivation{\vliin{}{}{%
@@
   \qquad
-  $\inlineequation[rule:ll-cut]{%
-      \vlderivation{\vliin{}{}{%
-          \vGG,\vGG',\vUnit,\vGD,\vGD'}{%
-          \vlhy{\vdash\vGG,\vP,\vGG'}}{%
-          \vlhy{\vdash\vGD,\vDual\vP,\vGD'}}}}$
+  $\inlineequation[rule:CutBVBad]{%
+      \vlderivation{\vlin{}{}{%
+          \vGG\vParr\vGG'\vParr\vGD\vParr\vGD'}{%
+          \vlhy{%
+            (\vGG\vParr\vP\vParr\vGG')
+            \vTens
+            (\vGD\vParr\vDual\vP\vParr\vGD')}}}}$
   \qquad
-  $\inlineequation[rule:bv-cut-good]{%
+  $\inlineequation[rule:CutBV]{%
       \vlderivation{\vlin{}{}{%
-          \vC\vPlug{\vP\vParr\vDual\vP}}{%
-          \vlhy{\vC\vPlug{\vUnit}}}}}$
-  \qquad
-  $\inlineequation[rule:mav-cut]{%
-      \vP\vParr\vDual\vP\vInferFrom\vUnit}$
+          \vC\vPlug{\vUnit}}{%
+          \vlhy{\vC\vPlug{\vP\vTens\vDual\vP}}}}}$
 \end{center}
-The inference rules of MAV are presented as a \emph{rewrite rules} on structures.
-We write $\vP\vInferFrom\vQ$ when $\vP$ can be inferred from $\vQ$.
-The axiom of linear logic is typically given as \ref{rule:axiom-ll}.
-In MAV, the structure connective $\vParr$ plays the same role as the comma does in the antecedent of a linear logic sequent.
+Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see.
+
+Proof trees are a cumbersome presentation for BV's derivations---they are convenient for trees, but cumbersome in the absence of branching.
+\emph{Rewriting systems}, on the other hand, are a well-known and convenient notation for such derivations.
+Hence, in MAV, inference rules are presented as rewrite rules.
+
+\emph{Inference}, written $\vInferFrom$, is the smallest relation defined by the following axioms:
+% NOTE: These shenanigans are for cross-text table alignment.
+\newlength{\vInferFromDefnWidthOfLBL}%
+\settowidth{\vInferFromDefnWidthOfLBL}{$\RuleName{AtomAxiom}$}%
+\newlength{\vInferFromDefnWidthOfLHS}%
+\settowidth{\vInferFromDefnWidthOfLHS}{$(\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)$}%
+\newlength{\vInferFromDefnWidthOfRHS}%
+\settowidth{\vInferFromDefnWidthOfRHS}{$(\vP\vParr\vR)\vWith(\vQ\vParr\vR)$}%
 \begin{displaymath}
@@
      & \vUnit
-     & \RuleLabel{axiom}
+     & \makebox[\vInferFromDefnWidthOfLBL][l]{$\RuleLabel{Axiom}$}
     \\
@@
      & \vP\vTens\vDual\vP
-     & \RuleLabel{cut}
+     & \RuleLabel{Cut}
     \\
@@
      & \vUnit
-     & \RuleLabel{tidy}
+     & \RuleLabel{Tidy}
     \\
@@
      & \vP\vTens(\vQ\vParr\vR)
-     & \RuleLabel{switch}
+     & \RuleLabel{Switch}
     \\
@@
      & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
-     & \RuleLabel{sequence}
+     & \RuleLabel{Sequence}
     \\
@@
      & \vP
-     & \RuleLabel{left}
+     & \RuleLabel{Left}
     \\
@@
      & \vQ
-     & \RuleLabel{right}
+     & \RuleLabel{Right}
     \\
@@
      & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
-     & \RuleLabel{external}
+     & \RuleLabel{External}
     \\
@@
      & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
-     & \RuleLabel{medial}
+     & \RuleLabel{Medial}
     \\
@@
      & \vP\vInferFrom\vQ
-     & \RuleLabel{mono}
+     & \RuleLabel{Mono}
     % \\
@@
     %  & \vP\vEquiv\vQ
-    %  & \RuleLabel{equiv}
+    %  & \RuleLabel{Equiv}
   \end{array}
 \end{displaymath}
+(If $\vP\vInferFrom\vQ$, we say that $\vP$ can be inferred from $\vQ$, \ie the arrow points from conclusion to premise.)
 
-We write $\vInferFrom*$ for the reflexive, transitive closure of $\vInferFrom$.
-We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ (\ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$) and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.
+\emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
+\emph{Invertible inference}, written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.
+\emph{Invertible derivation}, written $\vBiInfer*$, is the symmetric core of derivation, or, alternatively, the reflexive, transitive closure of invertible inference.
 
+A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and  use of \cref{rule:Axiom} is restricted to atoms.
+\begin{displaymath}
+  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
+    \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
+     & \vInferFrom
+     & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
+     & \RuleLabel{AtomAxiom}
+  \end{array}
+\end{displaymath}
+Usually, these restrictions correspond to the outcome cut elimination and identity expansion, respectively.
 \begin{remark}
@@
 \end{remark}
-
-A \emph{normal} derivation is a derivation where \cref{rule:cut} is not used and \cref{rule:axiom} is restricted to atoms.
-
-\begin{displaymath}
-  \begin{array}{l@{\;\vInferFrom\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
-    \vNeg\va\vParr\vPos\va
-     & \vUnit
-     & \RuleLabel{Axiom}
-  \end{array}
-\end{displaymath}
-
-\begin{itemize}
-  \item Structural equivalences are explicit.
-  \item Inference is a congruence.
-  \item Inference rules are unary.
-  \item Relate to usual presentation of MALL.
-  \item Relate to usual presentation of BV.
-\end{itemize}

### 2024-03-27 doc/sections/mav-syntax.tex
Semi complete intro to BV

@@
 \emph{Invertible derivation}, written $\vBiInfer*$, is the symmetric core of derivation, or, alternatively, the reflexive, transitive closure of invertible inference.
+\emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
 
-A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and  use of \cref{rule:Axiom} is restricted to atoms.
+A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and \cref{rule:Axiom} is restricted to \cref{rule:AtomAxiom}.
 \begin{displaymath}
@@
 \end{displaymath}
-Usually, these restrictions correspond to the outcome cut elimination and identity expansion, respectively.
+These restrictions correspond to the outcome of cut elimination and identity expansion, respectively.
 \begin{remark}
-  The structural connectives of BV are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
+  In BV, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
+  % The equations defining duality are usually included in the decidable equality on structures.
+  Inferences, derivations, and proofs are presented vertically, as (\ref{notation:vlin}), (\ref{notation:vlde}), and (\ref{notation:vlpr}), respectively.
+  \begin{center}
+    $\inlineequation[notation:vlin]{%
+        \vlderivation{\vlin{}{}{\vP}{\vlhy{\vQ}}}}$
+    \qquad
+    $\inlineequation[notation:vlde]{%
+        \vlderivation{\vlde{}{}{\vP}{\vlhy{\vQ}}}}$
+    \qquad
+    $\inlineequation[notation:vlpr]{%
+        \vlderivation{\vlpr{}{}{\vP}}}$
+  \end{center}
 \end{remark}

### 2024-03-27 doc/sections/mav-extensions.tex
[ tex ] future work notes

@@
-\section{Extensions}\label{sec:mav-extensions}
+\section{Conclusions and Future Work}\label{sec:mav-extensions}
 
-\subsection{Additive Units}
+\bob{Summarise what we've done here}
 
-\subsection{Multiplicative-Additive Linear Logic}
+\bob{This is all just notes for now}
 
-\subsection{Display Calculus}
+\subsection{Future Work: Extensions to MAV}
+
+\subsubsection{Additive Units}
+
+I think this will be easy.
+
+\subsubsection{Probabilistic Additives}
+
+Ross's CSL paper.
+
+\subsubsection{Exponentials, Kleene Star, and Inductive Propositions}
+
+Adding $\oc P$ and $\wn P$, as in System NEL. Adding a Kleene Star as
+exponential for $\vSeq$, which could bring us close to Concurrent
+Kleene Algebra (Hoare et al.).
+
+Baelde's fixpoint logic.
+
+\subsection{Future work: Other Substructural Logics}
+
+\subsubsection{Multiplicative-Additive Linear Logic}
+
+Can probably recreate Okada's result using $+$-closed
+
+\subsubsection{Bunched Implications}
+
+I'm pretty sure that the sheaf construction here can be used to do
+bunched implications too, reproducing Frumin's result in a different
+way.
+
+\subsubsection{Display Calculus}
 
 Cut-elimination for a Display calculus?
+
+\subsection{Future Work: Proof Semantics and Categorical Coherence}
+
+We have done provability semantics of MAV.

### 2024-03-27 doc/sections/mav-semantics.tex
[ tex ] fill in some bits

@@
 \begin{definition}
-  \bob{residuation}
+  A pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is \emph{left
+    residuated} if there is a function
+  $\leftblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
+  iff $x \leq z \leftblackspoon y$. The same structure is \emph{right
+    residuated} if there is a function
+  $\rightblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
+  iff $y \leq x \rightblackspoon z$. When $(\bullet, i)$ is
+  commutative, the two definitions coincide, and we just say that the
+  pomonoid is residuated.
 \end{definition}
+\bob{Check that the residuation definitions are the right way round}
 
 The definition of $*$-autonomous category is due to Barr
-\cite{Barr_1979}. For our purposes, we need the partial order
-analogue, also called a CL algebra by Troelstra
-\cite{Troelstra92:lll}.
+\cite{Barr_1979}, and predates the introduction of Linear Logic. For
+our purposes, we need the partial order analogue, also called a CL
+algebra by Troelstra \cite{Troelstra92:lll}.
 
@@
   If $\bullet$ is a join, or $\lhd$ is a meet, then all the conditions
-  for a duoidal relationship are automatically met for any other
-  monoid. \bob{fwd ref to where we use this.}
+  for a duoidal relationship are automatically met.
 \end{remark}
@@
 
-\bob{Change $;$ to $\lhd$}
+We define MAV-algebras as the algebraic semantics of MAV. The
+definition is a direct translation of the rules of MAV into
+order-theoretic language, using the definitions we have seen so far.
 
@@
   An \emph{MAV-algebra} is a structure
-  $(A, \leq, \otimes, ;, I, \lnot)$ with the following properties:
+  $(A, \leq, \otimes, \lhd, I, \lnot)$ with the following properties:
   \begin{enumerate}
   \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
-  \item $(A, \leq, ;, I)$ is a pomonoid.
-  \item $;$ is self dual: $\lnot (x ; y) = (\lnot x); (\lnot y)$.
-  \item $(\otimes, I)$ is duoidal over $(;, I)$.
+  \item $(A, \leq, \lhd, I)$ is a pomonoid.
+  \item $\lhd$ is self dual: $\lnot (x \lhd y) = (\lnot x)\lhd (\lnot y)$.
+  \item $(\otimes, I)$ is duoidal over $(\lhd, I)$.
   \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
@@
 \begin{proposition}\label{prop:mav-algebra-consequences}
-  Let $(A, \leq, \otimes, ;, I, \lnot)$ be a MAV-algebra.
+  Let $(A, \leq, \otimes, \lhd, I, \lnot)$ be a MAV-algebra.
   \begin{enumerate}
@@
           $(x \parr z) \with (y \parr z) = (x \with y) \parr z$.
-    \item $;$ is entropic over $\parr$:
-          $(w \parr x); (y \parr z) \leq (w;y) \parr (x;z)$.
-    \item $;$ is entropic over $\with$:
-          $(w \with x); (y \with z) \leq (w ; y) \with (x; z)$.
-    \item $\oplus$ is entropic over $;$:
-          $(w ; x) \oplus (y ; z) \leq (x \oplus y) ; (x \oplus z)$.
+    \item $\lhd$ is entropic over $\parr$:
+          $(w \parr x)\lhd (y \parr z) \leq (w\lhd y) \parr (x\lhd z)$.
+    \item $\lhd$ is entropic over $\with$:
+          $(w \with x)\lhd (y \with z) \leq (w \lhd y) \with (x\lhd z)$.
+    \item $\oplus$ is entropic over $\lhd$:
+          $(w \lhd x) \oplus (y \lhd z) \leq (x \oplus y) \lhd (x \oplus z)$.
   \end{enumerate}
@@
   $\sem{\vP\vParr\vQ} = \sem{\vP} \parr \sem{\vQ}$,
-  $\sem{\vP\vSeq\vQ} = \sem{\vP};\sem{\vQ}$,
+  $\sem{\vP\vSeq\vQ} = \sem{\vP}\lhd\sem{\vQ}$,
   $\sem{\vP\vWith\vQ} = \sem{\vP} \with \sem{\vQ}$, and
@@
   $k \lhd k \leq k$ and $j \leq k$, then
-  $x ; y = (x^+ \lhd y^+, x^- \lhd y^-)$ and $J = (j, j)$ form a
+  $x \lhd y = (x^+ \lhd y^+, x^- \lhd y^-)$ and $J = (j, j)$ form a
   self-dual pomonoid on $\Chu(A, k)$.
@@
 \begin{proof}
-  $x;y$ is well-defined because
+  $x\lhd y$ is well-defined because
   $(x^+ \lhd y^+) \bullet (x^- \lhd y^-) \leq (x^+ \bullet x^-) \lhd
@@
   $(\lhd, j)$ satisfies the conditions of Proposition
-  \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(;, J)$ are in a
+  \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(\lhd, J)$ are in a
   duoidal relationship on $\Chu(A, k)$.

### 2024-03-27 doc/sections/mav-cut-elimination.tex
[ tex ] Add a section on the Agda formalisation
[ tex ] finish off all of Sec 3 and Sec 4, except an introduction

@@
 
-\newcommand{\ChuEmbed}{\eta^c}
-\newcommand{\ClosedLowerEmbed}{\eta^+}
-\newcommand{\LowerEmbed}{\eta}
-
-Let $\Chu(\ClosedLowerSet{\textsc{CFMav}}, \ClosedDay{I})$ be the
-MAV-algebra constructed from the Cut-free proof MAV-frame (Proposition
-\ref{prop:cfmav-frame}), where elements are positive/negative pairs of
+Let $\Chu(\ClosedLowerSet{\NMAV}, \ClosedDay{I})$ be the MAV-algebra
+constructed from the normal proof MAV-frame (Proposition
+\ref{prop:nmav-frame}), where elements are positive/negative pairs of
 $+$-closed lower sets of formulas. We define the valuation of atoms as
 $V(\alpha) = \ChuEmbed(\ClosedLowerEmbed(\vDual{\alpha}))$. By Theorem
-\ref{thm:soundness}, we have an interpretation of SMAV formulas
+\ref{thm:soundness}, we have an interpretation of MAV formulas
 $\sem{P}$ such that if $P \longrightarrow^* I$, then $I \leq
-sem{P}$. We now prove our main proposition about the MAV-algebra
-\textsc{CFMav} that will allow us to derive the admissibility of Cut
-and all the other symmetric rules of SMAV.
+\sem{P}$. We now prove our main proposition about the MAV-algebra
+\NMAV{} that will allow us to derive the admissibility of all the
+non-normal proof rules of MAV.
 
 \begin{proposition}\label{prop:embedding-sem}
-  $\sem{P} \leq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$
+  $\sem{P} \sqsubseteq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$
 \end{proposition}
@@
   \ClosedLowerEmbed(\vDual{\alpha}) \leq \ClosedDay{I}$, which follows
-  from the preservation of monoids by $\ClosedLowerEmbed$ and the
-  \RuleLabel{Axiom} rule of MAV.
+  from the preservation of monoid operations by $\ClosedLowerEmbed$
+  and the \RuleLabel{Axiom} rule of MAV.
 
@@
   Using the monoidality and monotonicity of $\alpha$, this property is
-  implied by the following property in lower sets
-  $\LowerSet{\textsc{CFMav}}$:
+  implied by the following property of lower sets in
+  $\LowerSet{\NMAV}$:
   \begin{displaymath}
@@
 
-\begin{theorem}
-  If $P \longrightarrow^* I$ in SMAV, then $P \longrightarrow^* I$ in MAV.
+\begin{theorem}\label{thm:cut-elim}
+  If $P \longrightarrow^* I$ in MAV, then there is a normal proof $P \longrightarrow^* I$.
 \end{theorem}
@@
 \begin{proof}
-  By Theorem \ref{thm:soundness}, $P \longrightarrow^* I$ in SMAV
+  By Theorem \ref{thm:soundness}, $P \longrightarrow^* I$ in MAV
   implies $I \leq \sem{P}$. Combined with Proposition
   \ref{prop:embedding-sem}, we have
-  $I \leq \lnot \ChuEmbed(\LowerEmbed(P)$. By Definition
+  $I \sqsubseteq \lnot \ChuEmbed(\LowerEmbed(P)$. By Definition
   \ref{defn:chu} of the ordering of Chu elements, we have
@@
   $P \in \ClosedLowerEmbed(P)$, we have $P \in \ClosedDay{I}$, which
-  by definition means that $P \longrightarrow^* I$ in MAV.
+  by definition means that there is a normal proof
+  $P \longrightarrow^* I$.
 \end{proof}

### 2024-03-27 doc/sections/mav-semantics.tex
[ tex ] finish off all of Sec 3 and Sec 4, except an introduction

@@
   structure that is needed.
-\item The key structure is duoidality, or entropy.
+\item The key structure is duoidality.
 \item We develop some model theory here, and show that MAV-algebras
@@
 \subsection{Pomonoidal, $*$-autonomous, and Duoidal Structure on Partial Orders}
+
+At heart, the semantics of MAV is a collection of interacting monoids
+on a partial order. We collect here the basic definitions and kinds of
+interaction we will need.
 
@@
 \begin{definition}
-  A pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is \emph{left
-    residuated} if there is a function
-  $\leftblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
-  iff $x \leq z \leftblackspoon y$. The same structure is \emph{right
-    residuated} if there is a function
+  A commutative pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is
+  \emph{residuated} if there is a function
   $\rightblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
-  iff $y \leq x \rightblackspoon z$. When $(\bullet, i)$ is
-  commutative, the two definitions coincide, and we just say that the
-  pomonoid is residuated.
+  iff $x \leq y \rightblackspoon y$.
 \end{definition}
-\bob{Check that the residuation definitions are the right way round}
 
-The definition of $*$-autonomous category is due to Barr
-\cite{Barr_1979}, and predates the introduction of Linear Logic. For
-our purposes, we need the partial order analogue, also called a CL
-algebra by Troelstra \cite{Troelstra92:lll}.
+Classical Linear Logic adds a duality, or negation, to a commutative
+pomonoid structure. Semantically, duality with commutativity is
+captured in the definition of $*$-autonomous category is, due to Barr
+\cite{Barr_1979}. For our purposes, we need the partial order
+analogue, also called a CL algebra by Troelstra
+\cite{Troelstra92:lll}.
 
@@
 
-\bob{FIXME: cite that combinatorics book.}
-
-\bob{need to define \emph{entropy} and \emph{entropic} somewhere. I
-  think we can have that one pomonoid is \emph{entropic} over another,
-  and the structure of having two monoids where one is entropic over
-  the other is called duoidal structure.}
+BV and MAV extend CLL by adding a non-commutative pomonoid structure
+that interacts with the existing pomonoid via a kind of interchange
+law (the \RuleLabel{Sequence} rule in the proof system). We follow
+\cite{hopf-book} generalising these to the case of monoids with
+differing units. Their terminology is of a category having duoidal
+structure. We find it useful to describe one pomonoid as being
+\emph{duoidal over} another to emphasise the non-symmetric nature of
+the relationship, and by analogy with one monoid distributing over
+another.
 
 \begin{definition}
-  Two pomonoids $(\bullet, i)$ and $(\lhd, j)$ on a partial order
-  $(A, \leq)$ are in a \emph{duoidal} relationship if the following
+  A pomonoid $(\bullet, i)$ is \emph{duoidal over} another pomonoid
+  $(\lhd, j)$ on a partial order $(A, \leq)$ if the following
   inequalities hold:
@@
   three conditions for a duoidal relationship are automatically
-  satisfied.
-\end{remark}
-
-\begin{remark}
-  If $\bullet$ is a join, or $\lhd$ is a meet, then all the conditions
-  for a duoidal relationship are automatically met.
-\end{remark}
-
-\begin{remark}
-  The duoidal relationship is not symmetric.
+  satisfied. We can also ignore the existence of the units and just
+  describe two binary operators as being duoidal. If $\bullet$ is a
+  join, or $\lhd$ is a meet, then all the conditions for a duoidal
+  relationship are automatically met.
 \end{remark}
@@
           $(x \parr z) \with (y \parr z) = (x \with y) \parr z$.
-    \item $\lhd$ is entropic over $\parr$:
+    \item $\lhd$ is duoidal over $\parr$:
           $(w \parr x)\lhd (y \parr z) \leq (w\lhd y) \parr (x\lhd z)$.
-    \item $\lhd$ is entropic over $\with$:
+    \item $\lhd$ is duoidal over $\with$:
           $(w \with x)\lhd (y \with z) \leq (w \lhd y) \with (x\lhd z)$.
-    \item $\oplus$ is entropic over $\lhd$:
+    \item $\oplus$ is duoidal over $\lhd$:
           $(w \lhd x) \oplus (y \lhd z) \leq (x \oplus y) \lhd (x \oplus z)$.
@@
 
-To prove completeness of the cut-free fragment of SMAV, we will
-construct a particular MAV-algebra from the formulas and cut-free
-proofs. Since cut-free proofs do not a priori have all the necessary
-structure for an MAV-algebra, we develop a procedure to construct
-MAV-algebra from the lighter requirements of an MAV-frame, defined in
-this section. MAV-frames have an intuitive reading as a kind of
-process algebra, so we use process algebra-like notation. In the
-following sections, we show how every MAV-frame induces an
-MAV-algebra, and in Section XXX we will show that the MAV-algebra
-constructed from the cut-free proof MAV-frame allows us to prove that
-all proofs in SMAV have cut-free normal forms.
+To prove completeness of the normal proofs of MAV, we will construct a
+particular MAV-algebra from the formulas and normal proofs. Since
+normal proofs do not {\it a priori} have all the necessary structure
+for an MAV-algebra, in the following sections we develop a procedure
+to construct MAV-algebra from the lighter requirements of an
+MAV-frame. In Section \ref{sec:mav-cut-elimination} we will show that
+the MAV-algebra constructed from the normal proof MAV-frame allows us
+to prove that all proofs in MAV can be normalised to normal proofs.
 
 \begin{definition}
-  An \emph{MAV-frame} is a structure
-  $(F, \leq, I, \parallel, \lhd, +)$ where $(F, \leq)$ is a partial
-  order, $(F, \leq, I, \parallel)$ is a commutative pomonoid,
-  $(F, \leq, I, \lhd)$ is a pomonoid, $+$ is a binary monotone
-  function on $(F, \leq)$, and these data satisfy the following
-  inequalities:
+  An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, I, +)$
+  where $(F, \leq)$ is a partial order, $(F, \leq, \parr, I)$ is a
+  commutative pomonoid, $(F, \leq, \lhd, I)$ is a pomonoid, $+$ is a
+  binary monotone function on $(F, \leq)$, and these data satisfy the
+  following inequalities:
   \begin{enumerate}
-    \item $(w \lhd x) \parallel (y \lhd z) \leq (w \parallel y) \lhd (x \parallel z)$
-    \item $(x + y) \parallel z \leq (x \parallel z) + (y \parallel z)$
+    \item $(w \lhd x) \parr (y \lhd z) \leq (w \parr y) \lhd (x \parr z)$
+    \item $(x + y) \parr z \leq (x \parr z) + (y \parr z)$
     \item $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$
@@
 \begin{remark}
-  MAV-frames have a intuitive reading as a CCS-like process algebra
+  MAV-frames have a intuitive reading as CCS-like process algebras
   (see Milner \cite{milner89} for an introduction to CCS). If we
@@
   $a \in F$ and their duals $\overline{a} \in F$, satisfying
-  $a \parallel \overline{a} \leq I$, then we can read the constructs
-  of an MAV-frame as parallel composition, sequential composition, and
+  $a \parr \overline{a} \leq I$, then we can read the constructs of an
+  MAV-frame as parallel composition, sequential composition, and
   choice. The ordering is interpreted as a reduction relation. An
@@
 
-\begin{proposition}\label{prop:cfmav-frame}
-  The \emph{cut-free MAV-frame} $\textsc{CFMav}$ is the partial order
-  arising as the quotient of the preorder formed from the formulas of
-  MAV and $P \leq Q$ if $P \longrightarrow^* Q$. Define
-  $P \parallel Q = P \vParr Q$, $P \lhd Q = P \vSeq Q$,
+\newcommand{\NMAV}{\textsc{NMav}}
+
+\begin{proposition}\label{prop:nmav-frame}
+  The \emph{normal proof MAV-frame} \NMAV is the partial order arising
+  as the quotient of the preorder formed from the formulas of MAV and
+  $P \leq Q$ if there is a normal derivation $P \longrightarrow^*
+  Q$. Define $P \parr Q = P \vParr Q$, $P \lhd Q = P \vSeq Q$,
   $P + Q = P \vWith Q$ and $I = \vUnit$. The required (in)equalities
@@
   recovered by duality from the other connectives by the constructions
-  in the rest of this section. \bob{Which one is ``positive'' again?}
+  in the rest of this section.
 \end{remark}
@@
 partial order. This construction creates joins freely, so we restrict
-to $+$-closed lower sets in Section \ref{sec:closed-lower-sets}, which
-separates the Day construction of pomonoids into two separate
-cases. Finally, we create the $*$-autonomous structure using the Chu
-construction in Section \ref{sec:chu}. We maintain the duoidal
-structure through each construction.
+to $+$-closed lower sets in Section \ref{sec:closed-lower-sets} to
+turn the $+$ operation in MAV-frames into joins. Restricting to
+$+$-closed lower sets separates the Day construction of pomonoids into
+two separate cases, depending on how the original pomonoid interacts
+with $+$. Finally, we create the $*$-autonomous structure using the
+Chu construction in Section \ref{sec:chu}. The necessary duoidal
+structure is maintained through each construction.
 
@@
   \begin{enumerate}
-  \item $(\Day{\bullet}, \Day{i})$ is left and right residuated: there
-    exists a function
-    $\Day{\rightblackspoon} : \LowerSet{A} \times \LowerSet{A} \to
-    \LowerSet{A}$ such that ... \bob{FIXME}
   \item If $(\bullet, i)$ is a commutative pomonoid, then so is
-    $(\Day{\bullet}, \Day{i})$. In this case, the residuals coincide.
+    $(\Day{\bullet}, \Day{i})$.
+  \item $(\Day{\bullet}, \Day{i})$ has left and right residuals, which
+    coincide when it is commutative. We will only be interested in
+    residuals for commutative pomonoids, which we write as
+    $F \rightblackspoon G$.
   \item The embedding preserves the monoid:
@@
   \ref{prop:day-construction} gives us two pomonoids
-  $(\Day{\parallel}, \Day{I})$ and $(\Day{\lhd}, \Day{I})$ on
+  $(\Day{\parr}, \Day{I})$ and $(\Day{\lhd}, \Day{I})$ on
   $\LowerSet{A}$. Moreover, the next proposition states that the
@@
 handle pomonoids that are entopic under $+$. We need these
-constructions to lift the $\parallel$ and $\lhd$ pomonoids from
+constructions to lift the $\parr$ and $\lhd$ pomonoids from
 MAV-frames to $+$-closed lower sets. Finally in this section, we show
@@
   \ref{sec:mav-cut-elimination}.
-
-  \bob{Not an equality, I think, because $+$ isn't necessarily a join.}
 \end{remark}
@@
 \begin{proof}
-  We can define an operation
+  Define an operation
   $\bullet^c : \mathrm{ctxt}(F) \times \mathrm{ctxt}(G) \to
@@
   $(\ClosedLowerSet{A}, \subseteq)$. Moreover,
-  $\eta^+(x \lhd y) = \eta^+(x) \ClosedDay{\lhd} \eta^+(y)$.
+  $\eta^+(x \lhd y) \leq \eta^+(x) \ClosedDay{\lhd} \eta^+(y)$.
 \end{proposition}
@@
 \begin{proof}
-  Since $+$ is entropic over $(\lhd, j)$, the Day monoid $\Day{\lhd}$
-  is automatically $+$-closed. The monoid structure directly
-  transfers. Similarly, $\eta(j)$ is automatically $+$-closed since
-  $j + j \leq j$.
+  Since $+$ is duoidal over $(\lhd, j)$, the Day monoid $\Day{\lhd}$
+  is automatically $+$-closed by calculation. The monoid structure
+  directly transfers. Similarly, $\eta(j)$ is automatically $+$-closed
+  since $j + j \leq j$.
 \end{proof}
@@
   be constructed by Proposition \ref{prop:closed-monoid-distrib}; and
-  a non-symmetric operator like $\lhd$ will be entropic with respect
-  to $+$ and so $\ClosedDay{\lhd}$ will be constructed by Proposition
+  a non-symmetric operator like $\lhd$ will be duoidal under $+$ and
+  so $\ClosedDay{\lhd}$ will be constructed by Proposition
   \ref{prop:closed-monoid-duoidal}.
@@
 \begin{proposition}
-  Let $(\bullet, i)$ and $(\lhd, j)$ be pomonoids on $(A, \leq)$ in a
-  duoidal relationship, and assume that $(\bullet, i)$ distributes
-  over $+$ (as in Proposition \ref{prop:closed-monoid-distrib}) and
-  $+$ is entropic over $(\lhd, j)$ (as in Proposition
-  \ref{prop:closed-monoid-duoidal}). Then
-  $(\ClosedDay{\bullet}, \ClosedDay{i})$ and
-  $(\ClosedDay{\lhd}, \ClosedDay{j})$ are in a duoidal relationship on
+  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ be pomonoids on
+  $(A, \leq)$, and $(\bullet, i)$ distributes over $+$ (as in
+  Proposition \ref{prop:closed-monoid-distrib}) and $+$ is duoidal
+  over $(\lhd, j)$ (as in Proposition
+  \ref{prop:closed-monoid-duoidal}), then
+  $(\ClosedDay{\bullet}, \ClosedDay{i})$ is duoidal over
+  $(\ClosedDay{\lhd}, \ClosedDay{j})$ on
   $(\ClosedLowerSet{A}, \subseteq)$.
@@
 \begin{proof}
-  The entropic relationship established in Proposition
+  The duoidal relationship established in Proposition
   \ref{prop:lower-set-duoidal} carries over thanks to the properties
@@
 with pullbacks. In the partial order case, the requirement for
-pullbacks simplifies to binary meets. Therefore, for this section, we
+pullbacks simplifies to binary meets. For this section, we
 let $(A, \leq, \bullet, i, \rightblackspoon)$ be a partial order with
@@
   ordering $(a^+,a^-) \sqsubseteq (b^+, b^-)$ when $a^+ \leq b^+$ and
-  $b^- \leq a^-$.
+  $b^- \leq a^-$. There is a monotone embedding function
+  $\ChuEmbed : A \to \Chu(A, k)$ defined as
+  $\ChuEmbed(x) = (x, x \rightblackspoon k)$.
 \end{definition}
@@
   \end{displaymath}
+  Moreover,
+  $\ChuEmbed(x \bullet y) = \ChuEmbed(x) \otimes \ChuEmbed(y)$ and
+  $\ChuEmbed(i) = I$.
 \end{proposition}
@@
 \begin{proposition}\label{prop:chu-meets}
-  If $A$ has binary joins, then $(\Chu(A, k), \sqsubseteq) x$ has
+  If $A$ has binary joins, then $(\Chu(A, k), \sqsubseteq)$ has
   binary meets, given by
@@
 \begin{remark}
-  Since $(\Chu(A, k), \sqsubseteq)$ is a $*$-autonomous partial order,
-  then Proposition \ref{prop:chu-meets} also means that $\Chu(A, k)$
-  has all binary joins, with
+  Since $(\Chu(A, k), \sqsubseteq, \otimes, I, \lnot)$ is a
+  $*$-autonomous partial order, then Proposition \ref{prop:chu-meets}
+  also means that $\Chu(A, k)$ has all binary joins, with
   $(a^+, a^-) \oplus (b^+, b^-) = (a^+ \lor b^+, a^- \land b^-)$.
@@
 \begin{proposition}\label{prop:chu-self-dual}
-  Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that $(\bullet, i)$ is entropic over 
-  $k \lhd k \leq k$ and $j \leq k$, then
-  $x \lhd y = (x^+ \lhd y^+, x^- \lhd y^-)$ and $J = (j, j)$ form a
-  self-dual pomonoid on $\Chu(A, k)$.
+  Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that
+  $(\bullet, i)$ is duoidal over $k \lhd k \leq k$ and $j \leq k$,
+  then $x \lhd y = (x^+ \lhd y^+, x^- \lhd y^-)$ and $J = (j, j)$ form
+  a self-dual pomonoid on $\Chu(A, k)$.
 \end{proposition}
@@
   arising as the dual of that for $\otimes$ in a $*$-autonomous
-  partial order.
+  partial order, as we saw in Proposition
+  \ref{prop:mav-algebra-consequences}.
 \end{remark}
@@
 \begin{proposition}
-  If $(\bullet, i)$ is entropic over $(\lhd, j)$ on $(A, \leq)$, and
+  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
   $(\lhd, j)$ satisfies the conditions of Proposition
@@
   For the positive half of the Chu construction, this is a direct
-  consequence of the entropy on $(A, \leq)$. For the negative half, we
+  consequence of the duoidal relationship. For the negative half, we
   use Lemma \ref{lem:duoidal-residual} and the fact that meets are
@@
 \begin{theorem}
-  If $(F, \leq, \parallel, \lhd, I, +)$ is an MAV-frame, then
+  If $(F, \leq, \parr, \lhd, I, +)$ is an MAV-frame, then
   $(\Chu(\ClosedLowerSet{F}, I), \sqsubseteq)$ has the structure of an
@@
 \begin{proof}
-  Combining all the propositions above, in the special case when some
-  of the units collapse.
+  Combining the propositions above, in the special case of the units
+  of the two pomonoids being equal.
 \end{proof}

### 2024-03-27 doc/sections/mav-cut-elimination.tex
[ tex ] various fixes

@@
 Let $\Chu(\ClosedLowerSet{\NMAV}, \ClosedDay{I})$ be the MAV-algebra
-constructed from the normal proof MAV-frame (Proposition
-\ref{prop:nmav-frame}), where elements are positive/negative pairs of
-$+$-closed lower sets of formulas. We define the valuation of atoms as
+constructed (Theorem \ref{thm:algebra-from-frame}) from the normal
+proof MAV-frame (Proposition \ref{prop:nmav-frame}), where elements
+are positive/negative pairs of $+$-closed lower sets of formulas. We
+define the valuation of atoms as
 $V(\alpha) = \ChuEmbed(\ClosedLowerEmbed(\vDual{\alpha}))$. By Theorem
 \ref{thm:soundness}, we have an interpretation of MAV formulas
-$\sem{P}$ such that if $P \longrightarrow^* I$, then $I \leq
-\sem{P}$. We now prove our main proposition about the MAV-algebra
-\NMAV{} that will allow us to derive the admissibility of all the
-non-normal proof rules of MAV.
+$\sem{P}$ such that if $P \longrightarrow^* I$, then
+$I \sqsubseteq \sem{P}$. We now prove our main proposition about this
+interpretation in the MAV-algebra derived from the MAV-frame of normal
+proofs \NMAV{} that will allow us to derive the admissibility of all
+the non-normal proof rules of MAV.
 
@@
 \begin{proof}
-  By the definition of the Chu construction, this statement breaks
-  down into two inclusions between pairs of $+$-closed lower sets:
+  By Definition \ref{defn:chu}, this statement is two inclusions
+  between pairs of $+$-closed lower sets:
   \begin{enumerate}
@@
   We prove the second assuming the first. It suffices to prove that
-  $\sem{\vP}^+ \ClosedDay{\bullet} \ClosedLowerEmbed(P) \leq
+  $\sem{\vP}^+ \ClosedDay{\bullet} \ClosedLowerEmbed(P) \subseteq
   \ClosedDay{I}$, which follows from the first part and the property
   of all Chu-elements that
-  $\sem{\vP}^+ \ClosedDay{\bullet} \sem{\vP}^- \leq \ClosedDay{I}$.
+  $\sem{\vP}^+ \ClosedDay{\bullet} \sem{\vP}^- \subseteq \ClosedDay{I}$.
 
@@
   $\ClosedLowerEmbed(\alpha) \ClosedDay{\bullet}
-  \ClosedLowerEmbed(\vDual{\alpha}) \leq \ClosedDay{I}$, which follows
+  \ClosedLowerEmbed(\vDual{\alpha}) \subseteq \ClosedDay{I}$, which follows
   from the preservation of monoid operations by $\ClosedLowerEmbed$
@@
   $\ClosedLowerEmbed$. For example,
-  $\ClosedLowerEmbed(Q \vParr R) \leq \ClosedLowerEmbed(Q)
-  \ClosedDay{\bullet} \ClosedLowerEmbed(R) \leq \sem{Q}^-
+  $\ClosedLowerEmbed(Q \vParr R) \subseteq \ClosedLowerEmbed(Q)
+  \ClosedDay{\bullet} \ClosedLowerEmbed(R) \subseteq \sem{Q}^-
   \ClosedDay{\bullet} \sem{R}^- = \sem{Q \vParr R}^-$.
@@
   When $P = Q \vPlus R$, we have
-  $\ClosedLowerEmbed(Q \vPlus R) \leq \ClosedLowerEmbed(Q)$ and
-  $\ClosedLowerEmbed(Q \vPlus R) \leq \ClosedLowerEmbed(R)$, by the
+  $\ClosedLowerEmbed(Q \vPlus R) \subseteq \ClosedLowerEmbed(Q)$ and
+  $\ClosedLowerEmbed(Q \vPlus R) \subseteq \ClosedLowerEmbed(R)$, by the
   \RuleLabel{Left} and \RuleLabel{Right} rules. Therefore,
-  $\ClosedLowerEmbed(Q \vPlus R) \leq \ClosedLowerEmbed(Q) \lor
-  \ClosedLowerEmbed(R) \leq \sem{Q}^- \lor \sem{R}^- = \sem{Q \vPlus
+  $\ClosedLowerEmbed(Q \vPlus R) \subseteq \ClosedLowerEmbed(Q) \lor
+  \ClosedLowerEmbed(R) \subseteq \sem{Q}^- \lor \sem{R}^- = \sem{Q \vPlus
     R}^-$.
@@
   (\sem{R}^+ \rightblackspoon \sem{Q}^-)$. We prove inclusion in the
-  left-hand side, the right-hand side is similar. The key property we need to prove is:
+  left-hand side, the right-hand side is similar. The key property we
+  need to prove is:
   \begin{equation}\label{eq:interaction-leq}
     \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
-    \leq
+    \subseteq
     \ClosedLowerEmbed(R)
   \end{equation}
-  Using the monoidality and monotonicity of $\alpha$, this property is
-  implied by the following property of lower sets in
-  $\LowerSet{\NMAV}$:
+  Using the monoidality and monotonicity of $\alpha$, this inclusion
+  is implied by the following inclusion in $\LowerSet{\NMAV}$:
   \begin{displaymath}
     \LowerEmbed(Q \vTens R) \Day{\bullet} (U(\ClosedLowerEmbed(Q)) \rightblackspoon \Day{I})
-    \leq
+    \subseteq
     \LowerEmbed(R)
@@
   which follows from the \RuleLabel{Switch} rule of MAV and
-  calculation. Using Inequation \ref{eq:interaction-leq}, and property
-  (ii) above, we can prove the inequality we need:
+  calculation. Using \ref{eq:interaction-leq}, and inclusion (ii)
+  above, we can prove the inequality we need:
   \begin{displaymath}
     \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} \sem{Q}^+
-    \leq
+    \subseteq
     \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
-    \leq
+    \subseteq
     \ClosedLowerEmbed(R)
-    \leq
+    \subseteq
     \sem{R}^-
@@
   By Theorem \ref{thm:soundness}, $P \longrightarrow^* I$ in MAV
-  implies $I \leq \sem{P}$. Combined with Proposition
+  implies $I \sqsubseteq \sem{P}$. Combined with Proposition
   \ref{prop:embedding-sem}, we have

### 2024-03-27 doc/sections/mav-semantics.tex
[ tex ] various fixes

@@
 \begin{proposition}
-  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ be pomonoids on
-  $(A, \leq)$, and $(\bullet, i)$ distributes over $+$ (as in
-  Proposition \ref{prop:closed-monoid-distrib}) and $+$ is duoidal
-  over $(\lhd, j)$ (as in Proposition
-  \ref{prop:closed-monoid-duoidal}), then
-  $(\ClosedDay{\bullet}, \ClosedDay{i})$ is duoidal over
+  If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
+  $(\bullet, i)$ distributes over $+$ (as in Proposition
+  \ref{prop:closed-monoid-distrib}) and $+$ is duoidal over
+  $(\lhd, j)$ (as in Proposition \ref{prop:closed-monoid-duoidal}),
+  then $(\ClosedDay{\bullet}, \ClosedDay{i})$ is duoidal over
   $(\ClosedDay{\lhd}, \ClosedDay{j})$ on
@@
 
-To construct suitable MAV-algebras, we use the poset version of the
-Chu construction \cite{barr}. The Chu construction builds
+To construct suitable MAV-algebras, we use the partial order version
+of the Chu construction \cite{barr}. The Chu construction builds
 $*$-autonomous categories from symmetric monoidal closed categories
 with pullbacks. In the partial order case, the requirement for
-pullbacks simplifies to binary meets. For this section, we
-let $(A, \leq, \bullet, i, \rightblackspoon)$ be a partial order with
-a residuated pomonoid structure and all binary meets.
+pullbacks simplifies to binary meets. For this section, we let
+$(A, \leq, \bullet, i, \rightblackspoon)$ be a partial order with a
+residuated pomonoid structure and all binary meets.
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:algebra-from-frame}
   If $(F, \leq, \parr, \lhd, I, +)$ is an MAV-frame, then

### 2024-03-28 doc/sections/mav-cut-elimination.tex
[ tex ] finish off the semantics and cut elimination sections

@@
 \end{proof}
+
+Another consequence of Proposition \ref{prop:embedding-sem} is that
+MAV is complete for the MAV-frame semantics:
+
+\begin{theorem}\label{thm:completeness}
+  MAV is complete for the MAV-frame semantics: if, for all MAV-frames
+  $F$, $\sem{I} \sqsubseteq \sem{P}$ in
+  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{I}), \sqsubseteq)$, then
+  $P \longrightarrow^* I$.
+\end{theorem}

### 2024-03-28 doc/sections/mav-semantics.tex
[ tex ] more fixes
[ tex ] finish off the semantics and cut elimination sections

@@
 
-\bob{Short introduction to the section here}
+To prove the normalisation property for all MAV proofs, we use a
+semantic technique that is akin to Okada's phase space method and to
+Normalisation by Evaluation (NbE). We construct a semantics of the
+whole proof system from the system of normal proofs. This semantics is
+constructed in such a way that after interpreting a proof, the
+(existence of) a normal form can be extracted (or \emph{read back} or
+\emph{reified} in NbE terminology) from the semantic proof.
 
-\begin{itemize}
-\item We construct algebraic models of MAV
-\item MAV-algebras are algebras that MAV is sound for. In some
-  sense, this is straightforward, but we identify precisely the
-  structure that is needed.
-\item The key structure is duoidality.
-\item We develop some model theory here, and show that MAV-algebras
-  can be induced by the weaker structure of MAV-frames. This is
-  essential for the cut-free elimination proof.
-\end{itemize}
+To our knowledge, the semantics of MAV have not been previously
+studied in the literature. The rules are an extension of MALL, so an
+\emph{MAV-algebra} will partly xbe a $*$-autonomous partial order
+(Definition \ref{defn:star-autonomous}) with meets and joins. The
+additional structure for the $\vP \vSeq \vQ$ connective satisfies the
+conditions of a duoidal category \cite{hopf-book} (Definition
+\ref{defn:duoidal}). We show that MAV is sound for MAV-algebras in
+Theorem \ref{thm:soundness}.
+
+To build MAV-algebras from normal proofs, we define the weaker notion
+of an \emph{MAV-frame} (Definition \ref{defn:mav-frame}. We then show
+that a combination of certain closed lower sets (Section
+\ref{sec:closed-lower-sets}) and the Chu construction (Section
+\ref{sec:chu}) construct an MAV-algebra from any MAV-frame. Much of
+these constructions are well-known, but we have new results on lifting
+the Day construction of monoids on closed lower sets and the
+preservation of duoidal relationships that are required for MAV.
 
@@
 
-\begin{definition}
+\begin{definition}\label{defn:pomonoid}
   A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
@@
 
-\begin{definition}
+\begin{definition}\label{defn:residual}
   A commutative pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is
@@
 
-\begin{definition}
+\begin{definition}\label{defn:star-autonomous}
   A \emph{$*$-autonomous partial order} is a structure
@@
 
-\begin{definition}
+\begin{definition}\label{defn:duoidal}
   A pomonoid $(\bullet, i)$ is \emph{duoidal over} another pomonoid
@@
   \begin{enumerate}
-    \item There is another pomonoid structure $(\parr, I)$ on
+    \item There is another commutative pomonoid structure $(\parr, I)$ on
           $(A, \leq)$, defined as
@@
     \item $\oplus$ distributes over $\otimes$:
-          $x \otimes (y \oplus z) = ((x \otimes y) \oplus (x \otimes z)$.
+          $x \otimes (y \oplus z) = (x \otimes y) \oplus (x \otimes z)$.
     \item $\with$ distributes over $\parr$:
@@
 
-\begin{definition}
+\begin{definition}\label{defn:mav-frame}
   An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, I, +)$
@@
 
+The propositions in the preceeding three sections together prove that
+every MAV-frame yields an MAV-algebra:
+
 \begin{theorem}\label{thm:algebra-from-frame}
   If $(F, \leq, \parr, \lhd, I, +)$ is an MAV-frame, then
-  $(\Chu(\ClosedLowerSet{F}, I), \sqsubseteq)$ has the structure of an
+  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{I}), \sqsubseteq)$ has the structure of an
   MAV-algebra.
@@
 
-\begin{proof}
-  Combining the propositions above, in the special case of the units
-  of the two pomonoids being equal.
-\end{proof}
+With this theorem we can define a notion of validity in MAV in terms
+of truth in all MAV-frame generated algebras. By Theorem
+\ref{thm:soundness}, MAV is sound for this notion of validity:
+
+\begin{theorem}\label{thm:mavframe-soundness}
+  MAV is sound for the MAV-frame semantics: if $P \longrightarrow^* I$
+  then for all MAV-frames $F$, $\sem{I} \sqsubseteq \sem{P}$ in
+  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{I}), \sqsubseteq)$.
+\end{theorem}

### 2024-03-28 doc/sections/introduction.tex
Minor fixes

@@
 }~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
+The proof is constructive and mechanised in Agda~\cite{Agda264}.
 
@@
 The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
-The phase space model defines duals by means of double negation with respect to the monoidal structure, which means that attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
-\wen{%
-      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
-\bob{%
-      I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely.
-So I think it is unlikely that phase spaces can be adapted to BV.}
-\wen{%
-      Gave it a shot.}
+The phase space model derives duals by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
+Attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.

### 2024-03-28 doc/sections/mav-mechanisation.tex
Minor fixes

@@
 We developed the proof in the previous two sections in the Agda proof
-assistant \cite{agda}. The source code for this development is
+assistant \cite{Agda264}. The source code for this development is
 available at this URL:
@@
 The formalisation uses setoids to represent sets, reusing definitions
-from the Agda Standard Library \cite{agda-stdlib}. Each of the
+from the Agda Standard Library \cite{AgdaStdlib20}. Each of the
 definitions and propositions above links to the corresponding part of

### 2024-03-28 doc/sections/mav-syntax.tex
Minor fixes

@@
   \end{array}
+\end{displaymath}
+Structure contexts are one-hole contexts over structures. Plugging ($\vC\vPlug\vP$) replaces the hole in $\vC$ with $\vP$.
+\begin{displaymath}
+  \vC,\vD
+  \Coloneq \vEmpty
+  \mid     \vC\vSeq \vQ
+  \mid     \vP\vSeq \vD
+  \mid     \vC\vTens\vQ
+  \mid     \vP\vTens\vD
+  \mid     \vC\vParr\vQ
+  \mid     \vP\vParr\vD
+  \mid     \vC\vWith\vQ
+  \mid     \vP\vWith\vD
+  \mid     \vC\vPlus\vQ
+  \mid     \vP\vPlus\vD
 \end{displaymath}
@@
   \end{center}
+  The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
 \end{remark}

### 2024-03-28 doc/sections/mav-syntax.tex
Minor changes

@@
 
-A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and \cref{rule:Axiom} is restricted to \cref{rule:AtomAxiom}.
+\begin{definition}\label{defn:normal}
+  A derivation is \emph{normal} when it does not use \cref{rule:Cut} and its uses of \cref{rule:Axiom} are restricted to \cref{rule:AtomAxiom}, as defined by the following axiom:
   \begin{displaymath}
@@
   \end{displaymath}
-These restrictions correspond to the outcome of cut elimination and identity expansion, respectively.
+\end{definition}
+(The restrictions on normal derivations correspond to the result of cut elimination and identity expansion.)
 \begin{remark}

### 2024-03-29 doc/sections/mav-syntax.tex
[ agda tex ] Symmetric rules everywhere

--- 2024-03-28 doc/sections/mav-syntax.tex
@@
     \\
+    (\vP\vTens\vQ)\vParr\vR
+     & \vInferFrom
+     & \vP\vTens(\vQ\vParr\vR)
+     & \RuleLabel{Switch}
+    \\
     \vUnit\vWith\vUnit
@@
     \\
-    (\vP\vTens\vQ)\vParr\vR
+    \vUnit
      & \vInferFrom
-     & \vP\vTens(\vQ\vParr\vR)
-     & \RuleLabel{Switch}
+     & \vUnit \vPlus \vUnit
+     & \RuleLabel{CoTidy}
     \\
@@
     \\
+    (\vP\vTens\vR)\vSeq(\vQ\vTens\vS)
+     & \vInferFrom
+     & (\vP\vSeq\vQ)\vTens(\vR\vSeq\vS)
+     & \RuleLabel{CoSequence}
+    \\
     \vP\vPlus\vQ
@@
      & \RuleLabel{Left}
+    \\
+    \vP
+     & \vInferFrom
+     & \vP\vWith\vQ
+     & \RuleLabel{CoLeft}
     \\
@@
     \\
+    \vQ
+     & \vInferFrom
+     & \vP\vWith\vQ
+     & \RuleLabel{CoRight}
+    \\
     (\vP\vWith\vQ)\vParr\vR
@@
     \\
+    (\vP \vTens \vR) \vPlus (\vQ \vTens \vR)
+     & \vInferFrom
+     & (\vP \vPlus \vQ) \vTens \vR
+     & \RuleLabel{CoExternal}
+    \\
     (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
@@
      & \RuleLabel{Medial}
+    \\
+    (\vP \vPlus \vR) \vSeq (\vQ \vPlus \vS)
+     & \vInferFrom
+     & (\vP \vSeq \vQ) \vPlus (\vR \vSeq \vS)
+     & \RuleLabel{CoMedial}
     \\
@@
 
-\emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
-\emph{Invertible inference}, written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.
-\emph{Invertible derivation}, written $\vBiInfer*$, is the symmetric core of derivation, or, alternatively, the reflexive, transitive closure of invertible inference.
-\emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
+Note that, except for \cref{rule:Switch}, the rules come in pairs that are dual, in the sense that if a rule is of the form $P \vInferFrom Q$, then its partner is of the form $\vDual{P} \vInferFrom \vDual{Q}$.
+The \cref{rule:Switch} rule is, up to commutativity, already its own dual.
+The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new formulas going left-to-right.
+Normal proofs, which we define below, avoid these \emph{synthetic} rules.
 
-A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and \cref{rule:Axiom} is restricted to \cref{rule:AtomAxiom}.
-\begin{displaymath}
-  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
-    \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
-     & \vInferFrom
-     & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
-     & \RuleLabel{AtomAxiom}
-  \end{array}
-\end{displaymath}
-These restrictions correspond to the outcome of cut elimination and identity expansion, respectively.
+\begin{definition}
+  \emph{Derivation}, written $\vInferFrom*$ is the reflexive,
+  transitive closure of inference.  \emph{Invertible inference},
+  written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie
+  ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.  \emph{Invertible
+    derivation}, written $\vBiInfer*$, is the symmetric core of
+  derivation, or, alternatively, the reflexive, transitive closure of
+  invertible inference.  \emph{Proofs} are derivations that terminate
+  in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of
+  $\vP$.
+\end{definition}
+
 \begin{remark}
@@
 \end{remark}
+
+\begin{definition}\label{defn:normal}
+  A derivation is \emph{normal} when it does not use \cref{rule:Cut} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Axiom} are restricted to \cref{rule:AtomAxiom}, as defined by the following axiom:
+  \begin{displaymath}
+    \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
+      \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
+       & \vInferFrom
+       & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
+       & \RuleLabel{AtomAxiom}
+    \end{array}
+  \end{displaymath}
+\end{definition}
+Normal derivations avoid the use of rules that introduce new formulas into proofs, and so can be termed \emph{analytic} in contrast to the need for the synthetic rules to synthesise new formulas.
+
+Our main result, Theorem \ref{thm:cut-elim}, is that every formula that is provable in full MAV also has a normal proof.
+Therefore, the system with only analytic rules is complete for MAV provability.
+Horne \cite{Horne15:mav} proves this result via a syntactic proof involving rewriting and termination measures.
+In the following sections, we construct a semantic proof that normal proofs are complete for MAV.

### 2024-03-29 doc/sections/introduction.tex
Part of pushing through syntactic stuff

@@
 MAV and BV are \emph{deep inference} systems.
-Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to linear logic~\cite{Girard87:ll}.
+Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to classical linear logic~\cite[CLL]{Girard87:ll}.
 The problem with such a relation is that, while the multiplicative connectives of linear logic capture parallel composition, no connective of linear logic captures \emph{sequential composition}.

### 2024-03-29 doc/sections/mav-cut-elimination.tex
[ tex ] typos and small fixes
Part of pushing through syntactic stuff

--- 2024-03-27 doc/sections/mav-cut-elimination.tex
@@
 Let $\Chu(\ClosedLowerSet{\NMAV}, \ClosedDay{I})$ be the MAV-algebra
-constructed (Theorem \ref{thm:algebra-from-frame}) from the normal
-proof MAV-frame (Proposition \ref{prop:nmav-frame}), where elements
+constructed (\Cref{thm:algebra-from-frame}) from the normal
+proof MAV-frame (\Cref{prop:nmav-frame}), where elements
 are positive/negative pairs of $+$-closed lower sets of formulas. We
 define the valuation of atoms as
-$V(\alpha) = \ChuEmbed(\ClosedLowerEmbed(\vDual{\alpha}))$. By Theorem
-\ref{thm:soundness}, we have an interpretation of MAV formulas
-$\sem{P}$ such that if $P \longrightarrow^* I$, then
-$I \sqsubseteq \sem{P}$. We now prove our main proposition about this
+$V(\va) = \ChuEmbed(\ClosedLowerEmbed(\vDual\va))$. By
+\Cref{thm:soundness}, we have an interpretation of MAV formulas
+$\sem{\vP}$ such that if $\vP\vInferFrom*\vUnit$, then
+$I \sqsubseteq \sem{\vP}$. We now prove our main proposition about this
 interpretation in the MAV-algebra derived from the MAV-frame of normal
@@
 
-\begin{proposition}\label{prop:embedding-sem}
-  $\sem{P} \sqsubseteq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$
+\begin{proposition}\label[prop]{prop:embedding-sem}
+  $\sem{\vP} \sqsubseteq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$
 \end{proposition}
@@
 \begin{proof}
-  By Definition \ref{defn:chu}, this statement is two inclusions
+  By \Cref{defn:chu}, this statement is two inclusions
   between pairs of $+$-closed lower sets:
@@
 
-  We prove the first part by induction on $P$. In the cases when
-  $P = \vUnit$ or $P = \vDual{\alpha}$, we already have
-  $\sem{P}^- = \ClosedLowerEmbed(P)$. When $P = \alpha$, we have
-  $\sem{\alpha}^- = \ClosedLowerEmbed(\vDual{\alpha})
+  We prove the first part by induction on $\vP$.
+  In the cases when $\vP = \vUnit$ or $\vP = \vDual\va$, we already have
+  $\sem{\vP}^- = \ClosedLowerEmbed(P)$. When $\vP = \va$, we have
+  $\sem{\va}^- = \ClosedLowerEmbed(\vDual\va)
     \rightblackspoon^+ \ClosedDay{I}$. It suffices to prove that
-  $\ClosedLowerEmbed(\alpha) \ClosedDay{\bullet}
-  \ClosedLowerEmbed(\vDual{\alpha}) \subseteq \ClosedDay{I}$, which follows
-  from the preservation of monoid operations by $\ClosedLowerEmbed$
-  and the \RuleLabel{Axiom} rule of MAV.
+  $\ClosedLowerEmbed(\va) \ClosedDay{\bullet}
+    \ClosedLowerEmbed(\vDual\va) \subseteq \ClosedDay{I}$, which
+  follows from the preservation of monoid operations by
+  $\ClosedLowerEmbed$ and the \cref{rule:AtomAxiom} rule.
 
-  When $P = Q \vParr R$, $Q \vWith R$, or $Q \vSeq R$, the result
+  When $\vP = \vQ\vParr\vR$, $\vQ\vWith\vR$, or $\vQ\vSeq\vR$, the result
   follows from preservation of the corresponding monoid structure by
   $\ClosedLowerEmbed$. For example,
-  $\ClosedLowerEmbed(Q \vParr R) \subseteq \ClosedLowerEmbed(Q)
-  \ClosedDay{\bullet} \ClosedLowerEmbed(R) \subseteq \sem{Q}^-
-  \ClosedDay{\bullet} \sem{R}^- = \sem{Q \vParr R}^-$.
+  $\ClosedLowerEmbed(\vQ\vParr\vR) \subseteq \ClosedLowerEmbed(\vQ)
+    \ClosedDay{\bullet} \ClosedLowerEmbed(\vR) \subseteq \sem{\vQ}^-
+    \ClosedDay{\bullet} \sem{\vR}^- = \sem{\vQ\vParr\vR}^-$.
 
-  When $P = Q \vPlus R$, we have
-  $\ClosedLowerEmbed(Q \vPlus R) \subseteq \ClosedLowerEmbed(Q)$ and
-  $\ClosedLowerEmbed(Q \vPlus R) \subseteq \ClosedLowerEmbed(R)$, by the
-  \RuleLabel{Left} and \RuleLabel{Right} rules. Therefore,
-  $\ClosedLowerEmbed(Q \vPlus R) \subseteq \ClosedLowerEmbed(Q) \lor
-  \ClosedLowerEmbed(R) \subseteq \sem{Q}^- \lor \sem{R}^- = \sem{Q \vPlus
-    R}^-$.
+  When $\vP = \vQ\vPlus\vR$, we have
+  $\ClosedLowerEmbed(\vQ\vPlus\vR) \subseteq \ClosedLowerEmbed(\vQ)$ and
+  $\ClosedLowerEmbed(\vQ\vPlus\vR) \subseteq \ClosedLowerEmbed(\vR)$, by the
+  \cref{rule:Left} and \cref{rule:Right} rules. Therefore,
+  $\ClosedLowerEmbed(\vQ\vPlus\vR) \subseteq \ClosedLowerEmbed(\vQ) \lor
+    \ClosedLowerEmbed(\vR) \subseteq \sem{\vQ}^- \lor \sem{\vR}^- = \sem{\vQ\vPlus\vR}^-$.
 
-  When $P = Q \vTens R$, we have
-  $\sem{Q \vTens R}^- = (\sem{Q}^+ \rightblackspoon \sem{R}^-) \land
-  (\sem{R}^+ \rightblackspoon \sem{Q}^-)$. We prove inclusion in the
+  When $\vP = \vQ\vTens\vR$, we have
+  $\sem{\vQ\vTens\vR}^- = (\sem{\vQ}^+ \rightblackspoon \sem{\vR}^-) \land
+    (\sem{\vR}^+ \rightblackspoon \sem{\vQ}^-)$. We prove inclusion in the
   left-hand side, the right-hand side is similar. The key property we
@@
   \begin{equation}\label{eq:interaction-leq}
-    \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
+    \ClosedLowerEmbed(\vQ\vTens\vR) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
     \subseteq
@@
   \end{equation}
-  Using the monoidality and monotonicity of $\alpha$, this inclusion
+  Using the monoidality and monotonicity of $\va$, this inclusion
   is implied by the following inclusion in $\LowerSet{\NMAV}$:
   \begin{displaymath}
-    \LowerEmbed(Q \vTens R) \Day{\bullet} (U(\ClosedLowerEmbed(Q)) \rightblackspoon \Day{I})
+    \LowerEmbed(\vQ\vTens\vR) \Day{\bullet} (U(\ClosedLowerEmbed(Q)) \rightblackspoon \Day{I})
     \subseteq
@@
   \end{displaymath}
-  which follows from the \RuleLabel{Switch} rule of MAV and
+  which follows from the \cref{rule:Switch} rule of MAV and
   calculation. Using \ref{eq:interaction-leq}, and inclusion (ii)
@@
   \begin{displaymath}
-    \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} \sem{Q}^+
+    \ClosedLowerEmbed(\vQ\vTens\vR) \ClosedDay{\bullet} \sem{\vQ}^+
     \subseteq
-    \ClosedLowerEmbed(Q \vTens R) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
+    \ClosedLowerEmbed(\vQ\vTens\vR) \ClosedDay{\bullet} (\ClosedLowerEmbed(Q) \rightblackspoon^+ \ClosedDay{I})
     \subseteq
@@
     \subseteq
-    \sem{R}^-
+    \sem{\vR}^-
   \end{displaymath}
@@
 
-\begin{theorem}\label{thm:cut-elim}
-  If $P \longrightarrow^* I$ in MAV, then there is a normal proof $P \longrightarrow^* I$.
+\begin{theorem}\label[thm]{thm:cut-elim}
+  If $\vP\vInferFrom*\vUnit$ in MAV, then there is a normal proof $\vP\vInferFrom*\vUnit$.
 \end{theorem}
@@
 \begin{proof}
-  By Theorem \ref{thm:soundness}, $P \longrightarrow^* I$ in MAV
-  implies $I \sqsubseteq \sem{P}$. Combined with Proposition
-  \ref{prop:embedding-sem}, we have
-  $I \sqsubseteq \lnot \ChuEmbed(\LowerEmbed(P)$. By Definition
-  \ref{defn:chu} of the ordering of Chu elements, we have
-  $\ClosedLowerEmbed(P) \subseteq \ClosedDay{I}$. Since
-  $P \in \ClosedLowerEmbed(P)$, we have $P \in \ClosedDay{I}$, which
+  By \Cref{thm:soundness}, $\vP\vInferFrom*\vUnit$ in MAV
+  implies $I \sqsubseteq \sem{\vP}$. Combined with \Cref{prop:embedding-sem}, we have
+  $I \sqsubseteq \lnot \ChuEmbed(\LowerEmbed(\vP)$. By
+  \Cref{defn:chu} of the ordering of Chu elements, we have
+  $\ClosedLowerEmbed(\vP) \subseteq \ClosedDay{I}$. Since
+  $P \in \ClosedLowerEmbed(\vP)$, we have $\vP \in \ClosedDay{I}$, which
   by definition means that there is a normal proof
-  $P \longrightarrow^* I$.
+  $\vP\vInferFrom*\vUnit$.
 \end{proof}
+
+Another consequence of \Cref{prop:embedding-sem} is that
+MAV is complete for the MAV-frame semantics:
+
+\begin{theorem}\label[thm]{thm:completeness}
+  MAV is complete for the MAV-frame semantics: if, for all MAV-frames
+  $F$, $\sem{\vUnit} \sqsubseteq \sem{\vP}$ in
+  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{I}), \sqsubseteq)$, then
+  $\vP\vInferFrom*\vUnit$.
+\end{theorem}

### 2024-03-29 doc/sections/mav-mechanisation.tex
Part of pushing through syntactic stuff

@@
 formalising the development in a proof assistant like Agda is that the
-proof normalisation process (Theorem \ref{thm:cut-elim}) is
+proof normalisation process (\Cref{thm:cut-elim}) is
 executable. For example, we can normalise the one step SMAV proof
-(using \RuleLabel{Axiom}) of $\vP \vParr \vDual{\vP}$ where
+(using \cref{rule:Axiom}) of $\vP \vParr \vDual{\vP}$ where
 $\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a FIXME

### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] typos and small fixes
Part of pushing through syntactic stuff

@@
 \section{Semantic Models for MAV}\label{sec:mav-semantics}
-
-\newcommand{\LowerSet}[1]{\widehat{#1}}
-\newcommand{\Day}[1]{\mathop{\widehat{#1}}}
-\newcommand{\ClosedLowerSet}[1]{\widehat{#1}^+}
-\newcommand{\ClosedDay}[1]{\mathop{\widehat{#1}^+}}
-\newcommand{\Chu}{\mathrm{Chu}}
-\newcommand{\op}{\mathrm{op}}
 
@@
 studied in the literature. The rules are an extension of MALL, so an
-\emph{MAV-algebra} will partly xbe a $*$-autonomous partial order
-(Definition \ref{defn:star-autonomous}) with meets and joins. The
-additional structure for the $\vP \vSeq \vQ$ connective satisfies the
-conditions of a duoidal category \cite{hopf-book} (Definition
-\ref{defn:duoidal}). We show that MAV is sound for MAV-algebras in
-Theorem \ref{thm:soundness}.
+\emph{MAV-algebra} will partly be a $*$-autonomous partial order
+(\Cref{defn:star-autonomous}) with meets and joins. The
+additional structure for seq satisfies the
+conditions of a duoidal category \cite{hopf-book} (\Cref{defn:duoidal}). We show that MAV is sound for MAV-algebras in
+\Cref{thm:soundness}.
 
 To build MAV-algebras from normal proofs, we define the weaker notion
-of an \emph{MAV-frame} (Definition \ref{defn:mav-frame}. We then show
-that a combination of certain closed lower sets (Section
-\ref{sec:closed-lower-sets}) and the Chu construction (Section
-\ref{sec:chu}) construct an MAV-algebra from any MAV-frame. Much of
+of an \emph{MAV-frame} (\Cref{defn:mav-frame}). We show
+that a combination of certain closed lower sets (\Cref{sec:closed-lower-sets}) and the Chu construction (\Cref{sec:chu}) construct an MAV-algebra from any MAV-frame. Much of
 these constructions are well-known, but we have new results on lifting
@@
 
-At heart, the semantics of MAV is a collection of interacting monoids
+The semantics of MAV is a collection of interacting monoids
 on a partial order. We collect here the basic definitions and kinds of
@@
 
-\begin{definition}\label{defn:pomonoid}
+\begin{definition}\label[defn]{defn:pomonoid}
   A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
@@
 
-\begin{definition}\label{defn:residual}
+\begin{definition}\label[defn]{defn:residual}
   A commutative pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is
@@
 
-Classical Linear Logic adds a duality, or negation, to a commutative
+Linear logic adds a duality, or negation, to a commutative
 pomonoid structure. Semantically, duality with commutativity is
-captured in the definition of $*$-autonomous category is, due to Barr
-\cite{Barr_1979}. For our purposes, we need the partial order
-analogue, also called a CL algebra by Troelstra
-\cite{Troelstra92:lll}.
+captured in the definition of $*$-autonomous category is, due to Barr~\cite{Barr_1979}. For our purposes, we need the partial order
+analogue, also called a CL algebra by Troelstra~\cite{Troelstra92:lll}.
 
-\begin{definition}\label{defn:star-autonomous}
+\begin{definition}\label[defn]{defn:star-autonomous}
   A \emph{$*$-autonomous partial order} is a structure
@@
   immediate consequences, but we leave description of these until
-  after the definition of MAV-algebra in Definition
-  \ref{defn:mav-algebra}.
+  after the definition of MAV-algebra in \Cref{defn:mav-algebra}.
 \end{remark}
 
-BV and MAV extend CLL by adding a non-commutative pomonoid structure
+BV and MAV extend linear logic by adding a non-commutative pomonoid structure
 that interacts with the existing pomonoid via a kind of interchange
-law (the \RuleLabel{Sequence} rule in the proof system). We follow
+law (the \cref{rule:Sequence} rule in the proof system). We follow
 \cite{hopf-book} generalising these to the case of monoids with
@@
 
-\begin{definition}\label{defn:duoidal}
+\begin{definition}\label[defn]{defn:duoidal}
   A pomonoid $(\bullet, i)$ is \emph{duoidal over} another pomonoid
@@
 
-\begin{definition}\label{defn:mav-algebra}
+\begin{definition}\label[defn]{defn:mav-algebra}
   An \emph{MAV-algebra} is a structure
@@
 
-\begin{proposition}\label{prop:mav-algebra-consequences}
+\begin{proposition}\label[prop]{prop:mav-algebra-consequences}
   Let $(A, \leq, \otimes, \lhd, I, \lnot)$ be a MAV-algebra.
@@
 
-\begin{definition}\label{defn:mav-interpretation}
+\begin{definition}\label[defn]{defn:mav-interpretation}
   Let $\mathit{At}$ be a set of atomic propositions. Given an
@@
 
-\begin{theorem}\label{thm:soundness}
-  The interpretation defined in Definition
-  \ref{defn:mav-interpretation} is sound: for all formulas $P$, if
+\begin{theorem}\label[thm]{thm:soundness}
+  The interpretation defined in \Cref{defn:mav-interpretation} is sound: for all formulas $P$, if
   $P \longrightarrow^* I$, then $I \leq \sem{P}$.
@@
   Each of the required inequalities has been established in
-  Proposition \ref{prop:mav-algebra-consequences}.
+  \Cref{prop:mav-algebra-consequences}.
 \end{proof}
@@
 to construct MAV-algebra from the lighter requirements of an
-MAV-frame. In Section \ref{sec:mav-cut-elimination} we will show that
+MAV-frame. In \Cref{sec:mav-cut-elimination} we will show that
 the MAV-algebra constructed from the normal proof MAV-frame allows us
@@
 
-\begin{definition}\label{defn:mav-frame}
+\begin{definition}\label[defn]{defn:mav-frame}
   An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, I, +)$
@@
 
-\newcommand{\NMAV}{\textsc{NMav}}
-
-\begin{proposition}\label{prop:nmav-frame}
+\begin{proposition}\label[prop]{prop:nmav-frame}
   The \emph{normal proof MAV-frame} \NMAV is the partial order arising
@@
   $\otimes$ and $\oplus$ structure of MAV directly. We will see in
-  Section \ref{sec:mav-cut-elimination} that this structure is
+  \Cref{sec:mav-cut-elimination} that this structure is
   recovered by duality from the other connectives by the constructions
@@
 We construct MAV-algebras from MAV-frames in a three step process. In
-Section \ref{sec:lower-sets}, we use lower sets and the Day
+\Cref{sec:lower-sets}, we use lower sets and the Day
 construction to add meets, joins and residuals for pomonoids to a
 partial order. This construction creates joins freely, so we restrict
-to $+$-closed lower sets in Section \ref{sec:closed-lower-sets} to
+to $+$-closed lower sets in \Cref{sec:closed-lower-sets} to
 turn the $+$ operation in MAV-frames into joins. Restricting to
@@
 with $+$. Finally, we create the $*$-autonomous structure using the
-Chu construction in Section \ref{sec:chu}. The necessary duoidal
+Chu construction in \Cref{sec:chu}. The necessary duoidal
 structure is maintained through each construction.
@@
 
-\begin{proposition}\label{prop:day-construction}
+\begin{proposition}\label[prop]{prop:day-construction}
   If $(\bullet, i)$ is a pomonoid on $(A, \leq)$, then there is a
@@
 \begin{remark}
-  When $(A, \leq)$ is an MAV-frame, Proposition
-  \ref{prop:day-construction} gives us two pomonoids
+  When $(A, \leq)$ is an MAV-frame, \Cref{prop:day-construction} gives us two pomonoids
   $(\Day{\parr}, \Day{I})$ and $(\Day{\lhd}, \Day{I})$ on
@@
 
-\begin{proposition}\label{prop:lower-set-duoidal}
+\begin{proposition}\label[prop]{prop:lower-set-duoidal}
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ then
@@
 Day-pomonoids from lower sets, but in two different ways, depending on
-how the original pomonoid interacts with $+$. In Proposition
-\ref{prop:closed-monoid-distrib} we handle pomonoids that distribute
-over $+$, and in Propositional \ref{prop:closed-monoid-duoidal} we
+how the original pomonoid interacts with $+$. In \Cref{prop:closed-monoid-distrib} we handle pomonoids that distribute
+over $+$, and in \Cref{prop:closed-monoid-duoidal} we
 handle pomonoids that are entopic under $+$. We need these
@@
 MAV-frames to $+$-closed lower sets. Finally in this section, we show
-that duoidal structure on lower sets from Proposition
-\ref{prop:lower-set-duoidal} is preserved in $+$-closed lower sets.
+that duoidal structure on lower sets from
+\Cref{prop:lower-set-duoidal} is preserved in $+$-closed lower sets.
 
@@
 
-\begin{proposition}\label{prop:closed-eta-preserve-joins}
+\begin{proposition}\label[prop]{prop:closed-eta-preserve-joins}
   $\eta^+(x + y) \subseteq \eta^+(x) \lor \eta^+(y)$.
@@
 \begin{remark}
-  Proposition \ref{prop:closed-eta-preserve-joins} is the reason for
+  \Cref{prop:closed-eta-preserve-joins} is the reason for
   requiring $+$-closure. This property will allow us to prove the
-  crucial embedding property for all formulas in Section
-  \ref{sec:mav-cut-elimination}.
+  crucial embedding property for all formulas in \Cref{sec:mav-cut-elimination}.
 \end{remark}
 
-\begin{proposition}\label{prop:closed-monoid-distrib}
+\begin{proposition}\label[prop]{prop:closed-monoid-distrib}
   For a commutative pomonoid $(\bullet, i)$ on $(A, \leq)$ that
@@
 
-\begin{proposition}\label{prop:closed-monoid-duoidal}
+\begin{proposition}\label[prop]{prop:closed-monoid-duoidal}
   For a pomonoid $(\lhd, j)$ on $(A, \leq)$, if this satisfies
@@
 \begin{remark}
-  Generalising the situation for the unit $j$ in Proposition
-  \ref{prop:closed-monoid-duoidal}, $\eta(x)$ is closed for any $x$
+  Generalising the situation for the unit $j$ in \Cref{prop:closed-monoid-duoidal}, $\eta(x)$ is closed for any $x$
   such that $x + x \leq x$. Note that if $+$ were a join on
@@
   $\bullet$ will distribute over $+$ and so $\ClosedDay{\bullet}$ will
-  be constructed by Proposition \ref{prop:closed-monoid-distrib}; and
+  be constructed by \Cref{prop:closed-monoid-distrib}; and
   a non-symmetric operator like $\lhd$ will be duoidal under $+$ and
-  so $\ClosedDay{\lhd}$ will be constructed by Proposition
-  \ref{prop:closed-monoid-duoidal}.
+  so $\ClosedDay{\lhd}$ will be constructed by \Cref{prop:closed-monoid-duoidal}.
 \end{remark}
@@
   If we have two pomonoids on $(A, \leq)$ that share a unit, then the
-  two constructions of units in Propositions
-  \ref{prop:closed-monoid-distrib} and
-  \ref{prop:closed-monoid-duoidal} will yield the same element of
+  two constructions of units in \Cref{prop:closed-monoid-distrib,prop:closed-monoid-duoidal} will yield the same element of
   $\ClosedLowerSet{A}$.
@@
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
-  $(\bullet, i)$ distributes over $+$ (as in Proposition
-  \ref{prop:closed-monoid-distrib}) and $+$ is duoidal over
-  $(\lhd, j)$ (as in Proposition \ref{prop:closed-monoid-duoidal}),
+  $(\bullet, i)$ distributes over $+$ (as in \Cref{prop:closed-monoid-distrib}) and $+$ is duoidal over
+  $(\lhd, j)$ (as in \Cref{prop:closed-monoid-duoidal}),
   then $(\ClosedDay{\bullet}, \ClosedDay{i})$ is duoidal over
@@
 \begin{proof}
-  The duoidal relationship established in Proposition
-  \ref{prop:lower-set-duoidal} carries over thanks to the properties
+  The duoidal relationship established in \Cref{prop:lower-set-duoidal} carries over thanks to the properties
   of $\alpha$ and $U$. The fact that
@@
 
-\begin{definition}\label{defn:chu}
+\begin{definition}\label[defn]{defn:chu}
   Let $k$ be an element of $A$. $\Chu(A, k)$ is the partial order with
@@
 
-\begin{proposition}\label{prop:chu-meets}
+\begin{proposition}\label[prop]{prop:chu-meets}
   If $A$ has binary joins, then $(\Chu(A, k), \sqsubseteq)$ has
@@
   Since $(\Chu(A, k), \sqsubseteq, \otimes, I, \lnot)$ is a
-  $*$-autonomous partial order, then Proposition \ref{prop:chu-meets}
+  $*$-autonomous partial order, then \Cref{prop:chu-meets}
   also means that $\Chu(A, k)$ has all binary joins, with
@@
 interact well with $k$:
-\begin{proposition}\label{prop:chu-self-dual}
+\begin{proposition}\label[prop]{prop:chu-self-dual}
   Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that
@@
 
-\begin{lemma}\label{lem:duoidal-residual}
+\begin{lemma}\label[lem]{lem:duoidal-residual}
   If $(\bullet, j)$ is duoidal over $(\lhd, j)$ in a partial order
@@
 \begin{remark}
-  Lemma \ref{lem:duoidal-residual} is in some sense the
+  \Cref{lem:duoidal-residual} is in some sense the
   ``intuitionistic'' version of the duoidal relationship for $\parr$
   arising as the dual of that for $\otimes$ in a $*$-autonomous
-  partial order, as we saw in Proposition
-  \ref{prop:mav-algebra-consequences}.
+  partial order, as we saw in \Cref{prop:mav-algebra-consequences}.
 \end{remark}
@@
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
-  $(\lhd, j)$ satisfies the conditions of Proposition
-  \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(\lhd, J)$ are in a
+  $(\lhd, j)$ satisfies the conditions of \Cref{prop:chu-self-dual}, then $(\otimes, I)$ and $(\lhd, J)$ are in a
   duoidal relationship on $\Chu(A, k)$.
@@
   consequence of the duoidal relationship. For the negative half, we
-  use Lemma \ref{lem:duoidal-residual} and the fact that meets are
+  use \Cref{lem:duoidal-residual} and the fact that meets are
   always duoidal.
@@
 
-\begin{theorem}\label{thm:algebra-from-frame}
+\begin{theorem}\label[thm]{thm:algebra-from-frame}
   If $(F, \leq, \parr, \lhd, I, +)$ is an MAV-frame, then
@@
 With this theorem we can define a notion of validity in MAV in terms
-of truth in all MAV-frame generated algebras. By Theorem
-\ref{thm:soundness}, MAV is sound for this notion of validity:
+of truth in all MAV-frame generated algebras. By \Cref{thm:soundness}, MAV is sound for this notion of validity:
 
-\begin{theorem}\label{thm:mavframe-soundness}
+\begin{theorem}\label[thm]{thm:mavframe-soundness}
   MAV is sound for the MAV-frame semantics: if $P \longrightarrow^* I$

### 2024-03-29 doc/sections/mav-syntax.tex
Part of pushing through syntactic stuff

@@
 
-The structures of MAV are formed from positive and negative atoms ($\vPos\va$ and $\vNeg\va$), units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
+The structures of MAV are formed from positive and negative atoms ($\vPos\va$ and $\vNeg\va$) drawn from some set of atomic propositions, units ($\vUnit$), the non-commutative connective \emph{seq} ($\vSeq$), the multiplicative connectives \emph{tensor} and \emph{par} ($\vTens$ and $\vParr$) and additive connectives \emph{with} and \emph{plus} ($\vWith$ and $\vPlus$).
 \begin{displaymath}
@@
 
-Note that, except for \cref{rule:Switch}, the rules come in pairs that are dual, in the sense that if a rule is of the form $P \vInferFrom Q$, then its partner is of the form $\vDual{P} \vInferFrom \vDual{Q}$.
+Note that, except for \cref{rule:Switch}, the rules come in pairs that are dual, in the sense that if a rule is of the form $\vP\vInferFrom\vQ$, then its partner is of the form $\vDual\vP\vInferFrom\vDual\vQ$.
 The \cref{rule:Switch} rule is, up to commutativity, already its own dual.
@@
 
-\begin{definition}
-  \emph{Derivation}, written $\vInferFrom*$ is the reflexive,
-  transitive closure of inference.  \emph{Invertible inference},
-  written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie
-  ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.  \emph{Invertible
-    derivation}, written $\vBiInfer*$, is the symmetric core of
-  derivation, or, alternatively, the reflexive, transitive closure of
-  invertible inference.  \emph{Proofs} are derivations that terminate
-  in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of
-  $\vP$.
+\begin{definition}\label[defn]{defn:derivation}
+  \emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
+\emph{Invertible inference}, written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.
+\emph{Invertible derivation}, written $\vBiInfer*$, is the symmetric core of derivation.
+\emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
 \end{definition}

### 2024-03-29 doc/sections/mav-semantics.tex
Fix definition of NMav

@@
 \begin{theorem}\label[thm]{thm:soundness}
-  The interpretation defined in \Cref{defn:mav-interpretation} is sound: for all formulas $P$, if
-  $P \longrightarrow^* I$, then $I \leq \sem{P}$.
+  The interpretation in \Cref{defn:mav-interpretation} is sound:
+  for all structures $\vP$,
+  if $\vP\vInferFrom*\vUnit$,
+  then $I \leq \sem{\vP}$.
 \end{theorem}
@@
 particular MAV-algebra from the formulas and normal proofs. Since
-normal proofs do not {\it a priori} have all the necessary structure
+normal proofs do not \emph{a priori} have all the necessary structure
 for an MAV-algebra, in the following sections we develop a procedure
@@
   The \emph{normal proof MAV-frame} \NMAV is the partial order arising
-  as the quotient of the preorder formed from the formulas of MAV and
-  $P \leq Q$ if there is a normal derivation $P \longrightarrow^*
-    Q$. Define $P \parr Q = P \vParr Q$, $P \lhd Q = P \vSeq Q$,
-  $P + Q = P \vWith Q$ and $I = \vUnit$. The required (in)equalities
-  follow directly from the definition of $\longrightarrow^*$.
+  as the quotient of the preorder formed from the structures of MAV and
+  $\vP\leq\vQ$ if there is a normal derivation $\vP\vInferFrom*\vQ$,
+  defined as $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$,
+  where $\vSS$ is the set of all MAV structures.
+  The required (in)equalities follow directly from the definition of $\longrightarrow^*$.
 \end{proposition}
@@
 \begin{remark}
-  The construction of the MAV-frame \textsc{CFMav} does not use the
-  $\otimes$ and $\oplus$ structure of MAV directly. We will see in
-  \Cref{sec:mav-cut-elimination} that this structure is
-  recovered by duality from the other connectives by the constructions
-  in the rest of this section.
+  The construction of the MAV-frame \NMAV does not use the
+  $\vTens$ and $\vPlus$ structure of MAV directly.
+  This structure is recovered by duality from the other connectives by the constructions in the rest of this section.
 \end{remark}

### 2024-03-29 doc/sections/mav-semantics.tex
Forgot to push

@@
 
-\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
-
 \begin{definition}\label[defn]{defn:mav-interpretation}
@@
   $V : \mathit{At} \to A$, define the interpretation of MAV Formulas
-  as follows: $\sem{\vUnit} = I$, $\sem{\alpha} = V(\alpha)$,
-  $\sem{\vDual \alpha} = \lnot V(\alpha)$,
+  as follows:
+  $\sem{\vUnit} = I$,
+  $\sem{\va} = V(\va)$,
+  $\sem{\vDual \va} = \lnot V(\va)$,
   $\sem{\vP\vTens\vQ} = \sem{\vP} \otimes \sem{\vQ}$,

### 2024-03-29 doc/sections/introduction.tex
[ tex ] introduction & contribution

@@
 
-Horne~\cite{Horne15:mav} gave a syntactic proof of cut-elimination for MAV.
+\emph{Cut-elimination}, or \emph{admissibility of Cut}, is the fundamental property of Gentzen Sequent Calculi systems, which states that proofs using the Cut rule to introduce ``detours'' can be normalised to ones without.
+Crucial properties such as consistency and decidability follow directly from Cut-elimination.
+The Deep Inference analogue of Cut-elimination is the admissibility of the whole \emph{up} fragment of the calculus, which includes the Deep Inference form of Cut (which we describe in \Cref{sec:mav-syntax} below) as well as duals of most of the other rules of the calculus.
+Admissibility of the up fragment has the same metatheoretic benefits for Deep Inference systems as it does for Sequent Calculus ones.
+
+Guglielmi \cite[\S4.1]{Guglielmi14:di} proves admissibility via the Splitting Theorem, which shows that proofs of conjoined structures can be split into separate subproofs.
+This is proved by a detailed syntactic analysis of proofs.
+Horne~\cite{Horne15:mav} gave a syntactic proof of the admissibility of the up fragment for MAV, that extends Guglielmi's technique with further reasoning about the additives.
+The proof is quite lengthy and involves intrincate syntactic reasoning and the subtle and complex termination measures.
+
 We present an alternative proof of cut-elimination via a semantic model.
-This proof avoids some of the intrincate syntactic reasoning in Horne's proof and is more modular, as shown by the extensions we present in \cref{sec:mav-extensions}.
+This proof avoids some of the in Horne's proof.
+We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction.
 
@@
 Attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
+
+To our knowledge, all prior work on the metatheory of deep inference systems like BV and MAV has been carried out using syntactic techniques such as rewriting with termination measures, and translations into other logics with known cut-elimination properties.
+Our main contribution is the use of semantic techniques to derive the admissibility of identity expansion, cut, and the other \emph{co-} rules of MAV.
+To this end, we develop a number of results on the semantics of BV and MAV:
+\begin{enumerate}
+\item In \Cref{sec:mav-algebras}, we propose MAV-algebras as the algebraic counterpart of MAV.
+In short, an MAV-algebra is a $*$-autonomous partial order with meets, and another partially ordered monoidal structure that is \emph{duoidal} with respect to the $*$-autonomous structure.
+\item Normal proofs (our name for the ``up'' fragment) as we define them in the next section do not {\it a priori} support all the structure of an MAV-algebra, so we define the weaker notion of \emph{MAV-frame} (\Cref{defn:mav-frame}).
+These play the same role as Kripke structures do for modal and substructural logics.
+The first main technical contribution of the paper is in showing that every MAV-frame can be completed to an MAV-algebra.
+\item We then show that MAV-frames are strongly complete (in the terminology of Okada) for MAV by proving that the MAV-frame constructed from normal proofs can be used to deduce that all MAV-provable structures have normal proofs in \Cref{thm:cut-elim}.
+Completeness in the usual sense also follows in \Cref{thm:completeness}.
+\end{enumerate}
+
+We describe the MAV Deep Inference system in \Cref{sec:mav-syntax} and motivate the idea for readers not familiar with such systems.
+We present our proof in the full generality of MAV, but note that essentially the same proof applies to BV as well.
+We discuss further possible extensions in \Cref{sec:future-work}.

### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] introduction & contribution

@@
 \emph{MAV-algebra} will partly be a $*$-autonomous partial order
-(\Cref{defn:star-autonomous}) with meets and joins. The
-additional structure for seq satisfies the
-conditions of a duoidal category \cite{hopf-book} (\Cref{defn:duoidal}). We show that MAV is sound for MAV-algebras in
-\Cref{thm:soundness}.
+(\Cref{defn:star-autonomous}) with meets and joins. The additional
+structure for seq satisfies the conditions of a duoidal category
+\cite[Definition 6.1]{Aguiar_2010} (\Cref{defn:duoidal}). We show that
+MAV is sound for MAV-algebras in \Cref{thm:soundness}.
 
@@
 
-BV and MAV extend linear logic by adding a non-commutative pomonoid structure
-that interacts with the existing pomonoid via a kind of interchange
-law (the \cref{rule:Sequence} rule in the proof system). We follow
-\cite{hopf-book} generalising these to the case of monoids with
-differing units. Their terminology is of a category having duoidal
-structure. We find it useful to describe one pomonoid as being
-\emph{duoidal over} another to emphasise the non-symmetric nature of
-the relationship, and by analogy with one monoid distributing over
-another.
+BV and MAV extend linear logic by adding a non-commutative pomonoid
+structure that interacts with the existing pomonoid via a kind of
+interchange law (the \cref{rule:Sequence} rule in the proof
+system). We follow \cite[Definition 6.1]{Aguiar_2010} generalising
+these to the case of monoids with differing units. Their terminology
+is of a category having duoidal structure. We find it useful to
+describe one pomonoid as being \emph{duoidal over} another to
+emphasise the non-symmetric nature of the relationship, and by analogy
+with one monoid distributing over another.
 
@@
 \subsection{MAV-algebras}
+\label{sec:mav-algebras}
 
@@
     \item $(\otimes, I)$ and $(\parr, I)$ are linearly distributive
-          \cite{cockett}:
+          \cite{Cockett_1999}:
           $x \otimes (y \parr z) \leq (x \otimes y) \parr z$.
@@
 To prove completeness of the normal proofs of MAV, we will construct a
-particular MAV-algebra from the formulas and normal proofs. Since
+particular MAV-algebra from the structures and normal proofs. Since
 normal proofs do not \emph{a priori} have all the necessary structure
@@
 \begin{definition}\label[defn]{defn:mav-frame}
-  An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, I, +)$
-  where $(F, \leq)$ is a partial order, $(F, \leq, \parr, I)$ is a
-  commutative pomonoid, $(F, \leq, \lhd, I)$ is a pomonoid, $+$ is a
+  An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, i, +)$
+  where $(F, \leq)$ is a partial order, $(F, \leq, \parr, i)$ is a
+  commutative pomonoid, $(F, \leq, \lhd, i)$ is a pomonoid, $+$ is a
   binary monotone function on $(F, \leq)$, and these data satisfy the
@@
     \item $(w \lhd x) + (y \lhd z) \leq (w + y) \lhd (x + z)$
-    \item $I + I \leq I$
+    \item $i + i \leq i$
   \end{enumerate}
@@
 \begin{remark}
-  This is the Day monoidal product \cite{day} restricted to the case
-  of partial orders.
+  \Cref{prop:day-construction} is the Day monoidal product on functor
+  categories \cite{Day_1970} restricted to the case of partial orders
+  and lower sets.
 \end{remark}
@@
 
-In the phase semantics, formulas are interpreted as elements that are
+In the phase semantics, structures are interpreted as elements that are
 fixed points of a closure operator defined by a double negation with
@@
   By this proposition, $U \circ \alpha$ is a closure operator on
-  $\LowerSet{A}$ \cite{davey-priestley}, and the closed elements are
+  $\LowerSet{A}$ \cite{Davey_2002}, and the closed elements are
   those of $\ClosedLowerSet{A}$. The next proposition is standard for
@@
   requiring $+$-closure. This property will allow us to prove the
-  crucial embedding property for all formulas in \Cref{sec:mav-cut-elimination}.
+  crucial embedding property for all structures in \Cref{sec:mav-cut-elimination}.
 \end{remark}
@@
 To construct suitable MAV-algebras, we use the partial order version
-of the Chu construction \cite{barr}. The Chu construction builds
-$*$-autonomous categories from symmetric monoidal closed categories
-with pullbacks. In the partial order case, the requirement for
-pullbacks simplifies to binary meets. For this section, we let
+of the Chu construction \cite[Appendix by Po-Hsiang
+Chu]{Barr_1979}. The Chu construction builds $*$-autonomous categories
+from symmetric monoidal closed categories with pullbacks. In the
+partial order case, the requirement for pullbacks simplifies to binary
+meets. For this section, we let
 $(A, \leq, \bullet, i, \rightblackspoon)$ be a partial order with a
@@
 \begin{theorem}\label[thm]{thm:mavframe-soundness}
-  MAV is sound for the MAV-frame semantics: if $P \longrightarrow^* I$
+  MAV is sound for the MAV-frame semantics: if $P \vInferFrom* \vUnit$
   then for all MAV-frames $F$, $\sem{I} \sqsubseteq \sem{P}$ in

### 2024-03-29 doc/sections/mav-cut-elimination.tex
Consistent use of structure

@@
 proof MAV-frame (\Cref{prop:nmav-frame}), where elements
-are positive/negative pairs of $+$-closed lower sets of formulas. We
+are positive/negative pairs of $+$-closed lower sets of structures. We
 define the valuation of atoms as
 $V(\va) = \ChuEmbed(\ClosedLowerEmbed(\vDual\va))$. By
-\Cref{thm:soundness}, we have an interpretation of MAV formulas
+\Cref{thm:soundness}, we have an interpretation of MAV structures
 $\sem{\vP}$ such that if $\vP\vInferFrom*\vUnit$, then

### 2024-03-29 doc/sections/mav-mechanisation.tex
Consistent use of structure

@@
 executable. For example, we can normalise the one step SMAV proof
-(using \cref{rule:Axiom}) of $\vP \vParr \vDual{\vP}$ where
+using \cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
 $\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a FIXME

### 2024-03-29 doc/sections/mav-syntax.tex
Adjust positive and negative atoms to match use in semantics
Add index and restructure inference rule table
Consistent use of structure

@@
   \begin{array}{
-      l@{\;=\;}l @{\hspace{1cm}}
-      l@{\;=\;}l @{\hspace{1cm}}
-      l@{\;=\;}l @{\hspace{1cm}}
-      l@{\;=\;}l}
-    \vDual{\vPos\va}     & \vNeg\va
-                         &
-    \vDual{\vUnit}       & \vUnit
-                         &
-    \vDual{\vP\vTens\vQ} & \vDual\vP \vParr \vDual\vQ
-                         &
-    \vDual{\vP\vParr\vQ} & \vDual\vP \vTens \vDual\vQ
+      lcl @{\hspace{1cm}}
+      lcl @{\hspace{1cm}}
+      lcl @{\hspace{1cm}}
+      lcl}
+    \multicolumn{3}{l}{}
+    % \vDual{\vPos\va}
+    %  & =
+    %  & \vNeg\va
+     & \vDual{\vUnit}
+     & =
+     & \vUnit
+     & \vDual{\vP\vTens\vQ}
+     & =
+     & \vDual\vP \vParr \vDual\vQ
+     & \vDual{\vP\vParr\vQ}
+     & \vDual\vP \vTens \vDual\vQ
     \\
-    \vDual{\vNeg\va}     & \vPos\va
-                         &
-    \vDual{\vP\vSeq \vQ} & \vDual\vP \vSeq  \vDual\vQ
-                         &
-    \vDual{\vP\vWith\vQ} & \vDual\vP \vPlus \vDual\vQ
-                         &
-    \vDual{\vP\vPlus\vQ} & \vDual\vP \vWith \vDual\vQ
+    \vDual{\vNeg\va}
+     & =
+     & \vPos\va
+     & \vDual{\vP\vSeq \vQ}
+     & =
+     & \vDual\vP \vSeq  \vDual\vQ
+     & \vDual{\vP\vWith\vQ}
+     & =
+     & \vDual\vP \vPlus \vDual\vQ
+     & \vDual{\vP\vPlus\vQ}
+     & \vDual\vP \vWith \vDual\vQ
   \end{array}
@@
     \\
-    \vUnit
-     & \vInferFrom
-     & \vP\vTens\vDual\vP
-     & \RuleLabel{Cut}
-    \\
     (\vP\vTens\vQ)\vParr\vR
@@
     \\
+    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
+     & \vInferFrom
+     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
+     & \RuleLabel{Sequence}
+    \\
+    \vP\vPlus\vQ
+     & \vInferFrom
+     & \vP
+     & \RuleLabel{Left}
+    \\
+    \vP\vPlus\vQ
+     & \vInferFrom
+     & \vQ
+     & \RuleLabel{Right}
+    \\
+    (\vP\vWith\vQ)\vParr\vR
+     & \vInferFrom
+     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
+     & \RuleLabel{External}
+    \\
+    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
+     & \vInferFrom
+     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
+     & \RuleLabel{Medial}
+    \\
+     &
+     &
+     &
+    \\
+    \vUnit
+     & \vInferFrom
+     & \vP\vTens\vDual\vP
+     & \RuleLabel{Cut}
+    \\
     \vUnit
@@
      & \RuleLabel{CoTidy}
-    \\
-    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
-     & \vInferFrom
-     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
-     & \RuleLabel{Sequence}
     \\
@@
     \\
-    \vP\vPlus\vQ
-     & \vInferFrom
-     & \vP
-     & \RuleLabel{Left}
-    \\
     \vP
@@
      & \RuleLabel{CoLeft}
-    \\
-    \vP\vPlus\vQ
-     & \vInferFrom
-     & \vQ
-     & \RuleLabel{Right}
     \\
@@
     \\
-    (\vP\vWith\vQ)\vParr\vR
-     & \vInferFrom
-     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
-     & \RuleLabel{External}
-    \\
     (\vP \vTens \vR) \vPlus (\vQ \vTens \vR)
@@
     \\
-    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
-     & \vInferFrom
-     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
-     & \RuleLabel{Medial}
-    \\
     (\vP \vPlus \vR) \vSeq (\vQ \vPlus \vS)
@@
      & \RuleLabel{CoMedial}
+    \\
+     &
+     &
+     &
     \\
@@
 \end{displaymath}
-(If $\vP\vInferFrom\vQ$, we say that $\vP$ can be inferred from $\vQ$, \ie the arrow points from conclusion to premise.)
+If $\vP\vInferFrom\vQ$, we say that $\vP$ can be inferred from $\vQ$, \ie the arrow points from conclusion to premise.
 
-Note that, except for \cref{rule:Switch}, the rules come in pairs that are dual, in the sense that if a rule is of the form $\vP\vInferFrom\vQ$, then its partner is of the form $\vDual\vP\vInferFrom\vDual\vQ$.
-The \cref{rule:Switch} rule is, up to commutativity, already its own dual.
-The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new formulas going left-to-right.
+The inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vP\vInferFrom\vDual\vQ$.
+The exception is \cref{rule:Switch}, which is self-dual, up to commutativity.
+The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new structures going left-to-right.
 Normal proofs, which we define below, avoid these \emph{synthetic} rules.
@@
   The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
+  Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Axiom} and \cref{rule:Cut} are $\iD$ and $\iU$, respectively.
 \end{remark}
@@
 \end{definition}
-Normal derivations avoid the use of rules that introduce new formulas into proofs, and so can be termed \emph{analytic} in contrast to the need for the synthetic rules to synthesise new formulas.
+Normal derivations avoid the use of rules that introduce new structures into proofs, and so can be termed \emph{analytic} in contrast to the need for the synthetic rules to synthesise new structures.
 
-Our main result, Theorem \ref{thm:cut-elim}, is that every formula that is provable in full MAV also has a normal proof.
+Our main result, \Cref{thm:cut-elim}, is that every structure that is provable in full MAV also has a normal proof.
 Therefore, the system with only analytic rules is complete for MAV provability.

### 2024-03-29 doc/sections/mav-cut-elimination.tex
[ tex ] describe concurrent Kleene algebras and some small fixes

@@
 
-Let $\Chu(\ClosedLowerSet{\NMAV}, \ClosedDay{I})$ be the MAV-algebra
+Let $\Chu(\ClosedLowerSet{\NMAV}, \ClosedDay{\vUnit})$ be the MAV-algebra
 constructed (\Cref{thm:algebra-from-frame}) from the normal
@@
 \begin{proposition}\label[prop]{prop:embedding-sem}
-  $\sem{\vP} \sqsubseteq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$
+  For all structures $\vP$, $\sem{\vP} \sqsubseteq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$.
 \end{proposition}
@@
 \begin{proof}
-  By \Cref{defn:chu}, this statement is two inclusions
+  By \Cref{defn:chu}, this statement comprises two inclusions
   between pairs of $+$-closed lower sets:

### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] describe concurrent Kleene algebras and some small fixes

--- 2024-03-29 doc/sections/mav-semantics.tex
@@
   MAV-frames have a intuitive reading as CCS-like process algebras
-  (see Milner \cite{milner89} for an introduction to CCS). If we
+  (see Milner \cite{Milner89:CC} for an introduction to CCS). If we
   assume the existence of a collection of ``action'' elements
   $a \in F$ and their duals $\overline{a} \in F$, satisfying
-  $a \parr \overline{a} \leq I$, then we can read the constructs of an
+  $a \parr \overline{a} \leq i$, then we can read the constructs of an
   MAV-frame as parallel composition, sequential composition, and
@@
   process algebra.
+\end{remark}
+
+\begin{remark}
+  MAV-frames (and MAV-algebras) are also very similar to the
+  definition of a \emph{Concurrent Kleene Algebra} (CKA) due to Hoare,
+  M{\"o}ller, Struth and Wehrman \cite[Definition
+  4.1]{HoareMSW09}. One difference is that we do not assume that $+$
+  is a join, nor do we assume the existence of infinitary
+  joins. Consequently, we have no analogue of the Kleene Star. Another
+  difference is that the duoidal relationship is reversed in
+  MAV-frames, indicating that MAV-frames capture evolution of
+  processes while MAV-algebras and CKA capture properties of
+  processes.
 \end{remark}
@@
 \begin{remark}
-  The construction of the MAV-frame \NMAV does not use the
-  $\vTens$ and $\vPlus$ structure of MAV directly.
-  This structure is recovered by duality from the other connectives by the constructions in the rest of this section.
+  The construction of the MAV-frame \NMAV does not use the $\vTens$
+  and $\vPlus$ structure of MAV directly.  This structure is recovered
+  by duality from the other connectives by the constructions in the
+  rest of this section. This corresponds to the fact that the
+  \textsc{Co-X} rules in MAV that we wish to show admissible are the
+  ones that mention the $\otimes$ and $\oplus$ connectives, with the
+  exception of \cref{rule:Switch}, which has a special role to play in
+  \Cref{prop:embedding-sem} in mediating interaction.
 \end{remark}
@@
 We construct MAV-algebras from MAV-frames in a three step process. In
-\Cref{sec:lower-sets}, we use lower sets and the Day
-construction to add meets, joins and residuals for pomonoids to a
-partial order. This construction creates joins freely, so we restrict
-to $+$-closed lower sets in \Cref{sec:closed-lower-sets} to
-turn the $+$ operation in MAV-frames into joins. Restricting to
-$+$-closed lower sets separates the Day construction of pomonoids into
-two separate cases, depending on how the original pomonoid interacts
-with $+$. Finally, we create the $*$-autonomous structure using the
-Chu construction in \Cref{sec:chu}. The necessary duoidal
-structure is maintained through each construction.
+\Cref{sec:lower-sets}, we use lower sets and the Day construction to
+add meets, joins and residuals for pomonoids to a partial order. This
+construction creates joins freely, so we restrict to $+$-closed lower
+sets (\ie, order ideals, but not necessarily over a
+$\lor$-semilattice) in \Cref{sec:closed-lower-sets} to turn the $+$
+operation in MAV-frames into joins. Restricting to $+$-closed lower
+sets separates the Day construction of pomonoids into two separate
+cases, depending on how the original pomonoid interacts with
+$+$. Finally, we create the $*$-autonomous structure using the Chu
+construction in \Cref{sec:chu}. The necessary duoidal structure is
+maintained through each construction.
 
@@
 
-In the phase semantics, structures are interpreted as elements that are
+In the Phase Semantics, structures are interpreted as elements that are
 fixed points of a closure operator defined by a double negation with
@@
 
-\subsection{Construction of MAV-algebras}
+\subsection{Construction of MAV-algebras from MAV-frames}
 
@@
 \begin{theorem}\label[thm]{thm:algebra-from-frame}
-  If $(F, \leq, \parr, \lhd, I, +)$ is an MAV-frame, then
-  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{I}), \sqsubseteq)$ has the structure of an
-  MAV-algebra.
+  If $(F, \leq, \parr, \lhd, i, +)$ is an MAV-frame, then
+  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{i}), \sqsubseteq)$ has the
+  structure of an MAV-algebra.
 \end{theorem}
@@
 With this theorem we can define a notion of validity in MAV in terms
-of truth in all MAV-frame generated algebras. By \Cref{thm:soundness}, MAV is sound for this notion of validity:
+of truth in all MAV-frame generated algebras. By \Cref{thm:soundness},
+MAV is sound for this notion of validity:
 
@@
   MAV is sound for the MAV-frame semantics: if $P \vInferFrom* \vUnit$
-  then for all MAV-frames $F$, $\sem{I} \sqsubseteq \sem{P}$ in
-  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{I}), \sqsubseteq)$.
+  then for all MAV-frames $F$, $I \sqsubseteq \sem{P}$ in
+  $(\Chu(\ClosedLowerSet{F}, \ClosedDay{i}), \sqsubseteq)$.
 \end{theorem}

### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] title, grant ack, and small fixes

@@
 
+\begin{remark}
+  More generally, if $P \vInferFrom* Q$ in MAV, then
+  $\sem{Q} \leq \sem{P}$ in an MAV-algebra. Note that the ordering is
+  reversed! It will be reversed again in the definition of MAV-frame.
+\end{remark}
+
 \subsection{MAV-frames}
@@
 over $+$, and in \Cref{prop:closed-monoid-duoidal} we
-handle pomonoids that are entopic under $+$. We need these
+handle pomonoids that are duoidal under $+$. We need these
 constructions to lift the $\parr$ and $\lhd$ pomonoids from

### 2024-03-29 doc/sections/introduction.tex
[ tex ] Conclusions and Future Work, and some small fixes

@@
 The completeness of this model directly yields the existence of a cut-free proof for every proof constructible in the MALL sequent calculus.
-The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and by Frumin~\cite{Frumin22:psc} for bunched implications.
+The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and by Frumin~\cite{Frumin22:psc} for Bunched Implications.
 

### 2024-03-29 doc/sections/mav-extensions.tex
[ tex ] title, grant ack, and small fixes
[ tex ] Conclusions and Future Work, and some small fixes

--- 2024-03-22 doc/sections/mav-extensions.tex
@@
-\section{Extensions}\label{sec:mav-extensions}
+\section{Conclusions and Future Work}\label{sec:future-work}
 
-\subsection{Additive Units}
+We have presented semantic proof of generalised Cut elimination for
+the Multiplicative-Additive System Virtual (MAV), reducing Horne's
+approximately 41 page proof to 7 and also providing an Agda
+mechanisation. Our proof technique also restricts easily to BV (we
+simply skip the use of $+$-closed lower sets and use lower sets
+directly instead). We believe that adding additive units ($\top$ and
+$0$ in Girard's notation) will be straightforward.
 
-\subsection{Multiplicative-Additive Linear Logic}
+This work opens up several paths for future work. The theory developed
+here for lifting Day pomonoids to $+$-closed lower sets should also
+enable alternative Cut-elimination proofs for other substructural
+logics, such as MALL and Bunched Implications (Okada's technique has
+already been applied here by Frumin \cite{Frumin22:psc}). We find the
+technique of using $+$-closed lower sets rather than more opaque
+closure operators more revealing in how the
 
-\subsection{Display Calculus}
+We also plan to investigate extensions of MAV with exponentials, as in
+the System NEL \cite{GuglielmiS11}, and Kleene Star operators which
+can be seen as the exponential for the $\vSeq$ connective. Adding a
+Kleene Star would tighten the connection with Concurrent Kleene
+Algebras we highlighted in \Cref{remark:cka}. More generally, fixpoint
+operators following Baelde \cite{Baelde12} and De, Jafarrahmani and
+Saurin \cite{De22:psc}. The latters' use of Okada's technique is not
+compatible with Agda's logic because it relies on impredicativity to
+construct fixpoints with the double negation closure. We believe that
+our more direct predicative technique will be able to use Agda's
+inductive and coinductive types.
 
-Cut-elimination for a Display calculus?
+We also plan to extend our semantics of BV and MAV to a categorical
+semantics that considers equalities between proofs as well as
+provability. Such a semantics ought to be useful for treating MAV as a
+session-types style language, as considered by Ciobanu and Horne
+\cite{Ciobanu_2016}. The necessary analogue of MAV-algebras has
+already been investigated by Blute, Panangaden and Slavnov
+\cite{Blute_2010} as BV-categories, which are Aguiar and Mahajan's
+2-monoidal, or duoidal, categories \cite{Aguiar_2010} extended with
+duality. The key task will be to categorify the constructions in this
+paper to show how the categorical analogue of MAV-frames induces
+MAV-categories.

### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] Conclusions and Future Work, and some small fixes

@@
 
-\begin{remark}
+\begin{remark}\label[remark]{remark:cka}
   MAV-frames (and MAV-algebras) are also very similar to the
@@
   M{\"o}ller, Struth and Wehrman \cite[Definition
-  4.1]{HoareMSW09}. One difference is that we do not assume that $+$
+  4.1]{Hoare_2011}. One difference is that we do not assume that $+$
   is a join, nor do we assume the existence of infinitary
@@
   The \emph{normal proof MAV-frame} \NMAV is the partial order arising
-  as the quotient of the preorder formed from the structures of MAV and
-  $\vP\leq\vQ$ if there is a normal derivation $\vP\vInferFrom*\vQ$,
-  defined as $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$,
-  where $\vSS$ is the set of all MAV structures.
-  The required (in)equalities follow directly from the definition of $\longrightarrow^*$.
+  as the quotient of the preorder formed from the structures of MAV
+  and $\vP\leq\vQ$ if there is a normal derivation
+  $\vP\vInferFrom*\vQ$, defined as
+  $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$, where $\vSS$
+  is the set of all MAV structures.  The required (in)equalities
+  follow directly from the definition of $\vInferFrom*$ for normal
+  proofs.
 \end{proposition}

### 2024-03-29 doc/sections/introduction.tex
[ tex ] Make a submittable version

@@
 
-We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
+We present an algebraic semantics and semantic proof of generalised cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
       BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.

### 2024-03-29 doc/sections/mav-mechanisation.tex
[ tex ] Make a submittable version

@@
 The formalisation uses setoids to represent sets, reusing definitions
-from the Agda Standard Library \cite{AgdaStdlib20}. Each of the
-definitions and propositions above links to the corresponding part of
-the development.
+from the Agda Standard Library \cite{AgdaStdlib20}.
+% Each of the
+% definitions and propositions above links to the corresponding part of
+% the development.
+
+We did not attempt to formalise the syntactic proof of generalised
+cut-elimination directly. We suspect that this would likely be
+extremely involved due to the widespread and implicit use of syntactic
+equalties when manipulating formulas, as well as the construction of
+the relevant termination measures. The semantic constructions are
+relatively straightforward to formalise in Agda.
 
@@
 formalising the development in a proof assistant like Agda is that the
-proof normalisation process (\Cref{thm:cut-elim}) is
-executable. For example, we can normalise the one step SMAV proof
-using \cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
-$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a FIXME
-step MAV proof, given in the Appendix.
+proof normalisation process (\Cref{thm:cut-elim}) is executable. For
+example, we can normalise the one step SMAV proof using
+\cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
+$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38
+step (of which 9 are $\vInferFrom$ steps) MAV proof, presented online
+here:
+\begin{center}
+  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html#908}
+\end{center}
 
-\bob{Wen: do you want to write something about the formalisation of
-  the congruence rules in the proof system?}
+% \bob{Wen: do you want to write something about the formalisation of
+%   the congruence rules in the proof system?}

### 2024-03-29 doc/sections/mav-syntax.tex
[ tex ] Make a submittable version

@@
 \end{displaymath}
-Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective seq.
+Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective $\vSeq$.
 \begin{displaymath}
@@
     & \vDual{\vP\vParr\vQ}
+      & =
      & \vDual\vP \vTens \vDual\vQ
@@
     & \vDual{\vP\vPlus\vQ}
+      & =
      & \vDual\vP \vWith \vDual\vQ
@@
 \end{displaymath}
-Structures are considered equivalent modulo the decidable equality $\vEquiv$, which is the smallest congruence defined by the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a monoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative monoids.
+Structures are considered equivalent modulo the equality $\vEquiv$, which is the smallest congruence defined by the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a monoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative monoids.
 \begin{displaymath}

### 2024-03-29 doc/sections/mav-mechanisation.tex
[ tex ] terminology

@@
 proof normalisation process (\Cref{thm:cut-elim}) is executable. For
-example, we can normalise the one step SMAV proof using
+example, we can normalise the one step MAV proof using
 \cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
 $\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38
-step (of which 9 are $\vInferFrom$ steps) MAV proof, presented online
-here:
+step (of which 9 are $\vInferFrom$ steps) normal proof, presented
+online in Agda notation here:
 \begin{center}

### 2024-04-01 doc/sections/mav-mechanisation.tex
Use interact/co-interact

@@
 example, we can normalise the one step MAV proof using
-\cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
+\cref{rule:Interact} of $\vP \vParr \vDual{\vP}$ where
 $\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38

### 2024-04-01 doc/sections/mav-syntax.tex
Use interact/co-interact

@@
 \end{center}
-Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see.
+Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see. In BV, the axiom and cut rules are called \emph{interaction} and \emph{co-interaction}.
 
@@
      & \vUnit
-     & \makebox[\vInferFromDefnWidthOfLBL][l]{$\RuleLabel{Axiom}$}
+     & \makebox[\vInferFromDefnWidthOfLBL][l]{$\RuleLabel{Interact}$}
     \\
@@
      & \vP\vTens\vDual\vP
-     & \RuleLabel{Cut}
+     & \RuleLabel{CoInteract}
     \\
@@
 The exception is \cref{rule:Switch}, which is self-dual, up to commutativity.
-The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new structures going left-to-right.
+The \cref{rule:CoInteract}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new structures going left-to-right.
 Normal proofs, which we define below, avoid these \emph{synthetic} rules.
@@
   The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
-  Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Axiom} and \cref{rule:Cut} are $\iD$ and $\iU$, respectively.
+  Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Interact} and \cref{rule:CoInteract} are $\iD$ and $\iU$, respectively.
 \end{remark}
@@
 \begin{definition}\label{defn:normal}
-  A derivation is \emph{normal} when it does not use \cref{rule:Cut} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Axiom} are restricted to \cref{rule:AtomAxiom}, as defined by the following axiom:
+  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
   \begin{displaymath}
@@
        & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
-       & \RuleLabel{AtomAxiom}
+       & \RuleLabel{AtomInteract}
     \end{array}

### 2024-04-01 doc/sections/mav-syntax.tex
Fix relation to BV

@@
 \end{center}
-Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see. In BV, the axiom and cut rules are called \emph{interaction} and \emph{co-interaction}.
+Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see.
+In BV, to acknowledge this symmetry and the connection with CSS, the axiom and cut rules are referred to as \emph{interaction} and \emph{co-interaction}.
 
@@
   Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Interact} and \cref{rule:CoInteract} are $\iD$ and $\iU$, respectively.
+The exception are self-dual rules, which are named with a single letter.
+For instance, \cref{rule:Switch} is usually named $\sw$.
 \end{remark}

### 2024-04-01 doc/sections/mav-syntax.tex
Prioritize seq in definitions

@@
 \begin{definition}\label{defn:normal}
-  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
+  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} nor any of the other (\RuleName{CoX}) rules, and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
   \begin{displaymath}

### 2024-04-01 doc/sections/mav-mechanisation.tex
Minor fixes

@@
 extremely involved due to the widespread and implicit use of syntactic
-equalties when manipulating formulas, as well as the construction of
+equalities when manipulating structures, as well as the construction of
 the relevant termination measures. The semantic constructions are

### 2024-04-04 doc/sections/mav-mechanisation.tex
Fixes & add table

@@
 The formalisation uses setoids to represent sets, reusing definitions
-from the Agda Standard Library \cite{AgdaStdlib20}.
-% Each of the
-% definitions and propositions above links to the corresponding part of
-% the development.
+from the Agda Standard Library~\cite{AgdaStdlib20}.
 
@@
 \begin{center}
-  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html#908}
+  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html}
 \end{center}

### 2024-04-04 doc/sections/mav-semantics.tex
Fixes & add table

@@
 
-\subsection{Pomonoidal, $*$-autonomous, and Duoidal Structure on Partial Orders}
+\subsection{Pomonoidal, $*$-autonomous, and Duoidal Structure on Partial Orders}\label{sec:mav-semantics-preliminaries}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label[lem]{lem:dual-ok}
   For all $\vP$, $\sem{\vDual{\vP}} = \lnot \sem{\vP}$.
@@
 \subsection{MAV-frames}
+\label{sec:mav-frames}
 
@@
 
-\begin{definition}
+\begin{definition}\label[defn]{defn:lower-set}
   Given a partial order $(A, \leq)$, the set of lower sets
@@
 
-\begin{proposition}
+\begin{proposition}\label[defn]{defn:lower-set-embed-monotone}
   For any $(A, \leq)$, the function $\eta$ is monotone, and
@@
   intersection and union respectively.
-  %
   % \bob{and $\eta$ preserves any meets that exist}
@@
 
-\begin{definition}
+\begin{definition}\label[defn]{defn:closed-lower-set}
   A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if $x \in F$
@@
 
-\begin{proposition}
+\begin{proposition}\label[prop]{prop:chu-monoid-duoidal}
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
@@
 
-\subsection{Construction of MAV-algebras from MAV-frames}
+\subsubsection{Construction of MAV-algebras from MAV-frames}
+\label{sec:algebra-from-frame}
 

### 2024-04-04 doc/sections/mav-syntax.tex
Minor fixes
Fixes & add table

--- 2024-04-01 doc/sections/mav-syntax.tex
@@
 
+\emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
+\emph{Invertible derivation}, written $\vInferFromTo*$, is the symmetric core of derivation, \ie $\vP\vInferFromTo*\vQ=\vP\vInferFrom*\vQ\cap\vQ\vInferFrom*\vP$.
+\emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
+
 The inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vP\vInferFrom\vDual\vQ$.
@@
 Normal proofs, which we define below, avoid these \emph{synthetic} rules.
-
-\begin{definition}\label[defn]{defn:derivation}
-  \emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
-\emph{Invertible inference}, written $\vBiInfer$, is the symmetric core of $\vInferFrom$, \ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$.
-\emph{Invertible derivation}, written $\vBiInfer*$, is the symmetric core of derivation.
-\emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
-\end{definition}
 
@@
   Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Interact} and \cref{rule:CoInteract} are $\iD$ and $\iU$, respectively.
-The exception are self-dual rules, which are named with a single letter.
-For instance, \cref{rule:Switch} is usually named $\sw$.
+The exception are self-dual rules, which are named with a single letter, \eg \cref{rule:Switch} is usually named $\sw$.
 \end{remark}
 
-\begin{definition}\label{defn:normal}
-  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
+\begin{definition}\label[defn]{defn:normal}
+  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} nor any of the other (\RuleName{CoX}) rules, and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
   \begin{displaymath}

### 2024-04-04 doc/sections/mav-mechanisation.tex
Changes to mav-mechanisation

@@
 \label{sec:mechanisation}
-
-We developed the proof in the previous two sections in the Agda proof
-assistant \cite{Agda264}. The source code for this development is
-available at this URL:
+We formalised the proofs in the paper in Agda~\cite{Agda264}.
+The source code is available at the following URL:
 \begin{center}
@@
 \end{center}
+The formalisation uses setoids to represent sets, and reuses definitions from the Agda Standard Library~\cite{AgdaStdlib20} where appropriate.
 
-The formalisation uses setoids to represent sets, reusing definitions
-from the Agda Standard Library~\cite{AgdaStdlib20}.
+We did not attempt to formalise the syntactic proof of generalised cut-elimination directly.
+We suspect that this would likely be quite involved, due to the widespread and implicit use of syntactic equalities when manipulating structures, as well as the construction of the relevant termination measures.
+The semantic constructions are relatively straightforward to formalise in Agda.
 
-We did not attempt to formalise the syntactic proof of generalised
-cut-elimination directly. We suspect that this would likely be
-extremely involved due to the widespread and implicit use of syntactic
-equalities when manipulating structures, as well as the construction of
-the relevant termination measures. The semantic constructions are
-relatively straightforward to formalise in Agda.
-
-As well as giving confidence in our results, a key benefit of
-formalising the development in a proof assistant like Agda is that the
-proof normalisation process (\Cref{thm:cut-elim}) is executable. For
-example, we can normalise the one step MAV proof using
-\cref{rule:Interact} of $\vP \vParr \vDual{\vP}$ where
-$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38
-step (of which 9 are $\vInferFrom$ steps) normal proof, presented
-online in Agda notation here:
+In addition to increasing the confidence in our results, a key benefit of the formalised proof in a proof assistant such as Agda is that the proof normalisation procedure defined by \Cref{thm:cut-elim} is executable.
+As an example, we have normalised the one-step proof below:
+\begin{displaymath}
+  ((\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit))
+  \vParr
+  ((\vUnit \vWith \vUnit) \vSeq (\vUnit \vPlus \vUnit))
+  \xlongrightarrow{\cref{rule:Interact}}
+  \vUnit
+\end{displaymath}
+The proof normalises to a 38-step normal proof, of which 9 are inference steps, and the remainder are (sometimes spurious) equalities.
+The example can be found at the following URL:
 \begin{center}
-  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html}
+  \url{\AgdaBaseUrl/MAV.Example.html}
 \end{center}
-
-% \bob{Wen: do you want to write something about the formalisation of
-%   the congruence rules in the proof system?}

### 2024-04-04 doc/sections/introduction.tex
[ tex ] edit introduction and add some extra commentary

@@
       BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
-}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
-The proof is constructive and mechanised in Agda~\cite{Agda264}.
+}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}. The proof technique also extends to the additive units.
+Our proofs are constructive and mechanised in Agda~\cite{Agda264}.
 
 MAV and BV are \emph{deep inference} systems.
-Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to classical linear logic~\cite[CLL]{Girard87:ll}.
-The problem with such a relation is that, while the multiplicative connectives of linear logic capture parallel composition, no connective of linear logic captures \emph{sequential composition}.
-Eventually, Guglielmi's attempts yielded BV, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
-Such a connective was already present in another extension of linear logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of linear logic~\cite[\C8]{GirardTL89:proofs}.
+Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to Classical Linear Logic~\cite[CLL]{Girard87:ll}.
+The problem with such a relation is that, while the multiplicative connectives of Linear Logic capture parallel composition, no connective of Linear Logic captures \emph{sequential composition}.
+Eventually, Guglielmi's attempts yielded BV, which extends Multiplicative Linear Logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
+Such a connective was already present in another extension of Linear Logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
 Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
@@
 
-\emph{Cut-elimination}, or \emph{admissibility of Cut}, is the fundamental property of Gentzen Sequent Calculi systems, which states that proofs using the Cut rule to introduce ``detours'' can be normalised to ones without.
-Crucial properties such as consistency and decidability follow directly from Cut-elimination.
+\emph{Cut Elimination}, or \emph{admissibility of Cut}, is the fundamental property of Gentzen Sequent Calculi systems, which states that proofs using the Cut rule to introduce ``detours'' can be normalised to ones without.
+Crucial properties such as consistency and decidability follow from Cut-elimination.
 The Deep Inference analogue of Cut-elimination is the admissibility of the whole \emph{up} fragment of the calculus, which includes the Deep Inference form of Cut (which we describe in \Cref{sec:mav-syntax} below) as well as duals of most of the other rules of the calculus.
@@
 We present an alternative proof of cut-elimination via a semantic model.
-This proof avoids some of the in Horne's proof.
+This proof avoids some of the intrincacy of Horne's proof.
 We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction.
+We demonsrate this by scaling down to plain BV and up to MAV with additive units.
 
-The technique of cut-elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the phase space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
+The technique of demonstrating Cut Elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the phase space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
 The completeness of this model directly yields the existence of a cut-free proof for every proof constructible in the MALL sequent calculus.
@@
 The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
-The phase space model derives duals by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
-Attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
+The phase space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
+Attempts to extend the model with the non-commutative connective result in two distinct dual non-comutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
 
-To our knowledge, all prior work on the metatheory of deep inference systems like BV and MAV has been carried out using syntactic techniques such as rewriting with termination measures, and translations into other logics with known cut-elimination properties.
+To our knowledge, all prior work on the metatheory of Deep Inference systems like BV and MAV has been carried out using syntactic techniques such as rewriting with termination measures, or translations into other logics with known Cut-Elimination properties.
 Our main contribution is the use of semantic techniques to derive the admissibility of identity expansion, cut, and the other \emph{co-} rules of MAV.
@@
 We describe the MAV Deep Inference system in \Cref{sec:mav-syntax} and motivate the idea for readers not familiar with such systems.
-We present our proof in the full generality of MAV, but note that essentially the same proof applies to BV as well.
-We discuss further possible extensions in \Cref{sec:future-work}.
+
+All of our proofs have been mechanised and checked in the Agda proof assistant \cite{Agda264}.
+We briefly discuss the mechanisation in \Cref{sec:mechanisation} and provide a hyperlinked guide to the proof relating it to our mathematical development in \Cref{sec:table-of-statments}.
+Aside from the benefits of checking the proof, the Agda proof is executable and yields a program for actually normalising proofs.
+
+We present our proof in the full generality of MAV, but note that essentially the same proof applies to the subsystem BV as well.
+We have also extended the proof technique to include the additive units, and to BV with exponentials (System NEL, analysed by Guglielmi and Stra{\ss}burger \cite{Burger_2011,GuglielmiS11}) We discuss further extensions in \Cref{sec:future-work}.

### 2024-04-04 doc/sections/introduction.tex
[ tex ] Organise the introduction, and say what a structure is

@@
 
-MAV and BV are \emph{deep inference} systems.
+\subsection{BV, MAV, and Deep Inference}
+
+MAV and BV are \emph{Deep Inference} systems.
 Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to Classical Linear Logic~\cite[CLL]{Girard87:ll}.
@@
 
+\subsection{Contribution and Content of this Paper}
+
 To our knowledge, all prior work on the metatheory of Deep Inference systems like BV and MAV has been carried out using syntactic techniques such as rewriting with termination measures, or translations into other logics with known Cut-Elimination properties.
+
 Our main contribution is the use of semantic techniques to derive the admissibility of identity expansion, cut, and the other \emph{co-} rules of MAV.
-To this end, we develop a number of results on the semantics of BV and MAV:
+To this end, we have developed a number of results on the semantics of BV and MAV:
 \begin{enumerate}
@@
 
+As far as we are aware, the semantics of BV and its extensions have not been considered before in the literature.
+The crucial part of the proof is that the standard Chu construction extends to the self-dual non-commutative connective of BV and MAV (\Cref{prop:chu-self-dual} and \Cref{prop:chu-monoid-duoidal}).
+Our development of the semantics of MAV and BV also opens the possibility of using these logics as sound and complete for reasoning about the MAV-frame structures we define.
+
 All of our proofs have been mechanised and checked in the Agda proof assistant \cite{Agda264}.

### 2024-04-04 doc/sections/mav-syntax.tex
[ tex ] Organise the introduction, and say what a structure is

@@
 \section{The system MAV}\label{sec:mav-syntax}
+
+In Deep Inference terminology, proofs operate on \emph{structures}, which simultaneously play the role of formulas and sequents in traditional Sequent Calculus systems.
+There are a number of different notations in the literature for the structures of BV and related systems.
+For familiarity's sake, we opt for a notation similar to normal Linear Logic, albeit extended with the self-dual non-commutative connective $\vSeq$.
 

### 2024-04-04 doc/sections/mav-mechanisation.tex
[ tex ] link to the appendix from mechanisation section

@@
 The formalisation uses setoids to represent sets, and reuses definitions from the Agda Standard Library~\cite{AgdaStdlib20} where appropriate.
+We have provided a guide to the mechanisation relating it to the Definitions, Propositions, and Theorems in the previous sections in \Cref{sec:table-of-statments}.
 
-We did not attempt to formalise the syntactic proof of generalised cut-elimination directly.
+We did not attempt to formalise Horne's syntactic proof of generalised cut-elimination directly.
 We suspect that this would likely be quite involved, due to the widespread and implicit use of syntactic equalities when manipulating structures, as well as the construction of the relevant termination measures.

### 2024-04-04 doc/sections/mav-extensions.tex
[ tex ] more future work
Mid-sentence  commit

@@
-\section{Conclusions and Future Work}\label{sec:future-work}
+\section{Extensions and Future Work}\label{sec:future-work}
+We have presented a semantic proof of generalised Cut elimination for the Multiplicative-Additive System Virtual (MAV), which reduces Horne's approximately 41 page proof to a 7 page proof.
 
-We have presented semantic proof of generalised Cut elimination for
-the Multiplicative-Additive System Virtual (MAV), reducing Horne's
-approximately 41 page proof to 7 and also providing an Agda
-mechanisation. Our proof technique also restricts easily to BV (we
-simply skip the use of $+$-closed lower sets and use lower sets
-directly instead). We believe that adding additive units ($\top$ and
-$0$ in Girard's notation) will be straightforward.
+Our proof technique is modular, and can be adapted with relative ease to a variety of related systems.
+To evidence this claim, we have adapted our Agda formalisation to prove generalised cut elimination to the following systems:
+\begin{description}
+  \item[BV]
+        The basic system does not have the additives (\ie $\vWith$ and $\vPlus$).
+        The proof is a straightforward restriction of our proof for MAV,
+        but only relies on lower sets, rather than $+$-closed lower sets.
+        See:
+        \begin{center}
+          \url{\AgdaBaseUrl/BV.CutElim.html}
+        \end{center}
+  \item[MAUV]
+        The multiplicative-additive-unital system adds the additive units (\ie $\top$ and $\mathbf{0}$, using Girard's notation).
+        The proof is a straightforward extension of our proof for MAV, and requires the use of lower sets which are $+$-closed as well as $0$-closed.
+  \item[NEL]
+        Non-commutative exponential logic~\cite{GuglielmiS11} extends BV with the exponentials (\ie $!$ and $?$, using Girard's notation).
+\end{description}
+The work opens up several paths for future work. The theory developed
+here for lifting Day pomonoids to $+$-closed lower sets enables alternative Cut-elimination proofs for other substructural logics, such as MALL and Bunched Implications (Okada's technique has already been applied here by Frumin~\cite{Frumin22:psc}).
+We find the technique of using $+$-closed lower sets rather than more opaque closure operators more revealing in how the
 
-This work opens up several paths for future work. The theory developed
-here for lifting Day pomonoids to $+$-closed lower sets should also
-enable alternative Cut-elimination proofs for other substructural
-logics, such as MALL and Bunched Implications (Okada's technique has
-already been applied here by Frumin \cite{Frumin22:psc}). We find the
-technique of using $+$-closed lower sets rather than more opaque
-closure operators more revealing in how the
-
-We also plan to investigate extensions of MAV with exponentials, as in
+We plan to investigate extensions of MAV with exponentials, as in
 the System NEL \cite{GuglielmiS11}, and Kleene Star operators which
@@
 Kleene Star would tighten the connection with Concurrent Kleene
-Algebras we highlighted in \Cref{remark:cka}. More generally, fixpoint
+Algebras we highlighted in \Cref{remark:cka}. It would interesting to
+see to what extent MAV can be seen as a logic for processes
+represented as elements of MAV-frames. More generally, fixpoint
 operators following Baelde \cite{Baelde12} and De, Jafarrahmani and

### 2024-04-04 doc/sections/mav-extensions.tex
Finishing touches on conclusions & publish static HTML

@@
         but only relies on lower sets, rather than $+$-closed lower sets.
-        See:
+        The source code of the proof is available at the following URL:
         \begin{center}
@@
         The proof is a straightforward extension of our proof for MAV, and requires the use of lower sets which are $+$-closed as well as $0$-closed.
+        The source code of the proof is available at the following URL:
+        \begin{center}
+          \url{\AgdaBaseUrl/MAUV.CutElim.html}
+        \end{center}
   \item[NEL]
         Non-commutative exponential logic~\cite{GuglielmiS11} extends BV with the exponentials (\ie $!$ and $?$, using Girard's notation).
+        The proof is a straightforward extension of our proof for MAV, and requires that we:
+        \begin{enumerate*}
+          \item add \emph{near-exponentials}, which do not satisfy monoidality, to BV-frames;
+          \item construct exponentials on lower sets, which adds monoidality;
+          \item construct exponentials on Chu spaces, which adds duality; and
+          \item extend the main proposition (\Cref{prop:embedding-sem}) to account for the new connectives, which requires lemmas similar to those for $\vTens$ and $\vParr$.
+        \end{enumerate*}
+        The source code of the proof is available at the following URL:
+        \begin{center}
+          \url{\AgdaBaseUrl/NEL.CutElim.html}
+        \end{center}
 \end{description}
-The work opens up several paths for future work. The theory developed
-here for lifting Day pomonoids to $+$-closed lower sets enables alternative Cut-elimination proofs for other substructural logics, such as MALL and Bunched Implications (Okada's technique has already been applied here by Frumin~\cite{Frumin22:psc}).
-We find the technique of using $+$-closed lower sets rather than more opaque closure operators more revealing in how the
+The work opens up several paths for future work.
+The theory, developed here, for lifting Day pomonoids to $+$-closed lower sets enables alternative Cut-elimination proofs for other substructural logics, such as MALL and Bunched Implications.
+(Okada's technique has already been applied to Bunched Implications by Frumin~\cite{Frumin22:psc}.)
+We find the technique of using $+$-closed lower sets more revealing in how the join structure is preserved than the use of impredicative closure operators in Frumin's proof or double negation closure in Okada's.
 
-We plan to investigate extensions of MAV with exponentials, as in
-the System NEL \cite{GuglielmiS11}, and Kleene Star operators which
-can be seen as the exponential for the $\vSeq$ connective. Adding a
-Kleene Star would tighten the connection with Concurrent Kleene
-Algebras we highlighted in \Cref{remark:cka}. It would interesting to
-see to what extent MAV can be seen as a logic for processes
-represented as elements of MAV-frames. More generally, fixpoint
-operators following Baelde \cite{Baelde12} and De, Jafarrahmani and
-Saurin \cite{De22:psc}. The latters' use of Okada's technique is not
-compatible with Agda's logic because it relies on impredicativity to
-construct fixpoints with the double negation closure. We believe that
-our more direct predicative technique will be able to use Agda's
-inductive and coinductive types.
+We plan to investigate extensions of MAV with exponentials, as in the system NEL, and with a Kleene Star operator, which can be seen as the exponential for the $\vSeq$ connective.
+Adding a Kleene Star would tighten the connection with Concurrent Kleene Algebras we highlighted in~\Cref{remark:cka}.
+It would interesting to see to what extent MAV can be seen as a logic for processes represented as elements of MAV-frames.
+Furthermore, we plan to investigate fixpoint operators following Baelde~\cite{Baelde12} and De, Jafarrahmani and Saurin~\cite{De22:psc}.
+The latters' use of Okada's technique is not compatible with Agda's type theory, as it relies on impredicativity to construct fixpoints with the double negation closure.
+We believe that our more direct predicative technique will be able to use Agda's inductive and coinductive types.
 
-We also plan to extend our semantics of BV and MAV to a categorical
-semantics that considers equalities between proofs as well as
-provability. Such a semantics ought to be useful for treating MAV as a
-session-types style language, as considered by Ciobanu and Horne
-\cite{Ciobanu_2016}. The necessary analogue of MAV-algebras has
-already been investigated by Blute, Panangaden and Slavnov
-\cite{Blute_2010} as BV-categories, which are Aguiar and Mahajan's
-2-monoidal, or duoidal, categories \cite{Aguiar_2010} extended with
-duality. The key task will be to categorify the constructions in this
-paper to show how the categorical analogue of MAV-frames induces
-MAV-categories.
+Lastly, we plan to extend our semantics of BV and MAV to a categorical semantics that considers equalities between proofs as well as provability.
+Such a semantics ought to be useful for treating MAV as a session-typed language, as considered by Ciobanu and Horne~\cite{Ciobanu_2016}.
+The necessary analogue of MAV-algebras has already been investigated by Blute, Panangaden, and Slavnov~\cite{Blute_2010} as BV-categories, which are Aguiar and Mahajan's 2-monoidal (or duoidal) categories~\cite{Aguiar_2010} extended with duality.
+The key task will be to categorify the constructions in this paper to show how the categorical analogue of MAV-frames induces MAV-categories.

### 2024-04-04 doc/sections/mav-mechanisation.tex
Finishing touches on conclusions & publish static HTML

@@
 \end{center}
+Furhtermore, a hyperlinked HTML rendition of the source can be browsed at the following URL:
+\begin{center}
+  \url{\AgdaBaseUrl}
+\end{center}
+In \Cref{sec:table-of-statments}, we provide a guide to the mechanisation relating the Definitions, Propositions, and Theorems in the previous sections to the Agda definitions in the mechanisation.
 The formalisation uses setoids to represent sets, and reuses definitions from the Agda Standard Library~\cite{AgdaStdlib20} where appropriate.
-We have provided a guide to the mechanisation relating it to the Definitions, Propositions, and Theorems in the previous sections in \Cref{sec:table-of-statments}.
 

### 2024-04-10 doc/sections/introduction.tex
Draft version for MFPS 2024
[ tex ] cite journal version of BV/POMset logic complexity

@@
       BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
-}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}. The proof technique also extends to the additive units.
+}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
+The proof technique also extends to the additive units and the exponentials.
 Our proofs are constructive and mechanised in Agda~\cite{Agda264}.
@@
 Such a connective was already present in another extension of Linear Logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
-Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
+Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl,NguyenS23:complexity} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
 Neither BV nor Pomset logic has a sequent calculus. Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.

### 2024-05-30 doc/sections/introduction.tex
Spell check

@@
 Horne~\cite{Horne15:mav} gave a syntactic proof of the admissibility of the up fragment for MAV, that extends Guglielmi's technique with further reasoning about the additives.
-The proof is quite lengthy and involves intrincate syntactic reasoning and the subtle and complex termination measures.
+The proof is quite lengthy and involves intricate syntactic reasoning and the subtle and complex termination measures.
 
 We present an alternative proof of cut-elimination via a semantic model.
-This proof avoids some of the intrincacy of Horne's proof.
+This proof avoids some of the intricacy of Horne's proof.
 We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction.
-We demonsrate this by scaling down to plain BV and up to MAV with additive units.
+We demonstrate this by scaling down to plain BV and up to MAV with additive units.
 
@@
 The phase space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
-Attempts to extend the model with the non-commutative connective result in two distinct dual non-comutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
+Attempts to extend the model with the non-commutative connective result in two distinct dual non-commutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
 

### 2024-06-10 doc/sections/introduction.tex
[ tex ] Proof reading, and fixing some references

@@
 The problem with such a relation is that, while the multiplicative connectives of Linear Logic capture parallel composition, no connective of Linear Logic captures \emph{sequential composition}.
-Eventually, Guglielmi's attempts yielded BV, which extends Multiplicative Linear Logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
+Eventually, Guglielmi's attempts yielded BV, which extends Multiplicative Linear Logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective for sequential composition.
 Such a connective was already present in another extension of Linear Logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
 Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl,NguyenS23:complexity} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
-Neither BV nor Pomset logic has a sequent calculus. Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.
+Neither BV nor Pomset logic has a sequent calculus. Tiu~\cite{Tiu06:sisii} showed that no sequent calculus can capture BV, and it is assumed that this result extends to Pomset logic.
 
-\emph{Cut Elimination}, or \emph{admissibility of Cut}, is the fundamental property of Gentzen Sequent Calculi systems, which states that proofs using the Cut rule to introduce ``detours'' can be normalised to ones without.
+\emph{Cut-elimination}, or \emph{admissibility of Cut}, is the fundamental property of Gentzen Sequent Calculi systems, which states that proofs using the Cut rule to introduce ``detours'' can be normalised to ones without.
 Crucial properties such as consistency and decidability follow from Cut-elimination.
 The Deep Inference analogue of Cut-elimination is the admissibility of the whole \emph{up} fragment of the calculus, which includes the Deep Inference form of Cut (which we describe in \Cref{sec:mav-syntax} below) as well as duals of most of the other rules of the calculus.
-Admissibility of the up fragment has the same metatheoretic benefits for Deep Inference systems as it does for Sequent Calculus ones.
+Admissibility of the \emph{up} fragment has the same metatheoretic benefits for Deep Inference systems as it does for Sequent Calculus ones.
 
@@
 We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction.
-We demonstrate this by scaling down to plain BV and up to MAV with additive units.
+We demonstrate this by scaling down to plain BV and up to MAV with additive units, and also to BV with exponentials (Guglielmi and Stra{\ss}burger's System NEL \cite{Burger_2011,GuglielmiS11}).
 
@@
 The phase space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
-Attempts to extend the model with the non-commutative connective result in two distinct dual non-commutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
+Attempts to extend the model with the non-commutative connective result in two distinct but dual non-commutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
 
@@
 Our main contribution is the use of semantic techniques to derive the admissibility of identity expansion, cut, and the other \emph{co-} rules of MAV.
-To this end, we have developed a number of results on the semantics of BV and MAV:
+To this end, we have developed a number of results concerning the semantics of BV and MAV:
 \begin{enumerate}
       \item In \Cref{sec:mav-algebras}, we propose MAV-algebras as the algebraic counterpart of MAV.
-In short, an MAV-algebra is a $*$-autonomous partial order with meets, and another partially ordered monoidal structure that is \emph{duoidal} with respect to the $*$-autonomous structure.
-      \item Normal proofs (our name for the ``up'' fragment) as we define them in the next section do not {\it a priori} support all the structure of an MAV-algebra, so we define the weaker notion of \emph{MAV-frame} (\Cref{defn:mav-frame}).
+In short, an MAV-algebra is a $*$-autonomous partial order with meets, with another partially ordered monoid structure that is \emph{duoidal} with respect to the $*$-autonomous structure.
+      \item Normal proofs (our name for the ``up'' fragment) as we define them in the next section do not {\it prima facie} support all the structure of an MAV-algebra, so we define the weaker notion of \emph{MAV-frame} (\Cref{defn:mav-frame}).
 These play the same role as Kripke structures do for modal and substructural logics.
@@
 The crucial part of the proof is that the standard Chu construction extends to the self-dual non-commutative connective of BV and MAV (\Cref{prop:chu-self-dual} and \Cref{prop:chu-monoid-duoidal}).
-Our development of the semantics of MAV and BV also opens the possibility of using these logics as sound and complete for reasoning about the MAV-frame structures we define.
+Our development of the semantics of MAV and BV also opens the possibility of using these logics as sound and complete systems for reasoning about the MAV-frame structures we define.
 

### 2024-06-10 doc/sections/mav-semantics.tex
[ tex ] fix typo in residuation
[ tex ] Proof reading, and fixing some references

@@
 (\Cref{defn:star-autonomous}) with meets and joins. The additional
-structure for seq satisfies the conditions of a duoidal category
+structure for $\vSeq$ satisfies the conditions of a duoidal category
 \cite[Definition 6.1]{Aguiar_2010} (\Cref{defn:duoidal}). We show that
@@
 
-The semantics of MAV is a collection of interacting monoids
+The algebraic semantics of MAV is a collection of interacting monoids
 on a partial order. We collect here the basic definitions and kinds of
@@
   $\rightblackspoon : A \times A \to A$ such that $x \bullet y \leq z$
-  iff $x \leq y \rightblackspoon y$.
+  iff $x \leq y \rightblackspoon z$.
 \end{definition}
@@
 pomonoid structure. Semantically, duality with commutativity is
-captured in the definition of $*$-autonomous category is, due to Barr~\cite{Barr_1979}. For our purposes, we need the partial order
+captured in the definition of $*$-autonomous category, due to Barr~\cite{Barr_1979}. For our purposes, we need the partial order
 analogue, also called a CL algebra by Troelstra~\cite{Troelstra92:lll}.
@@
   \textsc{Co-X} rules in MAV that we wish to show admissible are the
-  ones that mention the $\otimes$ and $\oplus$ connectives, with the
+  ones that mention the $\vTens$ and $\vPlus$ connectives, with the
   exception of \cref{rule:Switch}, which has a special role to play in

### 2024-06-10 doc/sections/mav-syntax.tex
[ tex ] fix typo in associtativity equations
Add nota bene
Fix nota bene
[ tex ] Proof reading, and fixing some references

@@
 There are a number of different notations in the literature for the structures of BV and related systems.
-For familiarity's sake, we opt for a notation similar to normal Linear Logic, albeit extended with the self-dual non-commutative connective $\vSeq$.
+For familiarity's sake, we opt for a notation similar to the formulas of normal Linear Logic, albeit extended with the self-dual non-commutative connective $\vSeq$.
 
@@
     \vP\vSeq(\vQ\vSeq\vR)
-     & (\vP\vSeq\vQ)\vSeq\vP
+     & (\vP\vSeq\vQ)\vSeq\vR
      & \RuleLabel*[seq-assoc]{\vSeq-Assoc}
@@
     \vP\vTens(\vQ\vTens\vR)
-     & (\vP\vTens\vQ)\vTens\vP
+     & (\vP\vTens\vQ)\vTens\vR
      & \RuleLabel*[tens-assoc]{\vTens-Assoc}
@@
     \vP\vParr(\vQ\vParr\vR)
-     & (\vP\vParr\vQ)\vParr\vP
+     & (\vP\vParr\vQ)\vParr\vR
      & \RuleLabel*[parr-assoc]{\vParr-Assoc}
@@
 This would give us rule (\ref{rule:CutBVBad}) for BV.
-However, as BV's inference rules can work arbitrarily deep in the structure, the surrounding context of pars is unnecessary---and too restrictive. Hence, the cut for BV is rule (\ref{rule:CutBV}).
+However, as BV's inference rules can work arbitrarily deep in the structure, and the system contains the \cref{rule:Switch} rule, the surrounding context of $\vParr$s is unnecessary---and too restrictive.
+Hence, the cut for BV is rule (\ref{rule:CutBV}).
 \begin{center}
@@
 
-Proof trees are a cumbersome presentation for BV's derivations---they are convenient for trees, but cumbersome in the absence of branching.
+Proof trees are a cumbersome presentation for BV's derivations---they are convenient for branching sequent proofs, but BV derivations are sequences of structures.
 \emph{Rewriting systems}, on the other hand, are a well-known and convenient notation for such derivations.
@@
 
+\textbf{N.B.}\ $\vP\vInferFrom\vQ$ is an inference rule, \emph{not a sequent}. In sequent calculus notation, it is $\frac{\vQ}{\vP}$, \emph{not} $\vP\vdash\vQ$.
+
 \emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
@@
 
-The inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vP\vInferFrom\vDual\vQ$.
+The inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vQ\vInferFrom\vDual\vP$.
 The exception is \cref{rule:Switch}, which is self-dual, up to commutativity.
-The \cref{rule:CoInteract}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new structures going left-to-right.
+The \cref{rule:CoInteract}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce new structures going left-to-right.
 Normal proofs, which we define below, avoid these \emph{synthetic} rules.

### 2024-06-11 doc/sections/mav-semantics.tex
[ tex ] words for formatting

@@
   distributes over $+$
-  ($(x + y) \bullet z \leq (x \bullet z) + (y \bullet z)$), then
+  (i.e., $(x + y) \bullet z \leq (x \bullet z) + (y \bullet z)$ holds), we have that
   $F \ClosedDay{\bullet} G = \alpha(U F \Day{\bullet} U G)$ and

### 2024-06-11 doc/sections/mav-semantics.tex
[ tex ] NBE reference

@@
 semantic technique that is akin to Okada's phase space method and to
-Normalisation by Evaluation (NbE). We construct a semantics of the
+Normalisation by Evaluation (NbE) \cite{BergerES98}. We construct a semantics of the
 whole proof system from the system of normal proofs. This semantics is

### 2024-11-26 doc/sections/introduction.tex
[ paper ] final read through

@@
 Eventually, Guglielmi's attempts yielded BV, which extends Multiplicative Linear Logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective for sequential composition.
-Such a connective was already present in another extension of Linear Logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
+Such a connective was already present in another extension of Linear Logic, Pomset Logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
 Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl,NguyenS23:complexity} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
@@
 
-Guglielmi \cite[\S4.1]{Guglielmi14:di} proves admissibility via the Splitting Theorem, which shows that proofs of conjoined structures can be split into separate subproofs.
+Guglielmi \cite[\S4.1]{Guglielmi14:di} proves admissibility of Cut via the Splitting Theorem, which shows that proofs of conjoined structures can be split into separate subproofs.
 This is proved by a detailed syntactic analysis of proofs.
@@
 
-We present an alternative proof of cut-elimination via a semantic model.
+We present an alternative proof of Cut-elimination via a semantic model.
 This proof avoids some of the intricacy of Horne's proof.
-We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction.
-We demonstrate this by scaling down to plain BV and up to MAV with additive units, and also to BV with exponentials (Guglielmi and Stra{\ss}burger's System NEL \cite{Burger_2011,GuglielmiS11}).
+Our proof is more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction.
+We demonstrate this by scaling down to plain BV and up to MAV with additive units, and also including exponentials (Guglielmi and Stra{\ss}burger's System NEL \cite{Burger_2011,GuglielmiS11}).
 
-The technique of demonstrating Cut Elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the phase space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
+The technique of demonstrating Cut Elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the Phase Space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
 The completeness of this model directly yields the existence of a cut-free proof for every proof constructible in the MALL sequent calculus.
-The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and by Frumin~\cite{Frumin22:psc} for Bunched Implications.
+The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and was adapted to Bunched Implications by  Frumin~\cite{Frumin22:psc}.
 
-The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
-The phase space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
+The Phase Semantics-based proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
+The Phase Space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual.
 Attempts to extend the model with the non-commutative connective result in two distinct but dual non-commutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
@@
 
-Our main contribution is the use of semantic techniques to derive the admissibility of identity expansion, cut, and the other \emph{co-} rules of MAV.
+Our main contribution is the use of semantic techniques to derive the admissibility of identity expansion, cut, and the other \emph{up} rules of MAV.
 To this end, we have developed a number of results concerning the semantics of BV and MAV:
 \begin{enumerate}
-      \item In \Cref{sec:mav-algebras}, we propose MAV-algebras as the algebraic counterpart of MAV.
+      \item In \Cref{sec:mav-algebras}, we propose \emph{MAV-algebras} as the algebraic counterpart of MAV.
 In short, an MAV-algebra is a $*$-autonomous partial order with meets, with another partially ordered monoid structure that is \emph{duoidal} with respect to the $*$-autonomous structure.
-      \item Normal proofs (our name for the ``up'' fragment) as we define them in the next section do not {\it prima facie} support all the structure of an MAV-algebra, so we define the weaker notion of \emph{MAV-frame} (\Cref{defn:mav-frame}).
-These play the same role as Kripke structures do for modal and substructural logics.
+      \item Normal proofs (our name for the \emph{up} fragment) as we define them in the next section do not {\it prima facie} support all the structure of an MAV-algebra, so we define the weaker notion of \emph{MAV-frame} (\Cref{defn:mav-frame}).
+These play the same role as Kripke structures or frames do for modal and substructural logics.
 The first main technical contribution of the paper is in showing that every MAV-frame can be completed to an MAV-algebra.
@@
 We briefly discuss the mechanisation in \Cref{sec:mechanisation} and provide a hyperlinked guide to the proof relating it to our mathematical development in \Cref{sec:table-of-statments}.
-Aside from the benefits of checking the proof, the Agda proof is executable and yields a program for actually normalising proofs.
+Aside from the benefits of checking the proof, the Agda proof is executable and yields a program for normalising proofs.
 
-We present our proof in the full generality of MAV, but note that essentially the same proof applies to the subsystem BV as well.
-We have also extended the proof technique to include the additive units, and to BV with exponentials (System NEL, analysed by Guglielmi and Stra{\ss}burger \cite{Burger_2011,GuglielmiS11}) We discuss further extensions in \Cref{sec:future-work}.
+We present our proof for MAV specifically, but note that essentially the same proof applies to the subsystem BV as well.
+We have also extended the proof technique to include the additive units, and with exponentials (System NEL, analysed by Guglielmi and Stra{\ss}burger \cite{Burger_2011,GuglielmiS11}).
+We discuss further extensions in \Cref{sec:future-work}.

### 2024-11-26 doc/sections/mav-extensions.tex
[ tex ] Proof reading, and fixing some references
[ paper ] final read through

@@
         The multiplicative-additive-unital system adds the additive units (\ie $\top$ and $\mathbf{0}$, using Girard's notation).
-        The proof is a straightforward extension of our proof for MAV, and requires the use of lower sets which are $+$-closed as well as $0$-closed.
+        The proof is a straightforward extension of our proof for MAV, and requires the use of lower sets which are $0$-closed as well as $+$-closed.
         The source code of the proof is available at the following URL:
@@
         \end{center}
+  \item[MAUVE]
+    The combination of all the previous systems is MAUVE: \textbf{M}ultiplicative-\textbf{A}dditive-\textbf{U}nital System \textbf{V}irtual with \textbf{E}xponentials.
+The construction of exponentials on lower sets extends to $0$- and $+$-closed ideals.
+The source code of the proof is available at the following URL:
+    \begin{center}
+      \url{\AgdaBaseUrl/MAUVE.CutElim.html}
+    \end{center}
 \end{description}
 The work opens up several paths for future work.
-The theory, developed here, for lifting Day pomonoids to $+$-closed lower sets enables alternative Cut-elimination proofs for other substructural logics, such as MALL and Bunched Implications.
-(Okada's technique has already been applied to Bunched Implications by Frumin~\cite{Frumin22:psc}.)
+The theory developed here for lifting Day pomonoids to $+$-closed lower sets enables alternative Cut-elimination proofs for other substructural logics, such as MALL and Bunched Implications.
+(Okada's technique has already been adapted to Bunched Implications by Frumin~\cite{Frumin22:psc}.)
 We find the technique of using $+$-closed lower sets more revealing in how the join structure is preserved than the use of impredicative closure operators in Frumin's proof or double negation closure in Okada's.

### 2024-11-26 doc/sections/mav-semantics.tex
[ paper ] final read through

@@
 interchange law (the \cref{rule:Sequence} rule in the proof
-system). We follow \cite[Definition 6.1]{Aguiar_2010} generalising
+system). We follow Aguiar and Mahajan \cite[Definition 6.1]{Aguiar_2010} generalising
 these to the case of monoids with differing units. Their terminology
@@
   $\alpha$ preserves the monoid operation:
-  $\alpha F \ClosedDay{\bullet} \alpha F = \alpha (F \Day{\bullet}
+  $\alpha F \ClosedDay{\bullet} \alpha G = \alpha (F \Day{\bullet}
     G)$. With this, we can show that the monotonicity, associativity,

### 2024-11-26 doc/sections/mav-syntax.tex
[ paper ] final read through

@@
 Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see.
-In BV, to acknowledge this symmetry and the connection with CSS, the axiom and cut rules are referred to as \emph{interaction} and \emph{co-interaction}.
+In BV, to acknowledge this symmetry and the connection with Milner's CCS, the axiom and cut rules are referred to as \emph{interaction} and \emph{co-interaction}.
 
@@
   \end{center}
+
   The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
@@
 \begin{definition}\label[defn]{defn:normal}
-  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} nor any of the other (\RuleName{CoX}) rules, and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
+  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} nor any of the other (\RuleName{Co-}) rules, and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
   \begin{displaymath}
@@
 In the following sections, we construct a semantic proof that normal proofs are complete for MAV.
+In \Cref{sec:future-work}, we report on extensions of the same technique to variants of MAV.

### 2024-11-27 doc/sections/mav-extensions.tex
[ paper ] last updates

@@
 
-We plan to investigate extensions of MAV with exponentials, as in the system NEL, and with a Kleene Star operator, which can be seen as the exponential for the $\vSeq$ connective.
+We plan to investigate extensions of MAV with a Kleene Star operator, which can be seen as the exponential for the $\vSeq$ connective.
 Adding a Kleene Star would tighten the connection with Concurrent Kleene Algebras we highlighted in~\Cref{remark:cka}.
 It would interesting to see to what extent MAV can be seen as a logic for processes represented as elements of MAV-frames.
-Furthermore, we plan to investigate fixpoint operators following Baelde~\cite{Baelde12} and De, Jafarrahmani and Saurin~\cite{De22:psc}.
+More generally, we plan to investigate fixpoint operators following Baelde~\cite{Baelde12} and De, Jafarrahmani and Saurin~\cite{De22:psc}.
 The latters' use of Okada's technique is not compatible with Agda's type theory, as it relies on impredicativity to construct fixpoints with the double negation closure.
@@
 
-Lastly, we plan to extend our semantics of BV and MAV to a categorical semantics that considers equalities between proofs as well as provability.
+Lastly, we plan to extend our semantics of BV and MAV to a category-theoretic semantics that considers equalities between proofs as well as provability.
 Such a semantics ought to be useful for treating MAV as a session-typed language, as considered by Ciobanu and Horne~\cite{Ciobanu_2016}.

### 2025-05-02 journal-version/sections/mav-mechanisation.tex
[ tex ] Start on a journal version

--- 2024-04-04 doc/sections/mav-mechanisation.tex
@@
 \end{center}
-Furhtermore, a hyperlinked HTML rendition of the source can be browsed at the following URL:
+Furthermore, a hyperlinked HTML rendition of the source can be browsed at the following URL:
 \begin{center}
@@
 We suspect that this would likely be quite involved, due to the widespread and implicit use of syntactic equalities when manipulating structures, as well as the construction of the relevant termination measures.
-The semantic constructions are relatively straightforward to formalise in Agda.
+We found that the semantic constructions were relatively straightforward to formalise in Agda.
 
-In addition to increasing the confidence in our results, a key benefit of the formalised proof in a proof assistant such as Agda is that the proof normalisation procedure defined by \Cref{thm:cut-elim} is executable.
+In addition to increasing the confidence in our results, a key benefit of the formalised proof in a proof assistant for constructive proof such as Agda is that the proof normalisation procedure defined by \Cref{thm:cut-elim} is executable.
 As an example, we have normalised the one-step proof below:

### 2025-05-02 journal-version/paper.tex
[ tex ] Ported paper to LMCS class, except for appendix

\documentclass{lmcs}

\keywords{Linear Logic, Deep Inference, Algebraic Semantics, Metatheory}

\usepackage{hyperref}
\usepackage{mathcommand}
\usepackage{graphicx}
\usepackage{cmll}
\usepackage{mathpartir}
\usepackage[all]{xy}
\usepackage[inline]{enumitem}
\usepackage{amssymb}
\usepackage{fdsymbol}
\usepackage{stmaryrd}
\usepackage{parskip}
\usepackage[inline]{enumitem}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{longtable}
\usepackage[UKenglish,all]{foreign}
\usepackage[goodsyntax]{virginialake}
\vllineartrue%
%\usepackage{url}
%\sloppy

\input{local-macros}

\begin{document}

\title{A Semantic Proof of Generalised Cut Elimination for Deep Inference}
\titlecomment{Longer version of the MFPS version}
\thanks{This work was funded by the
  \href{https://www.ukri.org/about-us/epsrc/}{Engineering and Physical
    Sciences Research Council}: Grant number
  \href{https://gow.epsrc.ukri.org/NGBOViewGrant.aspx?GrantRef=EP/T026960/1}{EP/T026960/1,
    \emph{AISEC: AI Secure and Explainable by Construction}.}}

\author[R. Atkey]{Robert Atkey}[a]
\author[W. Kokke]{Wen Kokke}[b]

\address{Mathematically Structured Programming Group\\
  Computer and Information Sciences\\
  University of Strathclyde\\
  Glasgow, Scotland, UK}
\email{robert.atkey@strath.ac.uk}

\address{}
\email{me@wen.works}

% FIXME: shorten this
\begin{abstract}
  \emph{Multiplicative-Additive System Virtual} (MAV) is a logic that
  extends Multiplicative-Additive Linear Logic with a self-dual
  non-commutative operator expressing the concept of ``before'' or
  ``sequencing''. MAV is also an extenson of the the logic Basic
  System Virtual (BV) with additives. Formulas in BV have an appealing
  reading as processes with parallel and sequential composition. MAV
  adds internal and external choice operators. BV and MAV are also
  closely related to Concurrent Kleene Algebras.

  Proof systems for MAV and BV are Deep Inference systems, which allow
  inference rules to be applied anywhere inside a structure. As with
  any proof system, a key question is whether proofs in MAV can be
  reduced to a normal form, removing detours and the introduction of
  structures not present in the original goal. In Sequent Calcluli
  systems, this property is referred to as Cut Elimination. Deep
  Inference systems have an analogous Cut rule and other rules that
  are not present in normalised proofs. Cut Elimination for Deep
  Inference systems has the same metatheoretic benefits as for Sequent
  Calculi systems, including consistency and decidability.

  Proofs of Cut Elimination for BV, MAV, and other Deep Inference
  systems present in the literature have relied on intrincate
  syntactic reasoning and complex termination measures.

  We present a concise semantic proof that all MAV proofs can be
  reduced to a normal form avoiding the Cut rule and other ``non
  analytic'' rules. We also develop soundness and completeness proofs
  of MAV (and BV) with respect to a class of models. We have
  mechanised all our proofs in the Agda proof assistant, which
  provides both assurance of their correctness as well as yielding an
  executable normalisation procedure. Our technique extends to include
  exponentials and the additive units.
\end{abstract}

\maketitle

\input{sections/introduction}
%\input{sections/contribution}
\input{sections/mav-syntax}
\input{sections/mav-semantics}
\input{sections/mav-cut-elimination}
\input{sections/mav-mechanisation}
\input{sections/mav-extensions}

\section*{Acknowledgements}

We would like to thank Ross Horne for helpful comments and pointers to
related work. This work was funded by the
\href{https://www.ukri.org/about-us/epsrc/}{UKRI Engineering and
  Physical Sciences Research Council (EPSRC)}, grant number
\href{https://gow.epsrc.ukri.org/NGBOViewGrant.aspx?GrantRef=EP/T026960/1}{EP/T026960/1}
``\emph{AISEC: AI Secure and Explainable by Construction}''.

\bibliographystyle{alpha}
\bibliography{paper}

% \appendix

% \input{appendix/table-of-statements}

\end{document}

### 2025-05-02 journal-version/sections/mav-semantics.tex
[ tex ] Ported paper to LMCS class, except for appendix

--- 2024-11-26 doc/sections/mav-semantics.tex
@@
 
-\begin{definition}\label[defn]{defn:pomonoid}
+\begin{defi}\label[defn]{defn:pomonoid}
   A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
@@
   pomonoid where additionally $x \bullet y = y \bullet x$.
-\end{definition}
+\end{defi}
 
-\begin{definition}\label[defn]{defn:residual}
+\begin{defi}\label[defn]{defn:residual}
   A commutative pomonoid $(\bullet, i)$ on a poset $(A, \leq)$ is
@@
   iff $x \leq y \rightblackspoon z$.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}\label[defn]{defn:star-autonomous}
+\begin{defi}\label[defn]{defn:star-autonomous}
   A \emph{$*$-autonomous partial order} is a structure
@@
   $*$-autonomous partial order satisfies \emph{mix} if $\lnot I = I$.
-\end{definition}
+\end{defi}
 
-\begin{remark}
+\begin{rem}
   The structure of a $*$-autonomous partial order has a number of
@@
   after the definition of MAV-algebra in \Cref{defn:mav-algebra}.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{definition}\label[defn]{defn:duoidal}
+\begin{defi}\label[defn]{defn:duoidal}
   A pomonoid $(\bullet, i)$ is \emph{duoidal over} another pomonoid
@@
   \end{enumerate}
-\end{definition}
+\end{defi}
 
-\begin{remark}
+\begin{rem}
   In the case when the two pomonoids share a common unit the last
@@
   relationship are automatically met.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{definition}\label[defn]{defn:mav-algebra}
+\begin{defi}\label[defn]{defn:mav-algebra}
   An \emph{MAV-algebra} is a structure
@@
   \end{enumerate}
-\end{definition}
+\end{defi}
 
-\begin{proposition}\label[prop]{prop:mav-algebra-consequences}
+\begin{prop}\label[prop]{prop:mav-algebra-consequences}
   Let $(A, \leq, \otimes, \lhd, I, \lnot)$ be a MAV-algebra.
@@
   \end{enumerate}
-\end{proposition}
+\end{prop}
 
-\begin{definition}\label[defn]{defn:mav-interpretation}
+\begin{defi}\label[defn]{defn:mav-interpretation}
   Let $\mathit{At}$ be a set of atomic propositions. Given an
@@
   $\sem{\vP\vPlus\vQ} = \sem{\vP} \oplus \sem{\vQ}$.
-\end{definition}
+\end{defi}
 
-\begin{lemma}\label[lem]{lem:dual-ok}
+\begin{lem}\label[lem]{lem:dual-ok}
   For all $\vP$, $\sem{\vDual{\vP}} = \lnot \sem{\vP}$.
-\end{lemma}
+\end{lem}
 
-\begin{theorem}\label[thm]{thm:soundness}
+\begin{thm}\label[thm]{thm:soundness}
   The interpretation in \Cref{defn:mav-interpretation} is sound:
@@
   then $I \leq \sem{\vP}$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{remark}
+\begin{rem}
   More generally, if $P \vInferFrom* Q$ in MAV, then
@@
   reversed! It will be reversed again in the definition of MAV-frame.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{definition}\label[defn]{defn:mav-frame}
+\begin{defi}\label[defn]{defn:mav-frame}
   An \emph{MAV-frame} is a structure $(F, \leq, \parr, \lhd, i, +)$
@@
   \end{enumerate}
-\end{definition}
+\end{defi}
 
-\begin{remark}
+\begin{rem}
   An MAV-frame is essentially two duoidal relationships and a
   distributivity law.
-\end{remark}
+\end{rem}
 
-\begin{remark}
+\begin{rem}
   MAV-frames have a intuitive reading as CCS-like process algebras
@@
   process algebra.
-\end{remark}
+\end{rem}
 
-\begin{remark}\label[remark]{remark:cka}
+\begin{rem}\label[remark]{remark:cka}
   MAV-frames (and MAV-algebras) are also very similar to the
@@
   processes.
-\end{remark}
+\end{rem}
 
-\begin{proposition}\label[prop]{prop:nmav-frame}
+\begin{prop}\label[prop]{prop:nmav-frame}
   The \emph{normal proof MAV-frame} \NMAV is the partial order arising
@@
   proofs.
-\end{proposition}
+\end{prop}
 
-\begin{remark}
+\begin{rem}
   The construction of the MAV-frame \NMAV does not use the $\vTens$
@@
   \Cref{prop:embedding-sem} in mediating interaction.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{definition}\label[defn]{defn:lower-set}
+\begin{defi}\label[defn]{defn:lower-set}
   Given a partial order $(A, \leq)$, the set of lower sets
@@
   $\eta : A \to \LowerSet{A}$ as $\eta(x) = \{ y \mid y \leq x \}$.
-\end{definition}
+\end{defi}
 
-\begin{proposition}\label[defn]{defn:lower-set-embed-monotone}
+\begin{prop}\label[defn]{defn:lower-set-embed-monotone}
   For any $(A, \leq)$, the function $\eta$ is monotone, and
@@
   % \bob{and $\eta$ preserves any meets that exist}
-\end{proposition}
+\end{prop}
 
-\begin{proposition}\label[prop]{prop:day-construction}
+\begin{prop}\label[prop]{prop:day-construction}
   If $(\bullet, i)$ is a pomonoid on $(A, \leq)$, then there is a
@@
   \end{enumerate}
-\end{proposition}
+\end{prop}
 
-\begin{remark}
+\begin{rem}
   \Cref{prop:day-construction} is the Day monoidal product on functor
@@
   and lower sets.
-\end{remark}
+\end{rem}
 
-\begin{remark}
+\begin{rem}
   When $(A, \leq)$ is an MAV-frame, \Cref{prop:day-construction} gives us two pomonoids
@@
   construction:
-\end{remark}
+\end{rem}
 
-\begin{proposition}\label[prop]{prop:lower-set-duoidal}
+\begin{prop}\label[prop]{prop:lower-set-duoidal}
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ then
   $(\Day{\bullet}, \Day{i})$ is duoidal over $(\Day{\lhd}, \Day{j})$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{definition}\label[defn]{defn:closed-lower-set}
+\begin{defi}\label[defn]{defn:closed-lower-set}
   A lower set $F \in \LowerSet{A}$ is \emph{$+$-closed} if $x \in F$
@@
   $(\ClosedLowerSet{A}, \subseteq)$.
-\end{definition}
+\end{defi}
 
-\begin{proposition}
+\begin{prop}
   Let $U : \ClosedLowerSet{A} \to \LowerSet{A}$ be the ``forgetful''
@@
   $F \in \LowerSet{A}$, $F \subseteq U (\alpha F)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{definition}
+\begin{defi}
   Define the embedding $\eta^+ : A \to \ClosedLowerSet{A}$ as
   $\eta^+(x) = \alpha(\eta(x))$.
-\end{definition}
+\end{defi}
 
-\begin{remark}
+\begin{rem}
   By this proposition, $U \circ \alpha$ is a closure operator on
@@
   closure operator.
-\end{remark}
+\end{rem}
 
-\begin{proposition}
+\begin{prop}
   $(\ClosedLowerSet{A}, \subseteq)$ has all meets and joins. In the
@@
   by $F \lor G = \alpha (U F \cup U G)$.
-\end{proposition}
+\end{prop}
 
-\begin{proposition}\label[prop]{prop:closed-eta-preserve-joins}
+\begin{prop}\label[prop]{prop:closed-eta-preserve-joins}
   $\eta^+(x + y) \subseteq \eta^+(x) \lor \eta^+(y)$.
-\end{proposition}
+\end{prop}
 
-\begin{remark}
+\begin{rem}
   \Cref{prop:closed-eta-preserve-joins} is the reason for
@@
   crucial embedding property for all structures in \Cref{sec:mav-cut-elimination}.
-\end{remark}
+\end{rem}
 
-\begin{proposition}\label[prop]{prop:closed-monoid-distrib}
+\begin{prop}\label[prop]{prop:closed-monoid-distrib}
   For a commutative pomonoid $(\bullet, i)$ on $(A, \leq)$ that
@@
   $\eta^+(x \bullet y) = \eta^+(x) \ClosedDay{\bullet} \eta^+(y)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}\label[prop]{prop:closed-monoid-duoidal}
+\begin{prop}\label[prop]{prop:closed-monoid-duoidal}
   For a pomonoid $(\lhd, j)$ on $(A, \leq)$, if this satisfies
@@
   $\eta^+(x \lhd y) \leq \eta^+(x) \ClosedDay{\lhd} \eta^+(y)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{remark}
+\begin{rem}
   Generalising the situation for the unit $j$ in \Cref{prop:closed-monoid-duoidal}, $\eta(x)$ is closed for any $x$
@@
   $(A, \leq)$, then this would automatically be satisfied.
-\end{remark}
+\end{rem}
 
-\begin{remark}
+\begin{rem}
   We have used the same decoration $\ClosedDay{\bullet}$ and
@@
   so $\ClosedDay{\lhd}$ will be constructed by \Cref{prop:closed-monoid-duoidal}.
-\end{remark}
+\end{rem}
 
-\begin{remark}
+\begin{rem}
   If we have two pomonoids on $(A, \leq)$ that share a unit, then the
@@
   $\ClosedLowerSet{A}$.
-\end{remark}
+\end{rem}
 
-\begin{proposition}
+\begin{prop}
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
@@
   $(\ClosedLowerSet{A}, \subseteq)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{definition}\label[defn]{defn:chu}
+\begin{defi}\label[defn]{defn:chu}
   Let $k$ be an element of $A$. $\Chu(A, k)$ is the partial order with
@@
   $\ChuEmbed(x) = (x, x \rightblackspoon k)$.
-\end{definition}
+\end{defi}
 
-\begin{proposition}
+\begin{prop}
   $(\Chu(A, k), \sqsubseteq)$ has a $*$-autonomous structure defined
@@
   $\ChuEmbed(i) = I$.
-\end{proposition}
+\end{prop}
 
-\begin{remark}
+\begin{rem}
   If we choose $k = i$, then $(\Chu(A, i), \sqsubseteq)$ has
   $*$-autonomous structure that satisfies \emph{mix}.
-\end{remark}
+\end{rem}
 
-\begin{proposition}\label[prop]{prop:chu-meets}
+\begin{prop}\label[prop]{prop:chu-meets}
   If $A$ has binary joins, then $(\Chu(A, k), \sqsubseteq)$ has
@@
   $(a^+,a^-) \with (b^+,b^-) = (a^+ \land b^+, a^- \lor b^-)$.
-\end{proposition}
+\end{prop}
 
-\begin{remark}
+\begin{rem}
   Since $(\Chu(A, k), \sqsubseteq, \otimes, I, \lnot)$ is a
@@
   $(a^+, a^-) \oplus (b^+, b^-) = (a^+ \lor b^+, a^- \land b^-)$.
-\end{remark}
+\end{rem}
 
@@
 interact well with $k$:
-\begin{proposition}\label[prop]{prop:chu-self-dual}
+\begin{prop}\label[prop]{prop:chu-self-dual}
   Let $(\lhd, j)$ be a pomonoid on $(A, \leq)$ such that
@@
   a self-dual pomonoid on $\Chu(A, k)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{remark}
+\begin{rem}
   When $k = j$, the two conditions in the proposition are
@@
   have $I =J$.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{lemma}\label[lem]{lem:duoidal-residual}
+\begin{lem}\label[lem]{lem:duoidal-residual}
   If $(\bullet, j)$ is duoidal over $(\lhd, j)$ in a partial order
@@
     \rightblackspoon (x \lhd z)$.
-\end{lemma}
+\end{lem}
 
-\begin{remark}
+\begin{rem}
   \Cref{lem:duoidal-residual} is in some sense the
@@
   partial order, as we saw in \Cref{prop:mav-algebra-consequences}.
-\end{remark}
+\end{rem}
 
-\begin{proposition}\label[prop]{prop:chu-monoid-duoidal}
+\begin{prop}\label[prop]{prop:chu-monoid-duoidal}
   If $(\bullet, i)$ is duoidal over $(\lhd, j)$ on $(A, \leq)$, and
@@
   duoidal relationship on $\Chu(A, k)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{theorem}\label[thm]{thm:algebra-from-frame}
+\begin{thm}\label[thm]{thm:algebra-from-frame}
   If $(F, \leq, \parr, \lhd, i, +)$ is an MAV-frame, then
@@
   structure of an MAV-algebra.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}\label[thm]{thm:mavframe-soundness}
+\begin{thm}\label[thm]{thm:mavframe-soundness}
   MAV is sound for the MAV-frame semantics: if $P \vInferFrom* \vUnit$
@@
   $(\Chu(\ClosedLowerSet{F}, \ClosedDay{i}), \sqsubseteq)$.
-\end{theorem}
+\end{thm}

### 2025-05-02 journal-version/sections/introduction.tex
[ tex ] speculative list of improvements to this version

--- 2024-11-26 doc/sections/introduction.tex
@@
 We discuss further extensions in \Cref{sec:future-work}.
+
+\subsection{Differences from the MFPS version}
+
+\bob{This is a wishlist for now...}
+
+\begin{enumerate}
+\item We present Systems BV, MAV, NEL, MAUV, and MAUVE in full in \autoref{sec:mav-syntax}.
+\item We include several examples of the use of the systems, in \autoref{sec:mav-examples}, including its use in establishing simulation results, and the similarity with Concurrent Kleene Algebras.
+\item We include more explanation of why Okada's Phase Space semantic approach does not work for BV and its extensions.
+\item We explicitly define the semantics of each of the systems we consider in \autoref{sec:mav-semantics}.
+\item We explore the consequences of completeness more thoroughly \bob{What?}
+\item We add the Kleene star to the systems explored.
+\item Links to the Agda formalisation are now inline, instead of being in the appendix.
+\end{enumerate}

### 2025-05-12 journal-version/old-sections/mav-cut-elimination.tex
[ tex ] work on journal version

--- 2024-03-29 doc/sections/mav-cut-elimination.tex
@@
 
-\begin{proposition}\label[prop]{prop:embedding-sem}
+\begin{prop}\label[prop]{prop:embedding-sem}
   For all structures $\vP$, $\sem{\vP} \sqsubseteq \lnot (\ChuEmbed(\ClosedLowerEmbed(P)))$.
-\end{proposition}
+\end{prop}
 
@@
   follows from the preservation of monoid operations by
-  $\ClosedLowerEmbed$ and the \cref{rule:AtomAxiom} rule.
+  $\ClosedLowerEmbed$ and the \cref{rule:AtomInteract} rule.
 
@@
 
-\begin{theorem}\label[thm]{thm:cut-elim}
+\begin{thm}\label[thm]{thm:cut-elim}
   If $\vP\vInferFrom*\vUnit$ in MAV, then there is a normal proof $\vP\vInferFrom*\vUnit$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}\label[thm]{thm:completeness}
+\begin{thm}\label[thm]{thm:completeness}
   MAV is complete for the MAV-frame semantics: if, for all MAV-frames
@@
   $\vP\vInferFrom*\vUnit$.
-\end{theorem}
+\end{thm}

### 2025-05-12 journal-version/old-sections/mav-syntax.tex
[ tex ] work on journal version

--- 2024-11-26 doc/sections/mav-syntax.tex
@@
 
-\begin{remark}
+\begin{rem}
   In BV, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
@@
 The exception are self-dual rules, which are named with a single letter, \eg \cref{rule:Switch} is usually named $\sw$.
-\end{remark}
+\end{rem}
 
-\begin{definition}\label[defn]{defn:normal}
+\begin{defi}\label[defn]{defn:normal}
   A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} nor any of the other (\RuleName{Co-}) rules, and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
@@
   \end{displaymath}
-\end{definition}
+\end{defi}
 Normal derivations avoid the use of rules that introduce new structures into proofs, and so can be termed \emph{analytic} in contrast to the need for the synthetic rules to synthesise new structures.

### 2025-05-12 journal-version/paper.tex
[ tex ] remove some unneeded package imports
[ tex ] Build the journal version with Nix
[ tex ] work on journal version

@@
 \usepackage{mathcommand}
-\usepackage{graphicx}
 \usepackage{cmll}
 \usepackage{mathpartir}
-\usepackage[all]{xy}
 \usepackage[inline]{enumitem}
@@
 \usepackage{stmaryrd}
-\usepackage{parskip}
-\usepackage[inline]{enumitem}
 \usepackage{xspace}
@@
 
-\address{}
+\address{Well-Typed}
 \email{me@wen.works}
@@
 \begin{abstract}
-  \emph{Multiplicative-Additive System Virtual} (MAV) is a logic that
-  extends Multiplicative-Additive Linear Logic with a self-dual
-  non-commutative operator expressing the concept of ``before'' or
-  ``sequencing''. MAV is also an extenson of the the logic Basic
-  System Virtual (BV) with additives. Formulas in BV have an appealing
-  reading as processes with parallel and sequential composition. MAV
-  adds internal and external choice operators. BV and MAV are also
-  closely related to Concurrent Kleene Algebras.
-
-  Proof systems for MAV and BV are Deep Inference systems, which allow
-  inference rules to be applied anywhere inside a structure. As with
-  any proof system, a key question is whether proofs in MAV can be
-  reduced to a normal form, removing detours and the introduction of
-  structures not present in the original goal. In Sequent Calcluli
-  systems, this property is referred to as Cut Elimination. Deep
-  Inference systems have an analogous Cut rule and other rules that
-  are not present in normalised proofs. Cut Elimination for Deep
-  Inference systems has the same metatheoretic benefits as for Sequent
-  Calculi systems, including consistency and decidability.
-
-  Proofs of Cut Elimination for BV, MAV, and other Deep Inference
-  systems present in the literature have relied on intrincate
-  syntactic reasoning and complex termination measures.
-
-  We present a concise semantic proof that all MAV proofs can be
-  reduced to a normal form avoiding the Cut rule and other ``non
-  analytic'' rules. We also develop soundness and completeness proofs
-  of MAV (and BV) with respect to a class of models. We have
-  mechanised all our proofs in the Agda proof assistant, which
-  provides both assurance of their correctness as well as yielding an
-  executable normalisation procedure. Our technique extends to include
-  exponentials and the additive units.
+  We prove cut-elimination properties for some Deep Inference systems
+  using semantic techniques.
 \end{abstract}
@@
 \input{sections/introduction}
-%\input{sections/contribution}
 \input{sections/mav-syntax}

### 2025-05-12 journal-version/sections/mav-syntax.tex
[ tex ] work on journal version

\section{Deep Inference Proof Calculi}
\label{sec:deep-inference-calculi}

Deep Inference systems differ from Sequent Calculus systems in two major respects. Firstly, proofs operate on \emph{structures}, which simultaneously play the role of formulas and sequents in traditional Sequent Calculus systems. There are a number of different notations in the literature for the structures of BV and related systems. For familiarity's sake, we opt for a notation similar to the formulas of normal Linear Logic, albeit extended with the self-dual non-commutative connective $\vSeq$ when we consider this connective below. Secondly, Deep Inference proofs allow structures to be operated on at any depth in a structure, instead of only at the top-level as in Sequent Calculus proofs.

As not all readers will be familiar with Deep Inference formalisms, we present Deep Inference proof calculi starting with the Deep Inference version of Multiplicative Linear Logic with Mix (MLL+Mix), which is usually given as a Sequent Calculus \cite{Girard87:ll}. As a Deep Inference system, MLL has an appealing concise definition with just two rules, \cref{sec:mll-calculus}.

The use of Deep Inference is then justified by the addition of the sequencing connective $\vSeq$, giving Guglielmi's Basic System Virtual (BV) in \cref{sec:bv-calculus}. BV is extended in two directions, first with exponentials to give Non-commutative Exponential Logic (NEL), \cref{sec:nel-calculus}, and second with additives to give Multiplicative-Additive-Unital System Virtual (MAUV), \cref{sec:mauv-calculus}. Finally, we combine these extensions into Multiplicative-Additive-Unital System Virtual with Exponentials (MAUVE) in \cref{sec:mauve-calculus}.

\subsection{MLL+Mix: Multiplicative Linear Logic with Mix}
\label{sec:mll-calculus}

The structures of MLL are formed from positive and negative atoms
($\vPos\va$ and $\vNeg\va$) drawn from some set of atomic
propositions, units ($\vUnit$) and the multiplicative connectives
\emph{tensor} and \emph{par} ($\vTens$ and $\vParr$).
\begin{displaymath}
  \vP,\vQ,\vR,\vS
  \Coloneq \vPos\va
  \mid     \vNeg\va
  \mid     \vUnit
  \mid     \vP\vTens\vQ
  \mid     \vP\vParr\vQ
\end{displaymath}
Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative connectives.
\begin{displaymath}
  \begin{array}{
      lcl @{\hspace{1cm}}
      lcl @{\hspace{1cm}}
      lcl @{\hspace{1cm}}
      lcl}
    \vDual{\vNeg\va}
    & =
    & \vPos\va
    & \vDual{\vUnit}
    & =
    & \vUnit
    & \vDual{\vP\vTens\vQ}
    & =
    & \vDual\vP \vParr \vDual\vQ
    & \vDual{\vP\vParr\vQ}
    & =
    & \vDual\vP \vTens \vDual\vQ
  \end{array}
\end{displaymath}
Structures are considered equivalent modulo the equality $\vEquiv$, which is the smallest congruence defined by the associativity, commutativity, and identity laws that ensure that $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative monoids.
\begin{displaymath}
  \begin{array}{
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll @{\hspace{1cm}}
      l@{\;\vEquiv\;}ll}
    \vP\vTens\vUnit
     & \vP
     & \RuleLabel*[tens-unit]{\vTens-Unit}
     &
    \vP\vTens\vQ
     & \vQ\vTens\vP
     & \RuleLabel*[tens-comm]{\vTens-Comm}
     &
    \vP\vTens(\vQ\vTens\vR)
     & (\vP\vTens\vQ)\vTens\vR
     & \RuleLabel*[tens-assoc]{\vTens-Assoc}
    \\
    \vP\vParr\vUnit
     & \vP
     & \RuleLabel*[parr-unit]{\vParr-Unit}
     &
    \vP\vParr\vQ
     & \vQ\vParr\vP
     & \RuleLabel*[parr-comm]{\vParr-Comm}
     &
    \vP\vParr(\vQ\vParr\vR)
     & (\vP\vParr\vQ)\vParr\vR
     & \RuleLabel*[parr-assoc]{\vParr-Assoc}
  \end{array}
\end{displaymath}

Structure contexts are one-hole contexts over structures. Plugging ($\vC\vPlug\vP$) replaces the hole in $\vC$ with $\vP$.
\begin{displaymath}
  \vC,\vD
  \Coloneq \vEmpty
  \mid     \vC\vTens\vQ
  \mid     \vP\vTens\vD
  \mid     \vC\vParr\vQ
  \mid     \vP\vParr\vD
\end{displaymath}
The inference rules of MLL+Mix are presented as a \emph{rewriting system} on structures. As this may be surprising to readers unfamiliar with Deep Inference, let us examine how this presentation relates to the usual Sequent Calculus presentation of linear logic.
Rule~(\ref{rule:AxiomLL}), shown below, is the axiom rule in the usual one-sided presentation of linear logic.
In the one-sided presentation, the turnstile is vestigial syntax, and can be removed.
In Deep Inference systems for MLL, the $\vParr$ connective plays the same role as the comma does in the antecedent of a linear logic sequent, and the $\vUnit$ plays the same role as the empty sequent, which would give us rule~(\ref{rule:AxiomBV-bad}).
However, inference rules can work arbitrarily deep in the structure. (Hence, \emph{Deep} Inference.)
Hence, the axiom in a Deep Inference system is rule~(\ref{rule:AxiomBV}), where $\vC$ is a one-hole structure context.
\begin{center}
  $\inlineequation[rule:AxiomLL]{%
      \vlderivation{\vlin{}{}{\vdash\vP,\vDual\vP}{\vlhy{}}}}$
  \qquad
  $\inlineequation[rule:AxiomBV-bad]{%
      \vlderivation{\vlin{}{}{\vP\vParr\vDual\vP}{\vlhy{\vUnit}}}}$
  \qquad
  $\inlineequation[rule:AxiomBV]{%
      \vlderivation{\vlin{}{}{%
          \vC\vPlug{\vP\vParr\vDual\vP}}{%
          \vlhy{\vC\vPlug{\vUnit}}}}}$
  % \qquad
  % $\inlineequation[rule:mav-axiom]{%
  %     \vP\vParr\vDual\vP\vInferFrom\vUnit}$
\end{center}
Rule (\ref{rule:CutLL}) is the cut rule in the usual one-sided presentation of linear logic.
In rule (\ref{rule:CutLL}), as in any branching inference rule, the branching enforces the \emph{disjointness} of the premise derivations.
In Deep Inference, disjointness is internalised by the $\vTens$ connective.
Hence, it plays the same role as branching does in sequent calculus.
This would give us rule (\ref{rule:CutBVBad}).
However, as inference rules can work arbitrarily deep in the structure, and the system contains the \cref{rule:Switch} rule, the surrounding context of $\vParr$s is unnecessary---and too restrictive. Hence, Cut in Deep Inference is rule (\ref{rule:CutBV}).
\begin{center}
  $\inlineequation[rule:CutLL]{%
      \vlderivation{\vliin{}{}{%
          \vdash\vGG,\vGG',\vGD,\vGD'}{%
          \vlhy{\vdash\vGG,\vP,\vGG'}}{%
          \vlhy{\vdash\vGD,\vDual\vP,\vGD'}}}}$
  \qquad
  $\inlineequation[rule:CutBVBad]{%
      \vlderivation{\vlin{}{}{%
          \vGG\vParr\vGG'\vParr\vGD\vParr\vGD'}{%
          \vlhy{%
            (\vGG\vParr\vP\vParr\vGG')
            \vTens
            (\vGD\vParr\vDual\vP\vParr\vGD')}}}}$
  \qquad
  $\inlineequation[rule:CutBV]{%
      \vlderivation{\vlin{}{}{%
          \vC\vPlug{\vUnit}}{%
          \vlhy{\vC\vPlug{\vP\vTens\vDual\vP}}}}}$
\end{center}
Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see. To acknowledge this symmetry and the connection with Milner's CCS, the axiom and cut rules are referred to as \emph{interaction} and \emph{co-interaction}.

Proof trees are a cumbersome presentation for Deep Inference derivations---they are convenient for branching Sequent Calculus proofs, but Deep Inference derivations are really sequences of structures, where all branching is represented within those structures.
\emph{Rewriting systems}, on the other hand, are a well-known and convenient notation for such derivations.
Therefore, following Horne \cite{Horne15:mav}, we present the inference rules as rewrite rules.

% NOTE: These shenanigans are for cross-text table alignment.
\newlength{\vInferFromDefnWidthOfLBL}%
\settowidth{\vInferFromDefnWidthOfLBL}{$\RuleName{AtomAxiom}$}%
\newlength{\vInferFromDefnWidthOfLHS}%
\settowidth{\vInferFromDefnWidthOfLHS}{$(\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)$}%
\newlength{\vInferFromDefnWidthOfRHS}%
\settowidth{\vInferFromDefnWidthOfRHS}{$(\vP\vParr\vR)\vWith(\vQ\vParr\vR)$}%

\begin{defi}
  \emph{Inference} in MLL+Mix, written $\vInferFrom$, is the smallest relation defined by the following axioms:
  \begin{displaymath}
    \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
      \vP\vParr\vDual\vP
      & \vInferFrom
      & \vUnit
      & \makebox[\vInferFromDefnWidthOfLBL][l]{$\RuleLabel{Interact}$}
      \\
      (\vP\vTens\vQ)\vParr\vR
      & \vInferFrom
      & \vP\vTens(\vQ\vParr\vR)
      & \RuleLabel{Switch}
      \\
      &
      &
      &
      \\
      \vUnit
      & \vInferFrom
      & \vP\vTens\vDual\vP
      & \RuleLabel{CoInteract}
      \\
      &
      &
      &
      \\
      \vC\vPlug\vP\vInferFrom\vC\vPlug\vQ
      & \text{if}
      & \vP\vInferFrom\vQ
      & \RuleLabel{Mono}
      % \\
      % \vP\vInferFrom\vQ
      % & \text{if}
      % & \vP\vEquiv\vQ
      % & \RuleLabel{Equiv}
    \end{array}
  \end{displaymath}
  If $\vP\vInferFrom\vQ$, we say that $\vP$ can be inferred from $\vQ$, \ie the arrow points from conclusion to premise.
\end{defi}

\begin{rem}
  $\vP\vInferFrom\vQ$ is an inference rule, \emph{not a sequent}. In
  Sequent Calculus notation, it is $\frac{\vQ}{\vP}$, \emph{not}
  $\vP\vdash\vQ$. The sequent $\vP \vdash \vQ$ is expressed as
  $\vDual{\vP} \vParr \vQ$.
\end{rem}

\begin{defi}
  \emph{Derivation}, written $\vInferFrom*$ is the reflexive, transitive closure of inference.
  \emph{Invertible derivation}, written $\vInferFromTo*$, is the symmetric core of derivation, \ie $\vP\vInferFromTo*\vQ=\vP\vInferFrom*\vQ\cap\vQ\vInferFrom*\vP$.
  \emph{Proofs} are derivations that terminate in the unit, \eg a derivation $\vP\vInferFrom*\vUnit$ is a proof of $\vP$.
\end{defi}

In general in Deep Inference, inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vQ\vInferFrom\vDual\vP$. In MLL+Mix, the only dual pair is \cref{rule:Interact} and \cref{rule:CoInteract}. The \cref{rule:Switch} rule is self-dual up to commutativity. As we extend the system in the sections below, every new rules will have a dual counterpart. As can be seen by comparing the \cref{rule:Interact} and \cref{rule:CoInteract} rules, the difference is that (reading left-to-right) the \cref{rule:CoInteract} rule is \emph{synthetic}, in that it generates structures on the right-hand side that did not appear on the left, as opposed to the \emph{analytic} rule \cref{rule:Interact}, which does not introduce any new structures.

\begin{defi}\label[defn]{defn:normal}
  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
  \begin{displaymath}
    \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
      \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
       & \vInferFrom
       & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
       & \RuleLabel{AtomInteract}
    \end{array}
  \end{displaymath}
\end{defi}

Our main collection of results, broadly named cut-elimination, and presented in \cref{sec:cut-elimination}, is that for each of the systems we present in this section, every provable structure has a normal proof. The absence of \cref{rule:CoInteract} corresponds to Cut Elimination in Sequent Calculus, and the restriction of \cref{rule:Interact} to atoms corresponds to Identity Expansion.

\begin{rem}
  In many presentations of Deep Inference systems, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
  % The equations defining duality are usually included in the decidable equality on structures.
  Inferences, derivations, and proofs are presented vertically, as (\ref{notation:vlin}), (\ref{notation:vlde}), and (\ref{notation:vlpr}), respectively.
  \begin{center}
    $\inlineequation[notation:vlin]{%
        \vlderivation{\vlin{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlde]{%
        \vlderivation{\vlde{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlpr]{%
        \vlderivation{\vlpr{}{}{\vP}}}$
  \end{center}

  The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
  Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Interact} and \cref{rule:CoInteract} are $\iD$ and $\iU$, respectively. The exception are self-dual rules, which are named with a single letter, \eg \cref{rule:Switch} is usually named $\sw$.
\end{rem}

\subsection{BV: Basic System Virtual}
\label{sec:bv-calculus}

The Basic System Virtual (BV) extends structures with the non-commutative sequencing operation $\vSeq$...

This new connective is self-dual...

And we assume that is is a monoid with $\vI$ as its unit...

Structure contexts are extended ...

Add two new rules...

\subsection{NEL: Non-commutative Exponential Logic}
\label{sec:nel-calculus}

\subsection{MAUV: Multiplicative-Additive Unital System Virtual}
\label{sec:mauv-calculus}

\subsection{MAUVE: Multiplicative-Additive Unital System Virtual with Exponentials}
\label{sec:mauve-calculus}
